### 2020-11-09 paper/manuscript.tex
add tex

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required

%
\RequirePackage{fix-cm}
%
\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{moreverb,url}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{lineno}
\usepackage[misc]{ifsym}
\usepackage{bm}
\usepackage{amsmath}  
\usepackage{float}
\usepackage{multirow}
\usepackage{threeparttable}  
\usepackage{booktabs}
\usepackage{color}
\definecolor{revision_switch}{RGB}{255,0,0}
\graphicspath{{./fig/}}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Journal of Geodesy}
%
\begin{document}
\linenumbers
\title{GNSS displacement detection and extraction based on Bayesian inference
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}

%\titlerunning{Short form of title}        % if too long for running head

\author{Nan Shen\textsuperscript{1}\and
		Liang Chen\textsuperscript{12*}\and        
		Ruizhi Chen\textsuperscript{12} %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{
	\Letter Liang Chen\\
	{l.chen@whu.edu.cn}\\       
	\at
    {1} State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, 129 Luoyu Road, Wuhan 430079, China
    \at
    {2} Collaborative Innovation Center for Geospatial Technology,  129 Luoyu Road, Wuhan 430079, China
    \\
}

\date{Received: date }
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}

\keywords{GNSS\and unmodeled error\and machine learning\and convolutional neural network\and wavelet coherence}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}

\section{Methodology}
\subsection{GNSS Kinematic Positioning}

\subsection{Displacement Detection}
\begin{equation}\label{eq_ts}
\left[ {{x_1},{x_2}, \cdots {x_m}} \right]
\end{equation}
\begin{equation}\label{eq_cps}
\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]
\end{equation}
\begin{equation}\label{eq_ts_cps}
x \sim \left\{ {\begin{array}{*{20}{r}}
	{N({\mu _0},\sigma ),}&{t < {\tau _1}}\\
	{N({\mu _1},\sigma ),}&{{\tau _1} \le t < {\tau _2}}\\
	\vdots &{}\\
	{\begin{array}{*{20}{c}}
		{N({\mu _n},\sigma ),}
		\end{array}}&{{\tau _{n - 1}} \le t < {\tau _n}}\\
	{N({\mu _{n + 1}},\sigma ),}&{{\tau _n} \le t}
	\end{array}} \right.
\end{equation}

\section{Experiments and Results}

\section{Discussion}

\section{Conclusions}

\begin{acknowledgements}
This research was funded by the National Key Research and Development Programs 2018YFB0505400, the Natural Science Fund of Hubei Province 2018CFA007.
\end{acknowledgements}

%
\section*{Conflict of Interest}
The authors declare that they have no conflict of interest.
\section*{Author Contributions}
Conceptualization: Nan Shen; Methodology: Nan Shen; Writing - original draft preparation: Nan Shen; Writing - review and editing:Ruizhi Chen; Supervision: Liang Chen.
 \section*{Data Availability}

% BibTeX users please use one of
\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{ref}

\end{document}

### 2020-11-09 code/bocd/__init__.py

@@ -1,0 +1,1 @@
+from bocd import *

### 2020-11-09 code/bocd/bocd.py

@@ -1,0 +1,162 @@
+"""============================================================================
+Author: Gregory Gundersen
+Python implementation of Bayesian online changepoint detection for a normal
+model with unknown mean parameter. For details, see Adams & MacKay 2007:
+    "Bayesian Online Changepoint Detection"
+    https://arxiv.org/abs/0710.3742
+    "Conjugate Bayesian analysis of the Gaussian distribution"
+    https://www.cs.ubc.ca/~murphyk/Papers/bayesGauss.pdf
+This code is associated with the following blog posts:
+    http://gregorygundersen.com/blog/2019/08/13/bocd/
+    http://gregorygundersen.com/blog/2020/10/20/implementing-bocd/
+============================================================================"""
+
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import numpy as np
+from scipy.stats import norm
+
+
+# -----------------------------------------------------------------------------
+
+def bocd(data, model, hazard):
+    """Return run length posterior using Algorithm 1 in Adams & MacKay 2007.
+    """
+    # 1. Initialize lower triangular matrix representing the posterior as
+    # function of time. Model parameters are initialized in the model class.
+    (T,) = data.shape
+    R = np.zeros((T + 1, T + 1))
+    R[0, 0] = 1
+    message = np.array([1])
+
+    for t in range(1, T + 1):
+        # 2. Observe new datum.
+        x = data[t - 1]
+
+        # 3. Evaluate predictive probabilities.
+        pis = model.pred_prob(t, x)
+
+        # 4. Calculate growth probabilities.
+        growth_probs = pis * message * (1 - hazard)
+
+        # 5. Calculate changepoint probabilities.
+        cp_prob = sum(pis * message * hazard)
+
+        # 6. Calculate evidence
+        new_joint = np.append(cp_prob, growth_probs)
+        evidence = np.sum(new_joint)
+
+        # 7. Determine run length distribution.
+        R[t, :t + 1] = new_joint
+        if evidence > 0:
+            R[t, :t + 1] /= evidence
+
+        # 8. Update sufficient statistics.
+        model.update_params(t, x)
+
+        # Setup message passing.
+        message = new_joint
+
+    return R
+
+
+# -----------------------------------------------------------------------------
+
+
+class GaussianUnknownMean:
+
+    def __init__(self, mean0, var0, varx):
[…]

### 2020-11-09 code/main.py

@@ -1,14 +1,24 @@
 # coding:utf-8
-import numpy as np
+
 import matplotlib.pyplot as plt
 
-from proc.simple_handler import bayes_single_detector
+import numpy as np
+
+from proc.simple_handler import bayes_single_detector, bayes_multiple_detector
 from sim.sim_handler import sim_simple_steps
 
 if __name__ == '__main__':
-    l, noise, steps = 1000, 10, np.array([[300, -10],[500, -30],[700, -20]])
+    # 1----bayes_single_detector(disp extraction)
+    # l, noise, steps = 500, 10, np.array([[100, -30]])
+    #
+    # t, s = sim_simple_steps(l, noise, steps)
+    # plt.plot(t, s)
+    # plt.show()
+    # bayes_single_detector(t, s)
+    # 2----bayes_multiple_detector(disp extraction)
+    l, noise, steps = 500, 10, np.array([[100, -30], [200, -30], [300, -30]])
 
     t, s = sim_simple_steps(l, noise, steps)
     plt.plot(t, s)
     plt.show()
-    bayes_single_detector(t, s)
+    bayes_multiple_detector(t, s, 3)

### 2020-11-09 code/proc/changepoint_bayesian.py

@@ -1,0 +1,195 @@
+"""
+@author: Claudio Bellei
+-----------------------
+This code has been tested on pymc3 version 3.2
+"""
+
+import pymc3 as pm
+import numpy as np
+from scipy.stats import norm
+import theano
+from theano import tensor as T
+from pymc3.math import switch
+import matplotlib
+import matplotlib.pyplot as plt
+from collections import defaultdict
+import dill
+import pickle
+matplotlib.rc('font', size=10)
+matplotlib.rc('font', family='Arial')
+
+np.random.seed(100)
+
+
+
+class cpt_bayesian:
+    def __init__(self,type="normal-mean"):
+        self.type = type
+        self.labels = {"xlabel":"Time","ylabel":"Value"}
+        self.data = np.array([])
+
+        #define different template problems
+        if type=="1-cpt-mean" or type=="normal-mean":
+            self.case = 0
+            self.ncpt = 1
+            size = [2500,2500]
+            scale = [50,50] #standard deviation of distribution function
+            mu = [1000,1020] #mean of normal for first part
+        elif type=="1-cpt-var" or type=="normal-var":
+            self.case = 1
+            self.ncpt = 1
+            size = [2500,2500]
+            scale = [10,20] #standard deviation of normal distribution function
+            mu = [1000,1000] #mean of normal distributions
+            #define random variates
+        elif type=="2-cpt-mean":
+            self.case = 2
+            self.ncpt = 2
+            size = [1000,1000,1000]
+            scale = [30,30,30] #standard deviation of distribution function
+            mu = [1000,1100,800] #mean of normal distributions
+            #probability of failing the test
+        elif type=="3-cpt-mean":
+            self.case = 3
+            self.ncpt = 3
+            size = [1000,1000,500,1000]
+            mu = [1000,1100,800,1020]
+            scale = [30,30,30,30]
+        else:
+            print("invalid choice of type")
+            print("options are: normal-mean, normal-var,2-cpts-mean, 3-cpts-mean")
+
+        #stack data into single numpy array
+        for i in range(len(size)):
+            self.data = np.hstack([self.data,norm.rvs(loc=mu[i],size=size[i],scale=scale[i])])
+        self.N = len(self.data)
+
+    def plot_data(self,type="ts",p=None):
+        fig = plt.figure(figsize=(10,6))
+        n = len(self.data)
+        marker = ''
+        linestyle = '-'
[…]

### 2020-11-09 code/proc/simple_handler.py

@@ -3,12 +3,13 @@ import arviz as az
 import matplotlib.pyplot as plt
 import numpy as np
 import pymc3 as pm
+from theano import tensor as T
 
 
 def bayes_single_detector(t, s):
     with pm.Model() as abrupt_model:
         steppoint = pm.DiscreteUniform(
-            "steppoint", lower=t[1], upper=t[-1], testval=200
+            "steppoint", lower=t[1], upper=t[-1], testval=50
         )
         early_mu = pm.Uniform("early_mu", -50, 50)
         late_mu = pm.Uniform("late_mu", -50, 50)
@@ -17,7 +18,26 @@ def bayes_single_detector(t, s):
         s_obs = pm.Normal("s_obs", mu=mu, sigma=sigma, observed=s)
 
     with abrupt_model:
-        trace = pm.sample(5000)
+        trace = pm.sample(1000)
+        az.plot_trace(trace)
+        plt.show()
+    return trace
+
+
+def bayes_multiple_detector(t, s, n):
+    with pm.Model() as abrupt_model:
+        sigma = pm.Normal('sigma', mu=30, sigma=20)
+        mu = pm.Uniform("mu1", 0, 1000)
+        tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
+
+        for i in np.arange(2, n+1):
+            _mu = pm.Uniform("mu" + str(i), 0, 1000)
+            mu = T.switch(tau >= t, mu, _mu)
+            tau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
+        s_obs = pm.Normal("s_obs", mu=mu, sigma=sigma, observed=s)
+
+    with abrupt_model:
+        trace = pm.sample(1000)
         az.plot_trace(trace)
         plt.show()
     return trace

### 2020-11-11 paper/manuscript.tex
add io read

@@
 \usepackage{color}
+\usepackage{amssymb}
 \definecolor{revision_switch}{RGB}{255,0,0}
@@
 \section{Methodology}
-\subsection{GNSS Kinematic Positioning}
+\subsection{Relative real-time kinematic (RTK)}
+RTK is widely used in structural health monitoring, landslide monitoring, and other fields due to its high positioning accuracy and real-time efficiency.
+The observation model, the state model, and the extended Kalman filtering process of RTK are introduced below.
+\subsubsection{Observation model}
+The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
+\begin{figure*}
+	\begin{equation}
+	\left. \begin{array}{l}
+	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla \delta I_{\Phi {i_{br}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
+	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
+	\end{array} \right\}
+	\label{eq_dd_obs}
+	\end{equation}
+\end{figure*}
+In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; $\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; $\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; $\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD observation error of pseudo-range and carrier-phase, respectively; $\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites.
+For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
+\begin{figure*}
+	\begin{equation}
+	\left. \begin{array}{l}
+	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
+	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
+	\label{eq_dd_obs_simplified}
+	\end{equation}
+
+\end{figure*}
+By ignoring the influence of multipath, linearizing equation (\ref{eq_dd_obs_simplified}), we get
+\begin{equation}
+\label{eq_rtk_measure}
+{\bf{y}} = {\bf{Hx}} + {\bf{\varepsilon }}
+\end{equation}
+where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\cite{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.
+After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method.
+To obtain high precision positioning results, it is necessary to fix the integer ambiguity.
+The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively.
+Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\cite{teunissen1995the}.
+\begin{figure*}
+	\begin{equation}
+	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}})^T})
+	\label{eq_lamda}
+	\end{equation}
+\end{figure*}
+There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\cite{teunissen1995the} method is the most widely used one.
+The integer ambiguity is obtained by the integer least square method.
+Then, the test process is executed to determine whether to accept or reject the integer ambiguity\cite{wang2014ambiguity,wang2018improving}.
+If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.
+
+\subsubsection{State model}
+The state model is defined as follows (Takasu 2013)
+\begin{equation}
+{{\bf{x}}_k} = {\bf{F}}{{\bf{x}}_{k - 1}} + {\bf{w}}
+\end{equation}
+where ${\bf{F}} \buildrel \Delta \over = \left[ {\begin{array}{*{20}{c}}
+	{{{\bf{I}}_{3 \times 3}}}&{\bf{0}}\\
+	{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
+	\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station; Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed.
+$\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$.
+For kinematic positioning, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning.
+\subsubsection{Extended Kalman filtering}
+Kalman filtering includes two processes: prediction update and measurement update\cite{grewal2001kalman}. The prediction process is as follows:
+\begin{equation}
+{{\bf{\hat x}}_{k|k - 1}} = {\bf{F}}{{\bf{\hat x}}_{k - 1}}
+\end{equation}
+\begin{equation}
+{{\bf{Q}}_{k|k - 1}} = {\bf{F}}{{\bf{Q}}_{k - 1}}{{\bf{F}}^T} + {{\bf{G}}_w}(k)
+\end{equation}
+According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged.
+However, the coordinate covariance component becomes larger, while the ambiguity covariance component remains unchanged.
+The measurement update process is as follows:
+\begin{equation}
+{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}(k){{\bf{\hat x}}_{k|k - 1}}
+\end{equation}
+\begin{equation}
+{{\bf{S}}_k} = {\bf{H}}(k){{\bf{Q}}_{k|k - 1}}{\bf{H}}{(k)^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
+\end{equation}
+\begin{equation}
+{\bf{K}} = {{\bf{Q}}_{k|k - 1}}{\bf{H}}_k^T{\bf{S}}_k^{ - 1}
+\end{equation}
+where ${{\mathbf{v}}_{k}}$ denotes the innovation vector, and ${{\mathbf{S}}_{k}}$ is the covariance matrix of the innovation vector; $\mathbf{K}$ is the state estimation gain matrix.
+The final state is estimated as follows:
+\begin{equation}
+{{\bf{\hat x}}_k} = {{\bf{\hat x}}_{k|k - 1}} + {\bf{K}}{{\bf{v}}_k}
+\end{equation}
+\begin{equation}
+{{\bf{Q}}_k} = {{\bf{Q}}_{k|k - 1}} - {\bf{K}}{{\bf{S}}_k}{{\bf{K}}^T}
+\end{equation}
+where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the proposed method.
+
+Due to the complex spatiotemporal characteristics of observation errors, there are unmodeled error components in time series\cite{shen2020site}.
+To weaken the influence of these factors, the wavelet analysis tool is introduced as follows.
 
 \subsection{Displacement Detection}
+\subsubsection{Likelihood Function}
 \begin{equation}\label{eq_ts}
@@
 \end{equation}
+\begin{equation}\label{eq_likelihood}
+P({\bf{x}}\left| {\bf{\theta }} \right.) = P({\bf{x}}\left| {{\mu_0},{\mu_1},} \right. \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma )
+\end{equation}
+\begin{equation}\label{eq_likelihoodfunc}
+P({\bf{x}}\left| {\bf{\theta }} \right.) = \prod\limits_{x \le {\tau _1}} {P(x\left| {{\mu_0},\sigma } \right.)} \prod\limits_{i = 1}^{n - 1} {\prod\limits_{{\tau _i} \le x < {\tau _{i + 1}}} {P(x\left| {{\mu_i},\sigma } \right.)} \prod\limits_{{\tau _n} \le x} {P(x\left| {{\mu_n},\sigma } \right.)} }.
+\end{equation}
+\begin{equation}\label{eq_likelihoodfunc_detail}
+P({\bf{x}}\left| {\bf{\theta }} \right.) = \frac{1}{{{{(2\pi {\sigma ^2})}^{m/2}}}}\exp \left\{ {\frac{1}{{ - 2{\sigma ^2}}}\left[ {\sum\limits_{x < {\tau _1}} {{{(x - {\mu_0})}^2}} {\rm{ + }}\sum\limits_{i = 1}^{n - 1} {\sum\limits_{{\tau _i} \le x < {\tau _{i + 1}}} {{{(x - {\mu_i})}^2}} } {\rm{ + }}\sum\limits_{{\tau _n} \le x} {{{(x - {\mu_n})}^2}} } \right]} \right\}
+\end{equation}
+\subsubsection{Bayesian Inference}
+\begin{equation}\label{eq_bayesian_inference}
+P({\bf{\theta }}\left| {\bf{x}} \right.) = \frac{{P({\bf{\theta }})P({\bf{x}}\left| {\bf{\theta }} \right.)}}{{P({\bf{x}})}}
+\end{equation}
+
+\subsubsection{Priors}
+\begin{equation}\label{eq_bayesian_prior}
+P({\bf{\theta }}) = P({\bf{\tau }},{\bf{\mu }},\sigma ) = P({\bf{\tau }})P({\bf{\mu }})P(\sigma )
+\end{equation}
+\begin{equation}\label{eq_bayesian_prior_sigma}
+\sigma  \sim N({\mu _\sigma },{\sigma _\sigma })
+\end{equation}
+\begin{equation}\label{eq_bayesian_prior_mu}
+{\mu _i} \sim N({\mu _\mu },{\sigma _\mu })(i = 0,1, \cdots ,n)
+\end{equation}
+\begin{equation}\label{eq_bayesian_prior_mu_sum}
+P({\bf{\mu }}) = \prod\limits_{i = 0}^n {P({\mu _i})}
+\end{equation}
+
+\begin{equation}\label{eq_bayesian_prior_tau_basic}
+P({\tau _i}) = \left\{ {\begin{array}{*{20}{r}}
+	{{1 \mathord{\left/
+				{\vphantom {1 {({t_m} - {t_1}),}}} \right.
+				\kern-\nulldelimiterspace} {({t_m} - {t_1}),}}}&{i = 1}\\
+	{{1 \mathord{\left/
+				{\vphantom {1 {({t_m} - {\tau _{i - 1}}),}}} \right.
+				\kern-\nulldelimiterspace} {({t_m} - {\tau _{i - 1}}),}}}&{1 < i \le n}
+	\end{array}} \right.
+\end{equation}
+\begin{equation}\label{eq_bayesian_prior_tau_1}
+P({\bf{\tau }}) = P({\tau _1},{\tau _2}, \cdots ,{\tau _{n - 1}},{\tau _n})
+\end{equation}
+\begin{equation}\label{eq_bayesian_prior_tau_2}
+P({\bf{\tau }}) = P({\tau _n},{\tau _{n - 1}}, \cdots ,{\tau _2}\left| {{\tau _1}} \right.)P({\tau _1})
+\end{equation}
+\begin{equation}\label{eq_bayesian_prior_tau_3}
+P({\bf{\tau }}) = P({\tau _n},{\tau _{n - 1}}, \cdots ,{\tau _3}\left| {{\tau _2},{\tau _1}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
+\end{equation}
+\begin{equation}\label{eq_bayesian_prior_tau_4}
+P({\bf{\tau }}) = P({\tau _n},{\tau _{n - 1}}, \cdots ,{\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
+\end{equation}
+\begin{equation}\label{eq_bayesian_prior_tau_5}
+P({\bf{\tau }}) = P({\tau _n}\left| {{\tau _{n - 1}}} \right.) \cdots P({\tau _3}\left| {{\tau _2}} \right.)P(\left. {{\tau _2}} \right|{\tau _1})P({\tau _1})
+\end{equation}
+\subsection{Displacement Extraction}
 
 \section{Experiments and Results}
+To verify the feasibility of the proposed method, we carried out a series of experiments, including a simulation experiment and a field experiment.
+In the simulation experiment, data affected by noise and a trend item is simulated.
+In the field experiment, several displacement changes were triggered manually, and the relative real-time kinematic model is used to process the GNSS observations.
+\subsection{Simulation experiment}
+
+\subsection{Field experiment}
+The experiment was carried out on the roof of a building on the campus of Wuhan University.
+In the experiment, the equipment deployment is shown in Fig.
+\ref{fig_field_exp_config}.
+A hard plank is pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank.
+One receiver antenna is fixed on the plank as a rover; the other receiver antenna is fixed on a tripod beside it as the base station.
+Both antennas are connected to BD992 OEM boards on the table, and the OEM boards are connected to the laptops for data collection.
+As shown in subgraphs (c) and (d), the height of the antenna is measured with a tape before and after each movement of the object hanging on the plank.
+Besides, markers are made on the ground and on the antenna respectively to ensure that the same position is referenced for each measurement.
+The sampling frequency of the GNSS receiver is set to 1 Hz.
+The whole experiment lasted for nearly one hour, during which the object hanging on the plank was moved several times manually.
 

### 2020-11-11 code/config/configutil.py

@@ -1,0 +1,25 @@
+import configparser
+import os
+
+
+class ReadConfig:
+    """定义一个读取配置文件的类"""
+
+    def __init__(self, filepath=None):
+        if filepath:
+            configpath = filepath
+        else:
+            root_dir = os.path.dirname(os.path.abspath('.'))
+            configpath = os.path.join(root_dir, "config.cfg")
+        self.cf = configparser.ConfigParser()
+        self.cf.read(configpath ,encoding="utf-8-sig")
+
+    def getpath(self, param):
+        value = self.cf.get("path", param)
+        return value
+
+
+def getpath(key):
+    root_dir = os.path.dirname(os.path.abspath('.'))
+    readcfg = ReadConfig(root_dir + "\\config\\sn_laptop.cfg")
+    return readcfg.getpath(key)

### 2020-11-11 code/ioext/gnss_sol_handler.py

@@ -1,0 +1,22 @@
+from config.configutil import getpath
+import pandas as pd
+import matplotlib.pyplot as plt
+
+
+def loadsol(name):
+    solpath = getpath("rtksolpath")
+    df = pd.read_csv(solpath + name,
+                     names=['week', 'tow', 'north', 'east', 'up', 'q', 'ns', 'sdn', 'sde', 'sdu', 'sdene', 'sdeu',
+                            'sdun', 'age', 'ratio'], engine='python')
+    return df
+
+
+if __name__ == '__main__':
+    df = loadsol('rover_bd9_3_enu.pos')
+    plt.subplot(3, 1, 1)
+    plt.plot(df.loc[:, 'tow'], df.loc[:, 'north'])
+    plt.subplot(3, 1, 2)
+    plt.plot(df.loc[:, 'tow'], df.loc[:, 'east'])
+    plt.subplot(3, 1, 3)
+    plt.plot(df.loc[:, 'tow'], df.loc[:, 'up'])
+    plt.show()

### 2020-11-11 code/main.py

@@ -16,7 +16,7 @@ if __name__ == '__main__':
     # plt.show()
     # bayes_single_detector(t, s)
     # 2----bayes_multiple_detector(disp extraction)
-    l, noise, steps = 500, 10, np.array([[100, -30], [200, -30], [300, -30]])
+    l, noise, steps = 500, 10, np.array([[100, -30], [200, -30], [300, 30]])
 
     t, s = sim_simple_steps(l, noise, steps)
     plt.plot(t, s)

### 2020-11-11 code/proc/changepoint_bayesian.py

@@ -188,8 +188,8 @@ class cpt_bayesian:
             print("Can only plot theory result for single change point in mean")
             print("--Aborting--")
 
-# if __name__ == '__main__':
-#     d = cpt_bayesian("1-cpt-mean")
-#     d.plot_data()
-#     d.find_changepoint()
-#     d.plot_results()
+if __name__ == '__main__':
+    d = cpt_bayesian("3-cpt-mean")
+    d.plot_data()
+    d.find_changepoint()
+    d.plot_results()

### 2020-11-11 code/proc/simple_handler.py

@@ -26,18 +26,22 @@ def bayes_single_detector(t, s):
 
 def bayes_multiple_detector(t, s, n):
     with pm.Model() as abrupt_model:
-        sigma = pm.Normal('sigma', mu=30, sigma=20)
-        mu = pm.Uniform("mu1", 0, 1000)
+        sigma = pm.Normal('sigma', mu=10, sigma=5)
+        # sigma = pm.Uniform('sigma', 5, 15)
+        mu = pm.Uniform("mu1", 0, 30)
         tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
 
-        for i in np.arange(2, n+1):
-            _mu = pm.Uniform("mu" + str(i), 0, 1000)
+        for i in np.arange(2, n + 2):
+            _mu = pm.Uniform("mu" + str(i), -100, 100)
             mu = T.switch(tau >= t, mu, _mu)
-            tau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
+            if (i < (n + 1)):
+                tau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
         s_obs = pm.Normal("s_obs", mu=mu, sigma=sigma, observed=s)
 
     with abrupt_model:
-        trace = pm.sample(1000)
+        # pm.find_MAP()
+        trace = pm.sample(20000)
         az.plot_trace(trace)
         plt.show()
+        pm.summary(trace)
     return trace

### 2020-11-11 code/main.py
add gnss adaptive and save

@@ -1,24 +1,24 @@
 # coding:utf-8
 
 import matplotlib.pyplot as plt
+import arviz as az
 
-import numpy as np
-
-from proc.simple_handler import bayes_single_detector, bayes_multiple_detector
-from sim.sim_handler import sim_simple_steps
+from config.configutil import getpath
+from ioext.gnss_sol_handler import loadsol
+from proc.gnss_handler import bayes_multiple_detector
 
 if __name__ == '__main__':
-    # 1----bayes_single_detector(disp extraction)
-    # l, noise, steps = 500, 10, np.array([[100, -30]])
-    #
-    # t, s = sim_simple_steps(l, noise, steps)
-    # plt.plot(t, s)
-    # plt.show()
-    # bayes_single_detector(t, s)
-    # 2----bayes_multiple_detector(disp extraction)
-    l, noise, steps = 500, 10, np.array([[100, -30], [200, -30], [300, 30]])
-
-    t, s = sim_simple_steps(l, noise, steps)
-    plt.plot(t, s)
+    df = loadsol('rover_bd9_3_enu.pos')
+    t = df.loc[:, 'tow']-df.loc[0, 'tow']
+    plt.subplot(3, 1, 1)
+    plt.plot(t, df.loc[:, 'north'])
+    plt.subplot(3, 1, 2)
+    plt.plot(t, df.loc[:, 'east'])
+    plt.subplot(3, 1, 3)
+    plt.plot(t, df.loc[:, 'up'])
     plt.show()
-    bayes_multiple_detector(t, s, 3)
+    bayes_multiple_detector(t, df.loc[:, 'up'], 2)
+    #
+    # trace = az.from_netcdf(getpath('tracepath') + 'test')
+    # az.plot_trace(trace)
+    # plt.show()

### 2020-11-11 code/proc/gnss_handler.py

@@ -1,0 +1,33 @@
+# coding:utf-8
+import arviz as az
+import matplotlib.pyplot as plt
+import numpy as np
+import pymc3 as pm
+from pymc3 import save_trace
+from theano import tensor as T
+
+from config.configutil import getpath
+
+
+def bayes_multiple_detector(t, s, n):
+    with pm.Model() as abrupt_model:
+        sigma = pm.Normal('sigma', mu=0.03, sigma=0.015)
+        # sigma = pm.Uniform('sigma', 5, 15)
+        mu = pm.Uniform("mu1", -1.5, -1.4)
+        tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
+
+        for i in np.arange(2, n + 2):
+            _mu = pm.Uniform("mu" + str(i),-1.5, -1.4)
+            mu = T.switch(tau >= t, mu, _mu)
+            if (i < (n + 1)):
+                tau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
+        s_obs = pm.Normal("s_obs", mu=mu, sigma=sigma, observed=s)
+
+    with abrupt_model:
+        pm.find_MAP()
+        trace = pm.sample(5000)
+        az.plot_trace(trace)
+        az.to_netcdf(trace, getpath('tracepath')+'test')
+        plt.show()
+        pm.summary(trace)
+    return trace

### 2020-11-11 code/proc/simple_handler.py

@@ -45,3 +45,18 @@ def bayes_multiple_detector(t, s, n):
         plt.show()
         pm.summary(trace)
     return trace
+# if __name__ == '__main__':
+    # 1----bayes_single_detector(disp extraction)
+    # l, noise, steps = 500, 10, np.array([[100, -30]])
+    #
+    # t, s = sim_simple_steps(l, noise, steps)
+    # plt.plot(t, s)
+    # plt.show()
+    # bayes_single_detector(t, s)
+    # 2----bayes_multiple_detector(disp extraction)
+    # l, noise, steps = 500, 10, np.array([[100, -30], [200, -30], [300, 30]])
+    #
+    # t, s = sim_simple_steps(l, noise, steps)
+    # plt.plot(t, s)
+    # plt.show()
+    # bayes_multiple_detector(t, s, 3)

### 2020-11-12 paper/manuscript.tex
add MCMC

@@
 \linenumbers
-\title{GNSS displacement detection and extraction based on Bayesian inference
+\title{GNSS displacement detection based on Bayesian inference
 %\thanks{Grants or other notes
@@
 \subsubsection{Observation model}
-The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
+The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\citep{teunissen2017springer}.
 \begin{figure*}
@@
 \end{equation}
-where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\cite{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.
+where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\citep{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.
 After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method.
@@
 The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively.
-Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\cite{teunissen1995the}.
+Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\citep{teunissen1995the}.
 \begin{figure*}
@@
 \end{figure*}
-There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\cite{teunissen1995the} method is the most widely used one.
+There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\citep{teunissen1995the} method is the most widely used one.
 The integer ambiguity is obtained by the integer least square method.
-Then, the test process is executed to determine whether to accept or reject the integer ambiguity\cite{wang2014ambiguity,wang2018improving}.
+Then, the test process is executed to determine whether to accept or reject the integer ambiguity\citep{wang2014ambiguity,wang2018improving}.
 If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.
@@
 \subsubsection{Extended Kalman filtering}
-Kalman filtering includes two processes: prediction update and measurement update\cite{grewal2001kalman}. The prediction process is as follows:
+Kalman filtering includes two processes: prediction update and measurement update\citep{grewal2001kalman}. The prediction process is as follows:
 \begin{equation}
@@
 
-Due to the complex spatiotemporal characteristics of observation errors, there are unmodeled error components in time series\cite{shen2020site}.
+Due to the complex spatiotemporal characteristics of observation errors, there are unmodeled error components in time series\citep{shen2020site}.
 To weaken the influence of these factors, the wavelet analysis tool is introduced as follows.
@@
 \end{equation}
+
+\subsubsection{Markov Chain Monte Carlo (MCMC)}
+The posterior distribution of the parameters depends on the prior distribution and the likelihood function.
+Obtaining the posterior probability of parameters by direct integration or sum requires a lot of operations, which is difficult to achieve.
+In this work, the Markov chain Monte Carlo technique is used to approximate the integral or sum value.
+Monte Carlo sampling is to construct the integral or sum function as the expectation under a certain distribution, and then approximate the expectation by the corresponding average value\citep{goodfellow2016deep}.
+
+\begin{equation}\label{eq_monte_carlo_1}
+s =\sum\limits_x g(x)= \sum\limits_x {p(x)f(x) = {E_p}[f(x)]}
+\end{equation}
+\begin{equation}\label{eq_monte_carlo_2}
+s =\int {g(x)}= \int {p(x)f(x)dx}  = {E_p}[f(x)]
+\end{equation}
+where $g(x)$ is the function to be integrated or summated; $p(x)$ is the probability distribution or probability density function of $x$.
+The integral or summation problem of $g(x)$ is transformed into the mathematical expectation problem of $f(x)$ under the distribution $p(x)$.
+This mathematical expectation can be approximated by sampling from $p(x)$.
+
+\begin{equation}\label{eq_monte_carlo_3}
+\hat s = \frac{1}{n}\sum\limits_{i = 1}^n {f({x_i})}
+\end{equation}
+where $x_i$ is the sample with the distribution of $p(x)$.
+As can be seen from the above, Monte Carlo method as a general sampling simulation sum or integration method, depends on sampling from the distribution of $p(x)$.
+However, it is not easy to directly sample from the target distribution of $p(x)$.
+At present, the most popular solution is to use Markov chain Monte Carlo sampling, which provides a general way to construct a sequence that converges to the target distribution.
+According to Markov chain, the probability of state transition at a certain time only depends on its previous state, which is expressed as follows
+
+\begin{equation}\label{eq_markov_chain_1}
+P({x_{n + 1}}\left| {{x_n},{x_{n - 1}}} \right.,{x_{n - 2}}, \cdots ,{x_2},{x_1}) = P({x_{n + 1}}\left| {{x_n}} \right.)
+\end{equation}
+If a Markov process is neither periodic nor irreducible, then the Markov process is ergodic, that is, each state appears with a certain probability.
+The Markov process of ergodic states has an important property: no matter what the initial state probability is, the Markov process of the ergodic state tends to be a stable distribution after enough state transitions.
+That is, for the initial probability distribution is $\pi_0(x)$, the probability distribution after several rounds of state transition is as follows
+
+\begin{equation}\label{eq_markov_chain_2}
+\pi_{0}(x),\pi_{1}(x),\pi_{2}(x),\cdots \pi_{n}(x),\pi_{n+1}(x),\pi_{n+2}(x)\cdots
+\end{equation}
+There exists $n$ which satisfies the following conditions
+
+\begin{equation}\label{eq_markov_chain_3}
+\pi_{n}(x)=\pi_{n+1}(x)=\pi_{n+2}(x)\cdots
+\end{equation}
+This is the target distribution we want to construct.
+Based on the initial arbitrary simple probability distribution such as Gaussian distribution $\pi_{0}(x)$, the state value $x_0$ is obtained by sampling.
+Based on the probability distribution $\pi_{1}(x)=\pi_{0}(x)P(x\left| {{x_0}} \right.)$ sampling state value $x_1$, using the same method, execute $n$ times.
+Sample $(x_{n},x_{n+1},x_{n+2}\cdots)$ is the corresponding sample set of the target distribution.
+However, the implementation of MCMC also needs to consider other factors such as constructing the state transition matrix according to the target distribution, which is beyond the scope of this work.
+Two implementations of MCMC, a and the No-U-Turn sampler, are used to sample discrete random variables and continuous random variables, respectively.
+
 \subsection{Displacement Extraction}

### 2020-11-12 paper/manuscript.tex
add Bayesian Inference

@@
 \subsection{Displacement Detection}
+The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, where $m$ is the number of coordinate displacements.
+The time of displacement changes is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, where $n$ is the number of change points.
+The problem of displacement detection is defined as finding out the change points of displacement and giving the effective estimation of displacement.
+
+\subsubsection{Bayesian Inference}
+Bayesian inference is one of the most important skills in statistics.
+Bayesian inference deduces the posterior probability as the result of a priori probability and likelihood function.
+Bayesian inference calculates the posterior probability according to the Bayesian theorem
+
+\begin{equation}\label{eq_bayesian_inference}
+P({\bf{\theta }}\left| {\bf{x}} \right.) = \frac{{P({\bf{\theta }})P({\bf{x}}\left| {\bf{\theta }} \right.)}}{{P({\bf{x}})}}
+\end{equation}
+where $\bf{\theta }$ is the parameter to be estimated and $\bf{x}$ is the observation;$P({\bf{\theta }}\left| {\bf{x}} \right.)$ denotes the posterior probability; $P({\bf{\theta }})$ represents a priori probability, which refers to the probability obtained from previous experience and analysis;
+$P({\bf{x}}\left| {\bf{\theta }} \right.)$ is the likelihood function, which represents the probability of $x$ when a priori is established.
+${P({\bf{x}})}$ is the total likelihood, which is a constant value.
+
 \subsubsection{Likelihood Function}
-\begin{equation}\label{eq_ts}
-\left[ {{x_1},{x_2}, \cdots {x_m}} \right]
-\end{equation}
-\begin{equation}\label{eq_cps}
-\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]
-\end{equation}
+It is assumed that the displacement obtained by GNSS obeys Gaussian normal distribution.
+The displacement of each segment segmented by the change point obeys the Gaussian distribution of different mean and same variance, which is expressed as follows
+
 \begin{equation}\label{eq_ts_cps}
@@
 \end{equation}
+where the $n$ change points divide the time series into $n+1$ segments, and the mean values of each segment are ${\mu _0},{\mu _1},\cdots,{\mu _n}$; $\sigma$ is the standard deviation of each normal distribution; Then the likelihood probability is expressed as follows
+
 \begin{equation}\label{eq_likelihood}
@@
 \end{equation}
+where ${\bf{\theta }}=({{\mu_0},{\mu_1},} \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma) $; Assuming that the displacement observations are independent of each other, the likelihood probability can be expressed as
+
 \begin{equation}\label{eq_likelihoodfunc}
@@
 \end{equation}
+Combine \ref{eq_ts_cps} and \ref{eq_likelihoodfunc} to get the likelihood function as follows
+
 \begin{equation}\label{eq_likelihoodfunc_detail}
 P({\bf{x}}\left| {\bf{\theta }} \right.) = \frac{1}{{{{(2\pi {\sigma ^2})}^{m/2}}}}\exp \left\{ {\frac{1}{{ - 2{\sigma ^2}}}\left[ {\sum\limits_{x < {\tau _1}} {{{(x - {\mu_0})}^2}} {\rm{ + }}\sum\limits_{i = 1}^{n - 1} {\sum\limits_{{\tau _i} \le x < {\tau _{i + 1}}} {{{(x - {\mu_i})}^2}} } {\rm{ + }}\sum\limits_{{\tau _n} \le x} {{{(x - {\mu_n})}^2}} } \right]} \right\}
-\end{equation}
-\subsubsection{Bayesian Inference}
-\begin{equation}\label{eq_bayesian_inference}
-P({\bf{\theta }}\left| {\bf{x}} \right.) = \frac{{P({\bf{\theta }})P({\bf{x}}\left| {\bf{\theta }} \right.)}}{{P({\bf{x}})}}
 \end{equation}
@@
 However, the implementation of MCMC also needs to consider other factors such as constructing the state transition matrix according to the target distribution, which is beyond the scope of this work.
-Two implementations of MCMC, a and the No-U-Turn sampler, are used to sample discrete random variables and continuous random variables, respectively.
+Two implementations of MCMC,  the Metropolis-Hasting sampler\citep{chib1995understanding} and the No-U-Turn sampler\citep{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively.
 

### 2020-11-13 paper/manuscript.tex
add Prior

@@
 
-\subsubsection{Priors}
+\subsubsection{Prior Distribution}
+Assuming that the parameters ${\bf{\tau }}=(\tau_1,\mu_2,\cdots,\tau_n)$, ${\bf{\mu }}=(\mu_0,\mu_1,\cdots,\mu_n)$ and $\sigma$ are independent of each other, then:
+
 \begin{equation}\label{eq_bayesian_prior}
@@
 \end{equation}
+The posterior distribution consists of three parts, including the prior distribution of change point, mean value and standard deviation.
+
 \begin{equation}\label{eq_bayesian_prior_sigma}
@@
 \end{equation}
+
 \begin{equation}\label{eq_bayesian_prior_mu}
@@
 \end{equation}
+
 \begin{equation}\label{eq_bayesian_prior_mu_sum}

### 2020-11-13 paper/manuscript.tex
add priors

@@
 \subsection{Displacement Detection}
-The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, where $m$ is the number of coordinate displacements.
-The time of displacement changes is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, where $n$ is the number of change points.
+The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$,  and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate displacements.
+The time of displacement changes is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.
+The time corresponding to the $n$ change points satisfies the following relationship:$ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
 The problem of displacement detection is defined as finding out the change points of displacement and giving the effective estimation of displacement.
@@
 The posterior distribution consists of three parts, including the prior distribution of change point, mean value and standard deviation.
+It is assumed that the standard deviation $\sigma$ obeys the Gaussian normal distribution and is expressed as follows
 
@@
 \end{equation}
+where $\mu_{\sigma}$ and $\sigma_{\sigma}$ are determined according to the noise level of GNSS positioning.
+For the mean value of the segments divided by the change point, it is assumed to obey the continuous uniform distribution, that is
 
 \begin{equation}\label{eq_bayesian_prior_mu}
-{\mu _i} \sim N({\mu _\mu },{\sigma _\mu })(i = 0,1, \cdots ,n)
+{\mu _i} \sim U({x_l },{x_u })(i = 0,1, \cdots ,n)
 \end{equation}
+where $x_l$ and $x_u$ represent the lower limit and  upper limit of the uniform distribution, which are determined by the mean value of the coordinate time series and the possible range of variation.
+Assuming that the mean values of each segment are independent of each other, then
 
@@
 \end{equation}
+For the change point ${\bf{\tau }}$, we only know that it is a subset of the corresponding time series.
+It is assumed to obey the discrete uniform distribution.
+However, it should be noted that the lower limit of the distribution of the $i$th change point is determined by the $(i-1)$th change point, that is
 
 \begin{equation}\label{eq_bayesian_prior_tau_basic}
-P({\tau _i}) = \left\{ {\begin{array}{*{20}{r}}
-	{{1 \mathord{\left/
-				{\vphantom {1 {({t_m} - {t_1}),}}} \right.
-				\kern-\nulldelimiterspace} {({t_m} - {t_1}),}}}&{i = 1}\\
-	{{1 \mathord{\left/
-				{\vphantom {1 {({t_m} - {\tau _{i - 1}}),}}} \right.
-				\kern-\nulldelimiterspace} {({t_m} - {\tau _{i - 1}}),}}}&{1 < i \le n}
+P({\tau _i}\left| {{\tau _{i - 1}}} \right.) = \left\{ {\begin{array}{*{20}{r}}
+	{DiscreteU({t_1},{t_m}),}&{i = 1}\\
+	{DiscreteU({\tau _{i - 1}},{t_m}),}&{1 < i \le n}
 	\end{array}} \right.
 \end{equation}
+The joint probability of all change points is expressed as
+
 \begin{equation}\label{eq_bayesian_prior_tau_1}
@@
 \end{equation}
+According to the conditional probability at the change point ${\tau _1}$, the joint probability is expanded as
+
 \begin{equation}\label{eq_bayesian_prior_tau_2}
@@
 \end{equation}
+Further conditionally expand at the change point ${\tau _2}$ to get
+
 \begin{equation}\label{eq_bayesian_prior_tau_3}
@@
 \end{equation}
+Since the conditional probability $P({\tau _n},{\tau _{n - 1}}, \cdots ,{\tau _3}\left| {{\tau _2},{\tau _1}} \right.)$ is directly determined by ${\tau _2}$, it has no direct relationship with ${\tau _1}$.
+So the above formula is reduced to
+
 \begin{equation}\label{eq_bayesian_prior_tau_4}

### 2020-11-13 paper/manuscript.tex
add new action

@@
 \end{equation}
+Continue to expand in a similar way, and finally get
+
 \begin{equation}\label{eq_bayesian_prior_tau_5}
@@
 \end{equation}
+Through \ref{eq_bayesian_prior_tau_basic} and \ref{eq_bayesian_prior_tau_5}, the joint probability of all change points can be determined.
+Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula \ref{eq_bayesian_prior}, \ref{eq_bayesian_prior_sigma}, \ref{eq_bayesian_prior_mu_sum}, \ref{eq_bayesian_prior_tau_5}.
 
@@
 
-\subsection{Displacement Extraction}
-
 \section{Experiments and Results}

### 2020-11-13 code/proc/simple_handler.py

@@ -46,17 +46,17 @@ def bayes_multiple_detector(t, s, n):
         pm.summary(trace)
     return trace
 # if __name__ == '__main__':
-    # 1----bayes_single_detector(disp extraction)
+    # 1----bayes_single_detector(disp extraction) gauss noise only
     # l, noise, steps = 500, 10, np.array([[100, -30]])
     #
     # t, s = sim_simple_steps(l, noise, steps)
     # plt.plot(t, s)
     # plt.show()
     # bayes_single_detector(t, s)
-    # 2----bayes_multiple_detector(disp extraction)
-    # l, noise, steps = 500, 10, np.array([[100, -30], [200, -30], [300, 30]])
-    #
-    # t, s = sim_simple_steps(l, noise, steps)
-    # plt.plot(t, s)
-    # plt.show()
-    # bayes_multiple_detector(t, s, 3)
+    # 2----bayes_multiple_detector(disp extraction) gauss noise only
+    l, noise, steps = 500, 10, np.array([[100, -30], [200, -30], [300, 30]])
+
+    t, s = sim_simple_steps(l, noise, steps)
+    plt.plot(t, s)
+    plt.show()
+    bayes_multiple_detector(t, s, 3)

### 2020-11-14 paper/manuscript.tex
add introduction

@@
 \label{intro}
+%全球定位系统系统的应用-》位移探测
+%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
+%传统测量仪器的弊端，GNSS位移探测的优势。
+In recent decades, GNSS has been widely used in navigation, surveying, and civil aviation as a positioning method.
+Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring, industrial measurement, and other fields.
+Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence.
+
+%位移探测算法回顾，传统位移探测的弊端
+%位移探测的短板
+%本文拟采取的措施弥补这些短板
+%Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情
+%引入本文的研究内容和贡献
+%引入文章结构
 
 \section{Methodology}
-\subsection{Relative real-time kinematic (RTK)}
-RTK is widely used in structural health monitoring, landslide monitoring, and other fields due to its high positioning accuracy and real-time efficiency.
-The observation model, the state model, and the extended Kalman filtering process of RTK are introduced below.
-\subsubsection{Observation model}
-The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\citep{teunissen2017springer}.
-\begin{figure*}
-	\begin{equation}
-	\left. \begin{array}{l}
-	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla \delta I_{\Phi {i_{br}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
-	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
-	\end{array} \right\}
-	\label{eq_dd_obs}
-	\end{equation}
-\end{figure*}
-In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; $\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; $\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; $\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD observation error of pseudo-range and carrier-phase, respectively; $\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites.
-For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
-\begin{figure*}
-	\begin{equation}
-	\left. \begin{array}{l}
-	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
-	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
-	\label{eq_dd_obs_simplified}
-	\end{equation}
-
-\end{figure*}
-By ignoring the influence of multipath, linearizing equation (\ref{eq_dd_obs_simplified}), we get
-\begin{equation}
-\label{eq_rtk_measure}
-{\bf{y}} = {\bf{Hx}} + {\bf{\varepsilon }}
-\end{equation}
-where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\citep{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.
-After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method.
-To obtain high precision positioning results, it is necessary to fix the integer ambiguity.
-The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively.
-Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\citep{teunissen1995the}.
-\begin{figure*}
-	\begin{equation}
-	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}})^T})
-	\label{eq_lamda}
-	\end{equation}
-\end{figure*}
-There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\citep{teunissen1995the} method is the most widely used one.
-The integer ambiguity is obtained by the integer least square method.
-Then, the test process is executed to determine whether to accept or reject the integer ambiguity\citep{wang2014ambiguity,wang2018improving}.
-If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.
-
-\subsubsection{State model}
-The state model is defined as follows (Takasu 2013)
-\begin{equation}
-{{\bf{x}}_k} = {\bf{F}}{{\bf{x}}_{k - 1}} + {\bf{w}}
-\end{equation}
-where ${\bf{F}} \buildrel \Delta \over = \left[ {\begin{array}{*{20}{c}}
-	{{{\bf{I}}_{3 \times 3}}}&{\bf{0}}\\
-	{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
-	\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station; Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed.
-$\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$.
-For kinematic positioning, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning.
-\subsubsection{Extended Kalman filtering}
-Kalman filtering includes two processes: prediction update and measurement update\citep{grewal2001kalman}. The prediction process is as follows:
-\begin{equation}
-{{\bf{\hat x}}_{k|k - 1}} = {\bf{F}}{{\bf{\hat x}}_{k - 1}}
-\end{equation}
-\begin{equation}
-{{\bf{Q}}_{k|k - 1}} = {\bf{F}}{{\bf{Q}}_{k - 1}}{{\bf{F}}^T} + {{\bf{G}}_w}(k)
-\end{equation}
-According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged.
-However, the coordinate covariance component becomes larger, while the ambiguity covariance component remains unchanged.
-The measurement update process is as follows:
-\begin{equation}
-{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}(k){{\bf{\hat x}}_{k|k - 1}}
-\end{equation}
-\begin{equation}
-{{\bf{S}}_k} = {\bf{H}}(k){{\bf{Q}}_{k|k - 1}}{\bf{H}}{(k)^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
-\end{equation}
-\begin{equation}
-{\bf{K}} = {{\bf{Q}}_{k|k - 1}}{\bf{H}}_k^T{\bf{S}}_k^{ - 1}
-\end{equation}
-where ${{\mathbf{v}}_{k}}$ denotes the innovation vector, and ${{\mathbf{S}}_{k}}$ is the covariance matrix of the innovation vector; $\mathbf{K}$ is the state estimation gain matrix.
-The final state is estimated as follows:
-\begin{equation}
-{{\bf{\hat x}}_k} = {{\bf{\hat x}}_{k|k - 1}} + {\bf{K}}{{\bf{v}}_k}
-\end{equation}
-\begin{equation}
-{{\bf{Q}}_k} = {{\bf{Q}}_{k|k - 1}} - {\bf{K}}{{\bf{S}}_k}{{\bf{K}}^T}
-\end{equation}
-where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the proposed method.
-
-Due to the complex spatiotemporal characteristics of observation errors, there are unmodeled error components in time series\citep{shen2020site}.
-To weaken the influence of these factors, the wavelet analysis tool is introduced as follows.
+\label{method}
 
@@
 
+\subsection{Relative real-time kinematic (RTK)}
+RTK is widely used in structural health monitoring, landslide monitoring, and other fields due to its high positioning accuracy and real-time efficiency.
+The observation model, the state model, and the extended Kalman filtering process of RTK are introduced below.
+\subsubsection{Observation model}
+The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\citep{teunissen2017springer}.
+\begin{figure*}
+	\begin{equation}
+	\left. \begin{array}{l}
+	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla \delta I_{\Phi {i_{br}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
+	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
+	\end{array} \right\}
+	\label{eq_dd_obs}
+	\end{equation}
+\end{figure*}
+In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; $\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; $\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; $\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD observation error of pseudo-range and carrier-phase, respectively; $\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites.
+For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
+\begin{figure*}
+	\begin{equation}
+	\left. \begin{array}{l}
+	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
+	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
+	\label{eq_dd_obs_simplified}
+	\end{equation}
+
+\end{figure*}
+By ignoring the influence of multipath, linearizing equation (\ref{eq_dd_obs_simplified}), we get
+\begin{equation}
+\label{eq_rtk_measure}
+{\bf{y}} = {\bf{Hx}} + {\bf{\varepsilon }}
+\end{equation}
+where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\citep{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.
+After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method.
+To obtain high precision positioning results, it is necessary to fix the integer ambiguity.
+The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively.
+Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\citep{teunissen1995the}.
+\begin{figure*}
+	\begin{equation}
+	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}})^T})
+	\label{eq_lamda}
+	\end{equation}
+\end{figure*}
+There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\citep{teunissen1995the} method is the most widely used one.
+The integer ambiguity is obtained by the integer least square method.
+Then, the test process is executed to determine whether to accept or reject the integer ambiguity\citep{wang2014ambiguity,wang2018improving}.
+If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.
+
+\subsubsection{State model}
+The state model is defined as follows (Takasu 2013)
+\begin{equation}
+{{\bf{x}}_k} = {\bf{F}}{{\bf{x}}_{k - 1}} + {\bf{w}}
+\end{equation}
+where ${\bf{F}} \buildrel \Delta \over = \left[ {\begin{array}{*{20}{c}}
+	{{{\bf{I}}_{3 \times 3}}}&{\bf{0}}\\
+	{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
+	\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station; Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed.
+$\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$.
+For kinematic positioning, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning.
+\subsubsection{Extended Kalman filtering}
+Kalman filtering includes two processes: prediction update and measurement update\citep{grewal2001kalman}. The prediction process is as follows:
+\begin{equation}
+{{\bf{\hat x}}_{k|k - 1}} = {\bf{F}}{{\bf{\hat x}}_{k - 1}}
+\end{equation}
+\begin{equation}
+{{\bf{Q}}_{k|k - 1}} = {\bf{F}}{{\bf{Q}}_{k - 1}}{{\bf{F}}^T} + {{\bf{G}}_w}(k)
+\end{equation}
+According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged.
+However, the coordinate covariance component becomes larger, while the ambiguity covariance component remains unchanged.
+The measurement update process is as follows:
+\begin{equation}
+{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}(k){{\bf{\hat x}}_{k|k - 1}}
+\end{equation}
+\begin{equation}
+{{\bf{S}}_k} = {\bf{H}}(k){{\bf{Q}}_{k|k - 1}}{\bf{H}}{(k)^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
+\end{equation}
+\begin{equation}
+{\bf{K}} = {{\bf{Q}}_{k|k - 1}}{\bf{H}}_k^T{\bf{S}}_k^{ - 1}
+\end{equation}
+where ${{\mathbf{v}}_{k}}$ denotes the innovation vector, and ${{\mathbf{S}}_{k}}$ is the covariance matrix of the innovation vector; $\mathbf{K}$ is the state estimation gain matrix.
+The final state is estimated as follows:
+\begin{equation}
+{{\bf{\hat x}}_k} = {{\bf{\hat x}}_{k|k - 1}} + {\bf{K}}{{\bf{v}}_k}
+\end{equation}
+\begin{equation}
+{{\bf{Q}}_k} = {{\bf{Q}}_{k|k - 1}} - {\bf{K}}{{\bf{S}}_k}{{\bf{K}}^T}
+\end{equation}
+where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the proposed method.
+
 \section{Experiments and Results}
-To verify the feasibility of the proposed method, we carried out a series of experiments, including a simulation experiment and a field experiment.
-In the simulation experiment, data affected by noise and a trend item is simulated.
+To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation experiments and field experiments.
+In the simulation experiment, the data affected by different noises are simulated.
 In the field experiment, several displacement changes were triggered manually, and the relative real-time kinematic model is used to process the GNSS observations.

### 2020-11-14 code/proc/simple_handler.py

@@ -5,6 +5,8 @@ import numpy as np
 import pymc3 as pm
 from theano import tensor as T
 
+from sim.sim_handler import sim_simple_steps
+
 
 def bayes_single_detector(t, s):
     with pm.Model() as abrupt_model:
@@ -28,11 +30,11 @@ def bayes_multiple_detector(t, s, n):
     with pm.Model() as abrupt_model:
         sigma = pm.Normal('sigma', mu=10, sigma=5)
         # sigma = pm.Uniform('sigma', 5, 15)
-        mu = pm.Uniform("mu1", 0, 30)
+        mu = pm.Uniform("mu1", -30, 30)
         tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
 
         for i in np.arange(2, n + 2):
-            _mu = pm.Uniform("mu" + str(i), -100, 100)
+            _mu = pm.Uniform("mu" + str(i), -100, 0)
             mu = T.switch(tau >= t, mu, _mu)
             if (i < (n + 1)):
                 tau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
@@ -40,12 +42,16 @@ def bayes_multiple_detector(t, s, n):
 
     with abrupt_model:
         # pm.find_MAP()
-        trace = pm.sample(20000)
+        trace = pm.sample(5000, tune=2000)
         az.plot_trace(trace)
+        plt.show()
+        az.plot_autocorr(trace)
         plt.show()
         pm.summary(trace)
     return trace
-# if __name__ == '__main__':
+
+
+if __name__ == '__main__':
     # 1----bayes_single_detector(disp extraction) gauss noise only
     # l, noise, steps = 500, 10, np.array([[100, -30]])
     #
@@ -54,8 +60,7 @@ def bayes_multiple_detector(t, s, n):
     # plt.show()
     # bayes_single_detector(t, s)
     # 2----bayes_multiple_detector(disp extraction) gauss noise only
-    l, noise, steps = 500, 10, np.array([[100, -30], [200, -30], [300, 30]])
-
+    l, noise, steps = 3600, 10, np.array([[1000, -30], [2500, -30], [3200, 30]])
     t, s = sim_simple_steps(l, noise, steps)
     plt.plot(t, s)
     plt.show()

### 2020-11-14 code/sim/sim_handler.py

@@ -25,6 +25,7 @@ def sim_simple_steps(l, noise, steps):
     append : ndarray
         [time,value]
     """
+    np.random.seed(1)
     s = np.random.normal(0, noise, l)
     sshape = steps.shape
     for i in np.arange(0, sshape[0]):

### 2020-11-14 paper/manuscript.tex
add output code

@@
 %传统测量仪器的弊端，GNSS位移探测的优势。
-In recent decades, GNSS has been widely used in navigation, surveying, and civil aviation as a positioning method.
+%GNSS在位移探测中扮演的角色，以及位移探测的要求
+In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method.
 Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring, industrial measurement, and other fields.
 Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence.
+Displacement detection involves automatic identification of the time of displacement and determination of displacement.
+GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results.
 

### 2020-11-14 code/ioext/trace_io_handler.py

@@ -1,0 +1,21 @@
+import arviz as az
+import matplotlib.pyplot as plt
+import numpy as np
+from config.configutil import getpath
+import scipy.io as io
+
+
+def trace_export_4_mat(srcname, destname, n):
+    trace = az.from_netcdf(srcname)
+    data = {}
+    size = trace.posterior.sigma.data.size
+    data['sigma'] = trace.posterior.sigma.data.reshape(size, 1)
+    for i in np.arange(1, n + 1):
+        data['mu' + str(i)] = trace.posterior['mu' + str(i)].data.reshape(size, 1)
+        data['tau' + str(i)] = trace.posterior['tau' + str(i)].data.reshape(size, 1)
+    data['mu' + str(n + 1)] = trace.posterior['mu' + str(n + 1)].data.reshape(size, 1)
+    io.savemat(destname, data, oned_as='column')
+
+
+if __name__ == '__main__':
+    trace_export_4_mat(getpath('tracepath') + 'sim_simple', getpath('data4origin') + 'sim_simple_posterior.mat', 3)

### 2020-11-14 code/view/trace_view_handler.py

@@ -1,0 +1,13 @@
+import arviz as az
+import matplotlib.pyplot as plt
+
+from config.configutil import getpath
+
+
+def trace_plot(name):
+    trace=az.from_netcdf(name)
+    az.plot_trace(trace)
+    plt.show()
+
+if __name__ == '__main__':
+    trace_plot(getpath('tracepath')+'sim_simple')

### 2020-11-14 code/config/configutil.py
add figsrc

@@ -21,5 +21,5 @@ class ReadConfig:
 
 def getpath(key):
     root_dir = os.path.dirname(os.path.abspath('.'))
-    readcfg = ReadConfig(root_dir + "\\code\\config\\sn_laptop.cfg")
+    readcfg = ReadConfig(root_dir + "\\config\\sn_laptop.cfg")
     return readcfg.getpath(key)

### 2020-11-14 code/proc/simple_handler.py

@@ -4,7 +4,9 @@ import matplotlib.pyplot as plt
 import numpy as np
 import pymc3 as pm
 from theano import tensor as T
+import scipy.io as io
 
+from config.configutil import getpath
 from sim.sim_handler import sim_simple_steps
 
 
@@ -28,25 +30,26 @@ def bayes_single_detector(t, s):
 
 def bayes_multiple_detector(t, s, n):
     with pm.Model() as abrupt_model:
-        sigma = pm.Normal('sigma', mu=10, sigma=5)
+        sigma = pm.Normal('sigma', mu=30, sigma=5)
         # sigma = pm.Uniform('sigma', 5, 15)
         mu = pm.Uniform("mu1", -30, 30)
         tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
 
         for i in np.arange(2, n + 2):
-            _mu = pm.Uniform("mu" + str(i), -100, 0)
+            _mu = pm.Uniform("mu" + str(i), -200, 0)
             mu = T.switch(tau >= t, mu, _mu)
             if (i < (n + 1)):
                 tau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
         s_obs = pm.Normal("s_obs", mu=mu, sigma=sigma, observed=s)
 
     with abrupt_model:
-        # pm.find_MAP()
-        trace = pm.sample(5000, tune=2000)
+        pm.find_MAP()
+        trace = pm.sample(20000, tune=5000)
         az.plot_trace(trace)
         plt.show()
         az.plot_autocorr(trace)
         plt.show()
+        az.to_netcdf(trace, getpath('tracepath')+'sim_simple')
         pm.summary(trace)
     return trace
 
@@ -60,8 +63,9 @@ if __name__ == '__main__':
     # plt.show()
     # bayes_single_detector(t, s)
     # 2----bayes_multiple_detector(disp extraction) gauss noise only
-    l, noise, steps = 3600, 10, np.array([[1000, -30], [2500, -30], [3200, 30]])
+    l, noise, steps = 3600, 30, np.array([[1000, -50], [2500, -50], [3200, 100]])
     t, s = sim_simple_steps(l, noise, steps)
+    io.savemat(getpath('data4origin') + 'sim_simple_raw.mat', {'t': t, 'x': s}, oned_as='column')
     plt.plot(t, s)
     plt.show()
     bayes_multiple_detector(t, s, 3)

### 2020-11-15 paper/manuscript.tex
add random walk try

@@
 %GNSS在位移探测中扮演的角色，以及位移探测的要求
-In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method.
-Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring, industrial measurement, and other fields.
-Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence.
+%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
+In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\citep{teunissen2017springer}. 
+Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\citep{awange2012environmental}, industrial measurement\citep{pavasovic2011application}, and other fields.
+Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\citep{shen2019a}. 
 Displacement detection involves automatic identification of the time of displacement and determination of displacement. 
 GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. 
-
+Previous studies on displacement detection based on GNSS pay more attention to how to improve the positioning accuracy.
+The research on how to identify and extract displacement from the coordinate sequence obtained by GNSS is limited.
 %位移探测算法回顾，传统位移探测的弊端
 %位移探测的短板
+
 %本文拟采取的措施弥补这些短板
 %Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情
+
 %引入本文的研究内容和贡献
+
 %引入文章结构
@@
 Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula \ref{eq_bayesian_prior}, \ref{eq_bayesian_prior_sigma}, \ref{eq_bayesian_prior_mu_sum}, \ref{eq_bayesian_prior_tau_5}.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=8 cm]{v_simple_p_model}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_simple_p_model}
+\end{figure}
 
@@
 The integer ambiguity is obtained by the integer least square method.
-Then, the test process is executed to determine whether to accept or reject the integer ambiguity\citep{wang2014ambiguity,wang2018improving}.
+Then, the test process is executed to determine whether to accept or reject the integer ambiguity.
 If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.
@@
 \subsection{Simulation experiment}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10 cm]{v_sim_simple_gauss_ts}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_sim_simple_gauss_ts}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10 cm]{v_tau_sim_simple}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_tau_sim_simple}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10 cm]{v_sigma_sim_simple}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_sigma_sim_simple}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10 cm]{v_mu_sim_simple}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_mu_sim_simple}
+\end{figure}
 
@@
 \section*{Author Contributions}
-Conceptualization: Nan Shen; Methodology: Nan Shen; Writing - original draft preparation: Nan Shen; Writing - review and editing:Ruizhi Chen; Supervision: Liang Chen.
+Conceptualization: Nan Shen, Liang Chen; Methodology: Nan Shen; Writing - original draft preparation: Nan Shen; Writing - review and editing:Ruizhi Chen; Supervision: Liang Chen.
  \section*{Data Availability}

### 2020-11-15 code/config/configutil.py

@@ -21,5 +21,5 @@ class ReadConfig:
 
 def getpath(key):
     root_dir = os.path.dirname(os.path.abspath('.'))
-    readcfg = ReadConfig(root_dir + "\\config\\sn_laptop.cfg")
+    readcfg = ReadConfig(root_dir + "\\code\\config\\sn_laptop.cfg")
     return readcfg.getpath(key)

### 2020-11-15 code/proc/simple_handler.py

@@ -7,7 +7,7 @@ from theano import tensor as T
 import scipy.io as io
 
 from config.configutil import getpath
-from sim.sim_handler import sim_simple_steps
+from sim.sim_handler import sim_simple_steps, sim_gauss_randomwalk_steps
 
 
 def bayes_single_detector(t, s):
@@ -28,7 +28,7 @@ def bayes_single_detector(t, s):
     return trace
 
 
-def bayes_multiple_detector(t, s, n):
+def bayes_multiple_detector(t, s, n, tracename):
     with pm.Model() as abrupt_model:
         sigma = pm.Normal('sigma', mu=30, sigma=5)
         # sigma = pm.Uniform('sigma', 5, 15)
@@ -41,15 +41,49 @@ def bayes_multiple_detector(t, s, n):
             if (i < (n + 1)):
                 tau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
         s_obs = pm.Normal("s_obs", mu=mu, sigma=sigma, observed=s)
-
+    g = pm.model_to_graphviz(abrupt_model)
+    g.view()
     with abrupt_model:
         pm.find_MAP()
-        trace = pm.sample(20000, tune=5000)
+        trace = pm.sample(5000, tune=1000)
         az.plot_trace(trace)
         plt.show()
         az.plot_autocorr(trace)
         plt.show()
-        az.to_netcdf(trace, getpath('tracepath')+'sim_simple')
+        az.to_netcdf(trace, getpath('tracepath') + tracename)
+        pm.summary(trace)
+    return trace
+
+
+# add random walk
+def bayes_multiple_detector_I(t, s, n, tracename):
+    with pm.Model() as abrupt_model:
+        sigma = pm.Normal('sigma', mu=30, sigma=5)
+        # sigma = pm.Uniform('sigma', 5, 15)
+        mu = pm.Uniform("mu1", -30, 30)
+        tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
+
+        for i in np.arange(2, n + 2):
+            _mu = pm.Uniform("mu" + str(i), -100, 0)
+            mu = T.switch(tau >= t, mu, _mu)
+            if (i < (n + 1)):
+                tau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
+        # add random walk
+        # sigma_rw = pm.Uniform("sigma_rw", 0, 10)
[…]

### 2020-11-15 code/sim/sim_handler.py

@@ -33,3 +33,38 @@ def sim_simple_steps(l, noise, steps):
     t = np.arange(0, l)
     return t, s
 
+
+def sim_gauss_randomwalk_steps(l, noise, walknoise, steps):
+    """
+    Append values to the end of an array.
+
+    Parameters
+    ----------
+    l : int
+        data length
+    noise : float
+        noise level.
+    walknoise: float
+        gauss random walk noise level.
+    steps : array_like
+        [time1,step1]
+        [time2,step2]
+
+     Examples
+    --------
+    l, noise, steps = 1000, 30, np.array([[500, -30]])
+    t, s = sim_simple_steps(l, noise, steps)
+    Returns
+    -------
+    append : ndarray
+        [time,value]
+    """
+    np.random.seed(1)
+    s = np.random.normal(0, noise, l)
+    randwalk = np.random.normal(0, walknoise, l)
+    s = s + np.cumsum(randwalk)
+    sshape = steps.shape
+    for i in np.arange(0, sshape[0]):
+        s[steps[i, 0]:l] = s[steps[i, 0]:l] + steps[i, 1]
+    t = np.arange(0, l)
+    return t, s

### 2020-11-16 paper/manuscript.tex
add bd9_3_up.opju
add intro

@@
 \linenumbers
-\title{GNSS displacement detection based on Bayesian inference
+\title{GNSS-based displacement detection using Bayesian inference
 %\thanks{Grants or other notes
@@
 The research on how to identify and extract displacement from the coordinate sequence obtained by GNSS is limited.
-%位移探测算法回顾，传统位移探测的弊端
+
+%位移探测算法回顾，
+%传统位移探测的弊端
 %位移探测的短板
+%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
+In \cite{GUMUS2019131}, a displacement monitoring system was designed to evaluate Network Real Time Kinematic(NRTK) for displacement detection.
+The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
+
+A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\citep{rs12203375}.
+The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement is obtained by the direct difference between the coordinates of the start and end periods.
+
+In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\citep{atanasova2018ground,fuhrmann2015estimation}.
 
 %本文拟采取的措施弥补这些短板
+%目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
 %Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情
@@
 
+\begin{table*}[h!t]
+	\centering
+	%	\fontsize{6.5}{8}\selectfont
+	\begin{threeparttable}
+		\caption{Measured height before and after each movement of the object hanging on the plank, unit (mm).}
+		\label{tab_measured_height}
+		\begin{tabular}{ccccccccc}
+			\toprule
+			&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
+			\midrule
+			\multirow{3}*{Step 1} 
+			& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
+			& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
+			& & $\Delta h$ & 30.0& 29.8& 29.4& 29.2& 29.9&29.66\\
+			\hline
+			\multirow{3}*{Step 2} 
+			& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
+			& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
+			& & $\Delta h$ &27.5& 27.2& 27.1& 27.0& 27.1& 27.18\\
+			\bottomrule
+		\end{tabular}
+	\end{threeparttable}
+\end{table*}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_3_up_ts}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_bd9_3_up_ts}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_3_up_tau}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_bd9_3_up_tau}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_3_up_sigma}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_bd9_3_up_sigma}
+\end{figure} 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_3_up_mu}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_bd9_3_up_mu}
+\end{figure}
+
+\begin{table*}[h!t]
+	\centering
+	%	\fontsize{6.5}{8}\selectfont
+	\begin{threeparttable}
+		\caption{Measured height before and after each movement of the object hanging on the plank, unit (m).}
+		\label{tab_measured_height}
+		\begin{tabular}{ccccccccc}
+			\toprule
+			&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
+			\midrule
+			\multirow{3}*{Step 1} 
+			& & ${h_0}$    &368.5&	368.9&	369.0&	368.9&	369.0&	368.9\\
+			& & ${h_1}$    &348.1&	348.0&	348.0&	348.2&	348.3&	348.1\\
+			& & $\Delta h$ & 20.4&	 20.9&	 21.0&	 20.7&	 20.7&	 20.7\\
+			\hline               
+			\multirow{3}*{Step 2}
+			& & ${h_0}$    &347.5&	347.3&	347.6&	347.5&	347.4&	347.5\\
+			& & ${h_1}$    &326.1&	326.3&	326.1&	326.0&	326.1&	326.1\\
+			& & $\Delta h$ & 21.4&	 21.0&	 21.5&	 21.5&	 21.3&	 21.3\\
+			\hline               
+			\multirow{3}*{Step 3}
+			& & ${h_0}$    &325.0&	325.1&	324.9&	325.0&	325.2&	325.0\\
+			& & ${h_1}$    &305.5&	305.3&	305.4&	305.5&	305.6&	305.5\\
+			& & $\Delta h$ & 19.5&	 19.8&	 19.5&	 19.5&	 19.6&	 19.6\\
+			\bottomrule
+		\end{tabular}
+	\end{threeparttable}
+\end{table*}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_4_up_ts}
+	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\label{fig_v_bd9_4_up_ts}
+\end{figure}
+
 \section{Discussion}

### 2020-11-16 code/ioext/trace_io_handler.py

@@ -18,4 +18,6 @@ def trace_export_4_mat(srcname, destname, n):
 
 
 if __name__ == '__main__':
-    trace_export_4_mat(getpath('tracepath') + 'sim_simple', getpath('data4origin') + 'sim_simple_posterior.mat', 3)
+    # trace_export_4_mat(getpath('tracepath') + 'sim_simple', getpath('data4origin') + 'sim_simple_posterior.mat', 3)
+    trace_export_4_mat(getpath('tracepath') + 'bd9_3', getpath('data4origin') + 'bd9_3_up_posterior.mat', 2)
+

### 2020-11-16 code/main.py

@@ -9,15 +9,16 @@ from proc.gnss_handler import bayes_multiple_detector
 
 if __name__ == '__main__':
     df = loadsol('rover_bd9_3_enu.pos')
-    t = df.loc[:, 'tow']-df.loc[0, 'tow']
+    t = df.loc[:, 'tow'] - df.loc[0, 'tow']
+    scala = 1000
     plt.subplot(3, 1, 1)
-    plt.plot(t, df.loc[:, 'north'])
+    plt.plot(t, df.loc[:, 'north'] * scala)
     plt.subplot(3, 1, 2)
-    plt.plot(t, df.loc[:, 'east'])
+    plt.plot(t, df.loc[:, 'east'] * scala)
     plt.subplot(3, 1, 3)
-    plt.plot(t, df.loc[:, 'up'])
+    plt.plot(t, df.loc[:, 'up'] * scala)
     plt.show()
-    bayes_multiple_detector(t, df.loc[:, 'up'], 2)
+    bayes_multiple_detector(t, df.loc[:, 'up'] * scala, 2)
     #
     # trace = az.from_netcdf(getpath('tracepath') + 'test')
     # az.plot_trace(trace)

### 2020-11-16 code/proc/gnss_handler.py

@@ -5,19 +5,22 @@ import numpy as np
 import pymc3 as pm
 from pymc3 import save_trace
 from theano import tensor as T
+import scipy.io as io
 
 from config.configutil import getpath
+from ioext.gnss_sol_handler import loadsol
 
 
 def bayes_multiple_detector(t, s, n):
+    scala = 1000
     with pm.Model() as abrupt_model:
-        sigma = pm.Normal('sigma', mu=0.03, sigma=0.015)
+        sigma = pm.Normal('sigma', mu=0.02 * scala, sigma=0.015 * scala)
         # sigma = pm.Uniform('sigma', 5, 15)
-        mu = pm.Uniform("mu1", -1.5, -1.4)
+        mu = pm.Uniform("mu1", -1.5 * scala, -1.4 * scala)
         tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
 
         for i in np.arange(2, n + 2):
-            _mu = pm.Uniform("mu" + str(i),-1.5, -1.4)
+            _mu = pm.Uniform("mu" + str(i), -1.6 * scala, -1.4 * scala)
             mu = T.switch(tau >= t, mu, _mu)
             if (i < (n + 1)):
                 tau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
@@ -25,9 +28,33 @@ def bayes_multiple_detector(t, s, n):
 
     with abrupt_model:
         pm.find_MAP()
-        trace = pm.sample(5000)
+        trace = pm.sample(40000, tune=10000)
         az.plot_trace(trace)
-        az.to_netcdf(trace, getpath('tracepath')+'test')
+        az.to_netcdf(trace, getpath('tracepath') + 'bd9_4')
         plt.show()
         pm.summary(trace)
     return trace
+
+
+if __name__ == '__main__':
+    df = loadsol('rover_bd9_4_enu.pos')
+    t = df.loc[:, 'tow'] - df.loc[0, 'tow']
+    t = t.to_numpy()
+    scala = 1000
+    plt.subplot(3, 1, 1)
+    plt.plot(t, df.loc[:, 'north'] * scala)
+    plt.subplot(3, 1, 2)
+    plt.plot(t, df.loc[:, 'east'] * scala)
+    plt.subplot(3, 1, 3)
+    plt.plot(t, df.loc[:, 'up'] * scala)
+    plt.show()
+    s = df.loc[650:, 'up'].to_numpy() * scala
[…]

### 2020-11-17 paper/manuscript.tex
add results

@@
 %传统位移探测的弊端
-%位移探测的短板
+%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
 %随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
-In \cite{GUMUS2019131}, a displacement monitoring system was designed to evaluate Network Real Time Kinematic(NRTK) for displacement detection.
+In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\citep{wang2011gps}.The results showed that NRTK has advantages in accuracy and robustness.
+A displacement monitoring system was designed to evaluate NRTK for displacement detection\citep{GUMUS2019131}.
 The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
+In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection using PPP has been studied.
 
+\cite{gili2000using} was one of the first landslide monitoring studies using GNSS displacement detection technology, in which traditional measurement data are used as a comparison.
+The results showed that the accuracy of GPS measurement was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
 A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\citep{rs12203375}.
 The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement is obtained by the direct difference between the coordinates of the start and end periods.
-
 In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\citep{atanasova2018ground,fuhrmann2015estimation}.
@@
 \section{Experiments and Results}
-To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation experiments and field experiments.
+To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation and field experiments.
 In the simulation experiment, the data affected by different noises are simulated.
@@
 \subsection{Simulation experiment}
-\begin{figure}[H]
+In the experiment, we only simulate the position measurement.
+In this simulation data, Gaussian white noise with mean 0 mm and standard deviation 30 mm is added.
+At 1000 s, 2500 s, and 3200 s, the displacements of -50 mm, -50 mm, and 100 mm are added, respectively.
+The simulation results are shown in Fig.
+\ref{fig_v_sim_simple_gauss_ts}.
+
+\begin{figure}[htbp]
 	\centering
 	\includegraphics[width=10 cm]{v_sim_simple_gauss_ts}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\caption{Simulation data with multiple displacement change points.}
 	\label{fig_v_sim_simple_gauss_ts}
 \end{figure} 
+As shown in Fig.
+\ref{fig_v_sim_simple_gauss_ts}, the whole time series is divided into four segments by three displacement change points.
+Using the model designed above, Bayesian inference is realized by MCMC sampling.
+The histogram of posterior estimation of displacement change points is shown in Fig.
+\ref{fig_v_tau_sim_simple}.
 
-\begin{figure}[H]
+\begin{figure}[htbp]
 	\centering
 	\includegraphics[width=10 cm]{v_tau_sim_simple}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\caption{Histogram of posterior estimation of displacement change points in the simulation experiment.}
 	\label{fig_v_tau_sim_simple}
 \end{figure} 
+As can be seen from Fig.
+\ref{fig_v_tau_sim_simple}, all the designed displacement change points are identified.
+$\tau_3$ is the easiest to be identified, mainly due to the largest displacement amplitude.
+Due to the small displacement amplitude and fewer sample points for Bayesian estimation on the right, the estimation accuracy at $\tau_2$ is worse than the other two points.
 
-\begin{figure}[H]
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_mu_sim_simple}
+	\caption{Histogram of posterior estimation of the mean in the simulation experiment.}
+	\label{fig_v_mu_sim_simple}
+\end{figure}
+
+\begin{figure}[htbp]
 	\centering
 	\includegraphics[width=10 cm]{v_sigma_sim_simple}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\caption{Histogram of posterior estimation of the measurement noise in the simulation experiment.}
 	\label{fig_v_sigma_sim_simple}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=10 cm]{v_mu_sim_simple}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
-	\label{fig_v_mu_sim_simple}
 \end{figure}
@@
 
-\begin{figure}[H]
+\begin{figure}[htbp]
 	\centering
@@
 \end{figure} 
-\begin{figure}[H]
+\begin{figure}[htbp]
 	\centering
@@
 \end{table*}
-\begin{figure}[H]
+\begin{figure}[htbp]
 	\centering

### 2020-11-17 paper/manuscript.tex
add exp

@@
 Due to the small displacement amplitude and fewer sample points for Bayesian estimation on the right, the estimation accuracy at $\tau_2$ is worse than the other two points.
+The histogram of the posterior estimation of the mean is shown in Fig.
+\ref{fig_v_mu_sim_simple}.
 
@@
 \end{figure} 
+The blue curve in Fig.
+\ref{fig_v_mu_sim_simple} is the fitting result of the histogram.
+It can be seen that although we assume that the prior distribution of the mean in the model obeys a uniform distribution, the posterior estimate of the mean approximately obeys normal distribution.
+The vertical green dashed line in Fig.
+\ref{fig_v_mu_sim_simple} represents the mean value of \textbf{$\mu$} posterior samples, and the mean values of the four segments are 1.17 mm, -49.58 mm, -98.9 mm, and -3.65 mm.
+Among these means, $\mu_2$ has the highest estimation accuracy, and its corresponding posterior sample coverage is the narrowest.
+The estimation accuracy of $\mu_4$ is the lowest, and the corresponding posterior sample coverage is the widest.
+These are mainly due to the fact that the most observation samples are used for $\mu_2$ estimation, while the least observation samples are used for $\mu_4$ estimation.
+As shown in Fig.
+\ref{fig_v_sigma_sim_simple}, the standard deviation of the observations is also accurately estimated.
 
@@
 	\includegraphics[width=10 cm]{v_sigma_sim_simple}
-	\caption{Histogram of posterior estimation of the measurement noise in the simulation experiment.}
+	\caption{Histogram of posterior estimation of the observation noise in the simulation experiment.}
 	\label{fig_v_sigma_sim_simple}
@@
 In the experiment, the equipment deployment is shown in Fig.
-\ref{fig_field_exp_config}.
+\ref{fig_v_field_exp_config}.
 A hard plank is pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank.
@@
 
-\begin{table*}[h!t]
+The GNSS observation data collected above are processed by the open-source software RTKLIB\citep{takasu2011rtklib}.
+In this data processing, GNSS data were processed epoch by epoch using RTK mode.
+The coordinate output of the positioning mode is the only input of the proposed method.
+In the experiment, only the vertical displacement is triggered, so only the up-coordinate component is displayed.
+The results of RTK positioning are shown in Fig.
+\ref{fig_v_bd9_3_up_tau}.
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_field_exp_config}
+	\caption{Filed experiment configuration. (a) Overview; (b) Working platform; (c) Displacement control platform; (d) Displacement measurement by tape. }
+	\label{fig_v_field_exp_config}
+\end{figure} 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_3_up_ts}
+	\caption{The vertical component of coordinates obtained by RTK positioning in field experiment 1.}
+	\label{fig_v_bd9_3_up_ts}
+\end{figure}
+
+For such a short baseline, most of the errors can be eliminated by the double-difference observation.
+As can be seen from Fig.
+\ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as multipath that have not been eliminated.
+The RTK positioning results are processed by the proposed model, and Bayesian inference is realized by MCMC sampling.
+The histogram of posterior estimation of displacement change points is shown in Fig.
+\ref{fig_v_bd9_3_up_tau}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_3_up_tau}
+	\caption{Histogram of posterior estimation of displacement change points in field experiment 1.}
+	\label{fig_v_bd9_3_up_tau}
+\end{figure} 
+From the posterior sample distribution of $\tau_2$ in Fig.
+\ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s.
+The change point determined according to the maximum value of the posterior sample histogram of $\tau_1$ is 781 s.It can be seen from Fig.
+\ref{fig_v_bd9_3_up_tau} that there are two peaks in the posterior sample histogram of change point $\tau_1$, and the posterior distribution is not as obvious as in the simulation experiment.The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object.
+In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\citep{teunissen2017springer}.
+The posterior sample histogram of the mean value of each segment divided by the change point and the displacement measured by the tape are shown in Fig.
+\ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height}, respectively.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_3_up_mu}
+	\caption{Histogram of posterior estimation of the mean in field experiment 1.}
+	\label{fig_v_bd9_3_up_mu}
+\end{figure} 
+\begin{table*}[htbp]
 	\centering
@@
 	\begin{threeparttable}
-		\caption{Measured height before and after each movement of the object hanging on the plank, unit (mm).}
+		\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
 		\label{tab_measured_height}
@@
 			& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
-			& & $\Delta h$ & 30.0& 29.8& 29.4& 29.2& 29.9&29.66\\
+			& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
 			\hline
@@
 			& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
-			& & $\Delta h$ &27.5& 27.2& 27.1& 27.0& 27.1& 27.18\\
+			& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
 			\bottomrule
@@
 \end{table*}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=10 cm]{v_bd9_3_up_ts}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
-	\label{fig_v_bd9_3_up_ts}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=10 cm]{v_bd9_3_up_tau}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
-	\label{fig_v_bd9_3_up_tau}
-\end{figure}
+The $\mu_0$, $\mu_1$, and $\mu_2$ obtained by the mean of the posterior samples are -1446.03 mm, -1474.11 mm, and -1489.83 mm, respectively, and the two displacements obtained by the difference of these mean values are -28.08 mm, -15.72 mm, respectively.
+The two displacements measured by tape are -29.66 mm and -27.18 mm respectively.
+To our surprise, the displacement difference between the two methods at the two change points is 1.58 mm and 11.46 mm, respectively.
+The main reason is that the displacement control equipment is not completely controllable.
 
@@
 	\includegraphics[width=10 cm]{v_bd9_3_up_sigma}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\caption{Histogram of posterior estimation of the observation noise in field experiment 1.}
 	\label{fig_v_bd9_3_up_sigma}
-\end{figure} 
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=10 cm]{v_bd9_3_up_mu}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
-	\label{fig_v_bd9_3_up_mu}
 \end{figure}
@@
 \section*{Author Contributions}
-Conceptualization: Nan Shen, Liang Chen; Methodology: Nan Shen; Writing - original draft preparation: Nan Shen; Writing - review and editing:Ruizhi Chen; Supervision: Liang Chen.
+Conceptualization: Nan Shen, Liang Chen; Methodology: Nan Shen, Liang Chen; Writing - original draft preparation: Nan Shen; Writing - review and editing: Liang Chen, Ruizhi Chen; Supervision: Liang Chen.
  \section*{Data Availability}

### 2020-11-17 paper/manuscript.tex
add result sigma

@@
 To our surprise, the displacement difference between the two methods at the two change points is 1.58 mm and 11.46 mm, respectively.
-The main reason is that the displacement control equipment is not completely controllable.
+The main reason is that the displacement control device is not fully controllable.
+It can be seen from Fig.
+\ref{fig_v_bd9_3_up_ts} that before the second displacement change, the plank appears obvious floating when measuring with the tape.
+As shown in Fig.
+\ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
 
@@
 	\begin{threeparttable}
-		\caption{Measured height before and after each movement of the object hanging on the plank, unit (m).}
+		\caption{Measured height before and after each movement of the object hanging on the plank, unit (mm).}
 		\label{tab_measured_height}

### 2020-11-18 code/ioext/trace_io_handler.py
add field exp2 figs

@@ -19,5 +19,5 @@ def trace_export_4_mat(srcname, destname, n):
 
 if __name__ == '__main__':
     # trace_export_4_mat(getpath('tracepath') + 'sim_simple', getpath('data4origin') + 'sim_simple_posterior.mat', 3)
-    trace_export_4_mat(getpath('tracepath') + 'bd9_3', getpath('data4origin') + 'bd9_3_up_posterior.mat', 2)
+    trace_export_4_mat(getpath('tracepath') + 'bd9_4', getpath('data4origin') + 'bd9_4_up_posterior.mat', 2)
 

### 2020-11-18 code/view/trace_view_handler.py

@@ -10,4 +10,4 @@ def trace_plot(name):
     plt.show()
 
 if __name__ == '__main__':
-    trace_plot(getpath('tracepath')+'sim_simple')
+    trace_plot(getpath('tracepath')+'bd9_4')

### 2020-11-19 paper/manuscript.tex
add field exp2 figs
add field2 results

@@
 As shown in subgraphs (c) and (d), the height of the antenna is measured with a tape before and after each movement of the object hanging on the plank.
+Five readings are taken for each measurement to ensure data reliability.
 Besides, markers are made on the ground and on the antenna respectively to ensure that the same position is referenced for each measurement.
 The sampling frequency of the GNSS receiver is set to 1 Hz.
-The whole experiment lasted for nearly one hour, during which the object hanging on the plank was moved several times manually.
-
+We did two experiments, each lasting nearly 45 minutes.
+In the experiment, the objects hanging on the board were manually moved several times.
+The displacement amplitude of the second experiment is smaller than that of the first experiment.
 The GNSS observation data collected above are processed by the open-source software RTKLIB\citep{takasu2011rtklib}. 
-In this data processing, GNSS data were processed epoch by epoch using RTK mode.
-The coordinate output of the positioning mode is the only input of the proposed method.
-In the experiment, only the vertical displacement is triggered, so only the up-coordinate component is displayed.
-The results of RTK positioning are shown in Fig.
-\ref{fig_v_bd9_3_up_tau}.
 \begin{figure}[htbp]
@@
 \end{figure}
+
+\subsubsection{Field experiment 1}
+In this data processing, GNSS data were processed epoch by epoch using RTK mode.
+The coordinate output of the positioning mode is the only input of the proposed method.
+In the experiment, only the vertical displacement is triggered, so only the up-coordinate component is displayed.
+The results of RTK positioning are shown in Fig.
+\ref{fig_v_bd9_3_up_tau}.
 \begin{figure}[htbp]
@@
 \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as multipath that have not been eliminated.
-The RTK positioning results are processed by the proposed model, and Bayesian inference is realized by MCMC sampling.
+The RTK positioning results are processed by the proposed model, and Bayesian inference is implemented by MCMC sampling.
 The histogram of posterior estimation of displacement change points is shown in Fig.
@@
 
+\subsubsection{Field experiment 2}
+This experiment is similar to the previous one except that the displacement amplitude is smaller than that of the last one.
+For the data collected in this experiment,  the coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experimrnt, and the up component of the time series is shown in Fig.
+\ref{fig_v_bd9_4_up_ts}.
+In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_4_up_ts}
+	\caption{The vertical component of coordinates obtained by RTK positioning in field experiment 2.}
+	\label{fig_v_bd9_4_up_ts}
+\end{figure} 
 \begin{table*}[h!t]
@@
 	\begin{threeparttable}
-		\caption{Measured height before and after each movement of the object hanging on the plank, unit (mm).}
+		\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 2, unit (mm).}
 		\label{tab_measured_height}
@@
 			\multirow{3}*{Step 1}
-			& & ${h_0}$    &368.5&	368.9&	369.0&	368.9&	369.0&	368.9\\
-			& & ${h_1}$    &348.1&	348.0&	348.0&	348.2&	348.3&	348.1\\
-			& & $\Delta h$ & 20.4&	 20.9&	 21.0&	 20.7&	 20.7&	 20.7\\
+			& & ${h_0}$    &347.5&	347.3&	347.6&	347.5&	347.4&	347.5\\
+			& & ${h_1}$    &326.1&	326.3&	326.1&	326.0&	326.1&	326.1\\
+			& & $\Delta h$ &-21.4&	-21.0&	-21.5&	-21.5&	-21.3&	-21.3\\
 			\hline               
 			\multirow{3}*{Step 2}
-			& & ${h_0}$    &347.5&	347.3&	347.6&	347.5&	347.4&	347.5\\
-			& & ${h_1}$    &326.1&	326.3&	326.1&	326.0&	326.1&	326.1\\
-			& & $\Delta h$ & 21.4&	 21.0&	 21.5&	 21.5&	 21.3&	 21.3\\
-			\hline               
-			\multirow{3}*{Step 3}
-			& & ${h_0}$    &325.0&	325.1&	324.9&	325.0&	325.2&	325.0\\
+			& & ${h_
+				0}$    &325.0&	325.1&	324.9&	325.0&	325.2&	325.0\\
 			& & ${h_1}$    &305.5&	305.3&	305.4&	305.5&	305.6&	305.5\\
-			& & $\Delta h$ & 19.5&	 19.8&	 19.5&	 19.5&	 19.6&	 19.6\\
+			& & $\Delta h$ &-19.5&	-19.8&	-19.5&	-19.5&	-19.6&	-19.6\\
 			\bottomrule
@@
 \end{table*}
+As can be seen from Fig.
+\ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height}, the amplitude of the two displacements is smaller than that of the previous experiment.
+The time series are processed by the proposed model, and Bayesian inference is implemented by MCMC sampling.
+The results are shown in Fig.
+\ref{fig_v_bd9_4_up_tau}, \ref{fig_v_bd9_4_up_mu}, and \ref{fig_v_bd9_4_up_sigma}.
+
 \begin{figure}[htbp]
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_4_up_ts}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
-	\label{fig_v_bd9_4_up_ts}
+	\includegraphics[width=10 cm]{v_bd9_4_up_tau}
+	\caption{Histogram of posterior estimation of displacement change points in field experiment 2.}
+	\label{fig_v_bd9_4_up_tau}
 \end{figure} 
-
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_4_up_mu}
+	\caption{Histogram of posterior estimation of the mean in field experiment 2.}
+	\label{fig_v_bd9_4_up_mu}
+\end{figure} 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_4_up_sigma}
+	\caption{Histogram of posterior estimation of the observation noise in field experiment 2.}
+	\label{fig_v_bd9_4_up_sigma}
+\end{figure}
+Due to the decrease of displacement amplitude, the results are not as good as the previous experimental results. 
+It can be seen from Fig.
+\ref{fig_v_bd9_4_up_tau} that there are two peaks in the posterior sample histogram of $\tau_1$.
+Unlike Fig.
+\ref{fig_v_bd9_3_up_tau} of the previous experimental results, the two peaks are far away from each other, exceeding 500 s.
+Accordingly, there are two peaks in the posterior sample distribution of $\mu_0$, $\mu_1$ and $\sigma$.
+In addition, we found that the second peak of $\tau_1$ is very close to the peak of $\tau_2$, which is not what we want because we do not want to get very short segments.
+In the next section, we will discuss adding these additional priors to the model to improve the performance of Bayesian inference.
 \section{Discussion}

### 2020-11-19 code/proc/gnss_handler_each_sigma.py

@@ -1,0 +1,74 @@
+# coding:utf-8
+import arviz as az
+import matplotlib.pyplot as plt
+import numpy as np
+import pymc3 as pm
+from pymc3 import save_trace
+from theano import tensor as T
+import scipy.io as io
+
+from config.configutil import getpath
+from ioext.gnss_sol_handler import loadsol
+
+
+def bayes_multiple_detector_each_sigma(t, s, n):
+    scala = 1000
+    with pm.Model() as abrupt_model:
+        sigma = pm.Normal('sigma1', mu=0.02 * scala, sigma=0.015 * scala)
+        # sigma = pm.Uniform('sigma', 5, 15)
+        mu = pm.Uniform("mu1", -1.5 * scala, -1.4 * scala)
+        tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
+
+        for i in np.arange(2, n + 2):
+            _mu = pm.Uniform("mu" + str(i), -1.6 * scala, -1.4 * scala)
+            mu = T.switch(tau >= t, mu, _mu)
+            # _sigma = pm.Normal('sigma' + str(i), mu=0.02 * scala, sigma=0.015 * scala)
+            # sigma = T.switch(tau >= t, sigma, _sigma)
+            if i < (n + 1):
+                # BoundedUniform = pm.Bound(pm.Uniform, lower=700)
+                # dtau = BoundedUniform('dtau'+str(i), upper=t.max()-tau)
+                ttau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
+
+                tau = ttau
+
+        # add bound
+        tau1 = abrupt_model["tau1"]
+        tau2 = abrupt_model["tau2"]
+        dtau = pm.DiscreteUniform('dtau', tau1 + 500, tau2)
+        # BoundedUniform = pm.Bound(pm.HalfNormal, lower=300)
+        # dtau = BoundedUniform('dtau', mu=(tau2-tau1)/2, sigma=30)
+        # dtau = pm.Pareto("dtau", alpha=1, m=tau2 - tau1)
+        # dtau = pm.Pareto("dtau", alpha=1.0/(tau2 - tau1), m=500)
+        # d = tau2 - tau1
+        # dv = T.switch(d < 700, 0, dtau)
+
+        s_obs = pm.Normal("s_obs", mu=mu, sigma=sigma, observed=s)
[…]

### 2020-11-19 paper/manuscript.tex
add introduction

@@
 GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results.
-Previous studies on displacement detection based on GNSS pay more attention to how to improve the positioning accuracy.
-The research on how to identify and extract displacement from the coordinate sequence obtained by GNSS is limited.
+There are many researches on displacement detection based on GNSS, which can be divided into two categories.
 
@@
 %随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
+The first category is about the research of measurement technology in GNSS-based displacement detection.
 In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\citep{wang2011gps}.The results showed that NRTK has advantages in accuracy and robustness.
@@
 In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection using PPP has been studied.
+There are also some studies using the time-differenced carrier phases (TDCP) technique\citep{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection.
+This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
+This kind of method mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.
 
+In another category of GNSS-based displacement detection research, GNSS is only used as a long-term monitoring method.
 \cite{gili2000using} was one of the first landslide monitoring studies using GNSS displacement detection technology, in which traditional measurement data are used as a comparison.
@@
 In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\citep{atanasova2018ground,fuhrmann2015estimation}.
+In these studies, the GNSS static positioning mode is usually adopted.
+
+%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。
+At present, there are few studies on displacement identification and extraction of GNSS kinematic positioning time series.
+In \cite{li2010deformation}, a multiple Kalman filters model was proposed for deformation detection in the GPS real-time series.
+Different filters in the model represent different displacement models, which need to be defined in advance.
+In addition, epoch by epoch displacement detection is easily affected by observation noise.
+A modified real-time Chow test approach was proposed for fast deformation monitoring\citep{bellone2016real}.
+This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\citep{pirotti2015micro}.
 

### 2020-11-19 code/proc/gnss_handler_add_new_rule.py

@@ -14,7 +14,7 @@ from ioext.gnss_sol_handler import loadsol
 def bayes_multiple_detector_each_sigma(t, s, n):
     scala = 1000
     with pm.Model() as abrupt_model:
-        sigma = pm.Normal('sigma1', mu=0.02 * scala, sigma=0.015 * scala)
+        sigma = pm.Normal('sigma', mu=0.02 * scala, sigma=0.015 * scala)
         # sigma = pm.Uniform('sigma', 5, 15)
         mu = pm.Uniform("mu1", -1.5 * scala, -1.4 * scala)
         tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
@@ -22,34 +22,22 @@ def bayes_multiple_detector_each_sigma(t, s, n):
         for i in np.arange(2, n + 2):
             _mu = pm.Uniform("mu" + str(i), -1.6 * scala, -1.4 * scala)
             mu = T.switch(tau >= t, mu, _mu)
-            # _sigma = pm.Normal('sigma' + str(i), mu=0.02 * scala, sigma=0.015 * scala)
-            # sigma = T.switch(tau >= t, sigma, _sigma)
             if i < (n + 1):
-                # BoundedUniform = pm.Bound(pm.Uniform, lower=700)
-                # dtau = BoundedUniform('dtau'+str(i), upper=t.max()-tau)
                 ttau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
-
                 tau = ttau
 
-        # add bound
         tau1 = abrupt_model["tau1"]
         tau2 = abrupt_model["tau2"]
         dtau = pm.DiscreteUniform('dtau', tau1 + 500, tau2)
-        # BoundedUniform = pm.Bound(pm.HalfNormal, lower=300)
-        # dtau = BoundedUniform('dtau', mu=(tau2-tau1)/2, sigma=30)
-        # dtau = pm.Pareto("dtau", alpha=1, m=tau2 - tau1)
-        # dtau = pm.Pareto("dtau", alpha=1.0/(tau2 - tau1), m=500)
-        # d = tau2 - tau1
-        # dv = T.switch(d < 700, 0, dtau)
 
         s_obs = pm.Normal("s_obs", mu=mu, sigma=sigma, observed=s)
     g = pm.model_to_graphviz(abrupt_model)
     g.view()
     with abrupt_model:
-        pm.find_MAP()
+        # pm.find_MAP()
[…]

### 2020-11-19 paper/manuscript.tex
add methods

@@
 \cite{gili2000using} was one of the first landslide monitoring studies using GNSS displacement detection technology, in which traditional measurement data are used as a comparison.
-The results showed that the accuracy of GPS measurement was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
+The results showed that the accuracy of Global positioning system (GPS) measurement was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
 A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\citep{rs12203375}.
@@
 
-%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。
+%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
 At present, there are few studies on displacement identification and extraction of GNSS kinematic positioning time series.
@@
 This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\citep{pirotti2015micro}.
+Besides, \cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.
 
 %本文拟采取的措施弥补这些短板
-%目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
 %Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情
+Previous studies provide an important information for the application of displacement detection based on GNSS, but most of them focus on the detection of long term displacement.
+Few studies have explored the use of GNSS kinematic positioning for short-term displacement detection.
+Although the displacement can be obtained directly by the difference of GNSS positioning coordinates, the identification and extraction of displacement are still challenging due to the influence of measurement errors.
+At present, most of the displacement detection methods based on GNSS kinematic positioning are based on single epoch observations, which are easily affected by measurement noise and gross error.
 
 %引入本文的研究内容和贡献
+The primary aim of this paper is to explore using the context data of change point from GNSS kinematic positioning for displacement detection.
+This study utilized Bayesian inference to identify and extract displacement, and the Markov Chain Monte Carlo (MCMC) technique is adopted to implement the Bayesian inference.
+Simulation experiments and field experiments were carried out to verify the feasibility of the proposed method.
+The posterior sample distribution of parameters is used to analyze the reliability of displacement detection.
+The study presented here is one of the first investigations to utilize Bayesian inference for displacement detection based on GNSS kinematic positioning.
+The remaining part is as follows.
+Section \ref{method} shows the methodology used for this study, Section \ref{exp} presents the experimental results, the discussion is given in Section \ref{disc}, and finally, the conclusion is given in the last section.
 
@@
 \label{method}
+In this section, the Bayesian model of displacement detection and its implementation based on MCMC are presented first. Then the GNSS  real-time kinematic positioning model is introduced.
+\subsection{Bayesian Model for Displacement Detection}
 
-\subsection{Displacement Detection}
 The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$,  and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate displacements.
@@
 Bayesian inference deduces the posterior probability as the result of a priori probability and likelihood function.
-Bayesian inference calculates the posterior probability according to the Bayesian theorem
+Bayesian inference calculates the posterior probability according to the Bayesian theorem\citep{chen2009modulation,chen2013bayesian}
 
@@
 Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula \ref{eq_bayesian_prior}, \ref{eq_bayesian_prior_sigma}, \ref{eq_bayesian_prior_mu_sum}, \ref{eq_bayesian_prior_tau_5}.
+The graphical representation of the Bayesian model of displacement detection is shown in Fig.
+\ref{fig_v_simple_p_model}.
 \begin{figure}[H]
@@
 	\includegraphics[width=8 cm]{v_simple_p_model}
-	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
+	\caption{Bayesian model for displacement detection.}
 	\label{fig_v_simple_p_model}
 \end{figure} 
+As shown in Fig.
+\ref{fig_v_simple_p_model}, green represents the independent distribution, blue denotes the distribution dependent on other random variables, and red is the distribution of observations.
+After the Bayesian model of displacement detection is given, MCMC, one of the implementation methods of Bayesian inference, is introduced.
 
@@
 Two implementations of MCMC,  the Metropolis-Hasting sampler\citep{chib1995understanding} and the No-U-Turn sampler\citep{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively.
+Next, the data source of the proposed method: GNSS real-time kinematic positioning is introduced.
 
@@
 \section{Experiments and Results}
+\label{exp}
 To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation and field experiments.
@@
 \end{figure} 
-
 \subsection{Field experiment}
@@
 \section{Discussion}
+\label{disc}
 
 \section{Conclusions}
+\label{concl}
 

### 2020-11-19 code/ioext/trace_io_handler.py

@@ -10,6 +10,9 @@ def trace_export_4_mat(srcname, destname, n):
     data = {}
     size = trace.posterior.sigma.data.size
     data['sigma'] = trace.posterior.sigma.data.reshape(size, 1)
+    # data['dtau'] = trace.posterior.dtau.data.reshape(size, 1)
+
+
     for i in np.arange(1, n + 1):
         data['mu' + str(i)] = trace.posterior['mu' + str(i)].data.reshape(size, 1)
         data['tau' + str(i)] = trace.posterior['tau' + str(i)].data.reshape(size, 1)
@@ -19,5 +22,5 @@ def trace_export_4_mat(srcname, destname, n):
 
 if __name__ == '__main__':
     # trace_export_4_mat(getpath('tracepath') + 'sim_simple', getpath('data4origin') + 'sim_simple_posterior.mat', 3)
-    trace_export_4_mat(getpath('tracepath') + 'bd9_4', getpath('data4origin') + 'bd9_4_up_posterior.mat', 2)
+    trace_export_4_mat(getpath('tracepath') + 'bd9_4', getpath('data4origin') + 'bd9_4_up.mat', 2)
 

### 2020-11-19 code/proc/gnss_handler.py

@@ -28,7 +28,7 @@ def bayes_multiple_detector(t, s, n):
 
     with abrupt_model:
         pm.find_MAP()
-        trace = pm.sample(40000, tune=10000)
+        trace = pm.sample(20000, tune=5000)
         az.plot_trace(trace)
         az.to_netcdf(trace, getpath('tracepath') + 'bd9_4')
         plt.show()
@@ -54,7 +54,3 @@ if __name__ == '__main__':
     plt.show()
     io.savemat(getpath('data4origin') + 'bd9_4_up_raw.mat', {'t': t, 'x': s}, oned_as='column')
     bayes_multiple_detector(t, s, 2)
-    #
-    # trace = az.from_netcdf(getpath('tracepath') + 'test')
-    # az.plot_trace(trace)
-    # plt.show()

### 2020-11-19 code/view/trace_view_handler.py

@@ -10,4 +10,4 @@ def trace_plot(name):
     plt.show()
 
 if __name__ == '__main__':
-    trace_plot(getpath('tracepath')+'bd9_4')
+    trace_plot(getpath('tracepath')+'bd9_4_each_sigma')

### 2020-11-20 code/ioext/trace_io_handler.py
add new rule fig arc

@@ -10,7 +10,7 @@ def trace_export_4_mat(srcname, destname, n):
     data = {}
     size = trace.posterior.sigma.data.size
     data['sigma'] = trace.posterior.sigma.data.reshape(size, 1)
-    # data['dtau'] = trace.posterior.dtau.data.reshape(size, 1)
+    data['dtau'] = trace.posterior.dtau.data.reshape(size, 1)
 
 
     for i in np.arange(1, n + 1):
@@ -22,5 +22,5 @@ def trace_export_4_mat(srcname, destname, n):
 
 if __name__ == '__main__':
     # trace_export_4_mat(getpath('tracepath') + 'sim_simple', getpath('data4origin') + 'sim_simple_posterior.mat', 3)
-    trace_export_4_mat(getpath('tracepath') + 'bd9_4', getpath('data4origin') + 'bd9_4_up.mat', 2)
+    trace_export_4_mat(getpath('tracepath') + 'bd9_4_add_new_rule_1', getpath('data4origin') + 'bd9_4_up_posterior_add_new_rule_.mat', 2)
 

### 2020-11-20 paper/manuscript.tex
add dis figs

@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=8 cm]{v_simple_p_model_add_new_rule}
+	\caption{Bayesian model for displacement detection with an additional prior.}
+	\label{fig_v_simple_p_model_add_new_rule}
+\end{figure} 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_4_up_tau_add_new_rule}
+	\caption{Histogram of posterior estimation of displacement change points in field experiment 2 with an additional prior.}
+	\label{fig_v_bd9_4_up_tau_add_new_rule}
+\end{figure} 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_4_up_mu_add_new_rule}
+	\caption{Histogram of posterior estimation of the mean in field experiment 2 with an additional prior.}
+	\label{fig_v_bd9_4_up_mu_add_new_rule}
+\end{figure} 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_4_up_sigma_add_new_rule}
+	\caption{Histogram of posterior estimation of the observation noise in field experiment 2 with an additional prior.}
+	\label{fig_v_bd9_4_up_sigma_add_new_rule}
+\end{figure}
+
 \section{Conclusions}

### 2020-11-20 paper/manuscript.tex
add disc intro

@@
 In addition, we found that the second peak of $\tau_1$ is very close to the peak of $\tau_2$, which is not what we want because we do not want to get very short segments.
-In the next section, we will discuss adding these additional priors to the model to improve the performance of Bayesian inference.
+In the next section, we will discuss adding an additional prior to the model to improve the performance of Bayesian inference.
 \section{Discussion}
 \label{disc}
+In the above experiment, due to the influence of observation noise, there are several significant peaks of posterior samples, and the posterior distribution of change points is close to each other.
+The interval between adjacent change points is constrained by adding an additional prior.
+The random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.
+\begin{equation}\label{eq_bayesian_prior_d_tau}
+P(d\tau_{i})=DiscreteU(\tau_{i} + d,\tau_{i+1})
+\end{equation}
+where $d$ is the shortest time interval to be restricted. The new Bayesian probability model with additional prior is shown in Fig. \ref{fig_v_simple_p_model_add_new_rule}.
 

### 2020-11-21 paper/manuscript.tex
add discussion

@@
 \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s.
-The change point determined according to the maximum value of the posterior sample histogram of $\tau_1$ is 781 s.It can be seen from Fig.
-\ref{fig_v_bd9_3_up_tau} that there are two peaks in the posterior sample histogram of change point $\tau_1$, and the posterior distribution is not as obvious as in the simulation experiment.The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object.
+The change point determined according to the maximum value of the posterior sample histogram of $\tau_1$ is 781 s.
+However, as can be seen from Fig.
+\ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample histogram of change point $\tau_1$, and the posterior distribution is not as obvious as in the simulation experiment.
+The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
 In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\citep{teunissen2017springer}. 
@@
 \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
+%我们发现此处变点后验样本中的两个峰值对于均值和标准差中没有出现。
+%主要原因是变点的峰值距离很近，对于划分的段没有很明显的影响，因此对后验均值和标准差的浮动没有很大影响。
+%而在现实中，这种情况是会发生的，例如滑坡或者沉降，整个位移变化过程需要一定的时间，存在多个变化点。
+%然而，我们可能更加关注主要变化点，后面通过加入额外先验来提升主要变化点的识别，弱化次要变化点。
 
@@
 \end{figure} 
+The two peaks in the posterior sample of the change point do not appear in $\mu$ and $\sigma$. 
+The main reason is that the peak interval of change points is very close, which has no obvious influence on the segments divided, so it has little influence on the posterior mean and standard deviation.
+In reality, this kind of situation exists, for example, in the process of landslide or subsidence, multiple displacements occur in a short time, so there are multiple change points. 
+However, people pay more attention to the main change points.
+By adding additional priors to improve the identification of major change points, weakening secondary change points will be discussed later.
 
@@
 \label{disc}
-In the above experiment, due to the influence of observation noise, there are several significant peaks of posterior samples, and the posterior distribution of change points is close to each other.
+In field experiment 1, there are two significant peaks in the posterior sample distribution at the same change point.
+In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
 The interval between adjacent change points is constrained by adding an additional prior. 
 The random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.
+
 \begin{equation}\label{eq_bayesian_prior_d_tau}
@@
 \end{figure} 
+As shown in Formula \ref{eq_bayesian_prior_d_tau} and Fig.
+\ref{fig_v_simple_p_model_add_new_rule}, the distribution of newly added random variables depends on the change points and the constrained interval.
+In the following data processing, the interval $d$ is set to 300.
+The data in field experiment 1 is reprocessed with the new Bayesian model, and the posterior distribution of displacement change points is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=10 cm]{v_bd9_3_up_tau_add_new_rule}
+	\caption{Histogram of posterior estimation of displacement change points in field experiment 2 with an additional prior.}
+	\label{fig_v_bd9_3_up_tau_add_new_rule}
+\end{figure}
+
+%从图16和图14的对比中可以看出，图14中t1次峰值得到了有效抑制，更加有利于主要变化点的识别。
+%此外，t2以及均值和方差的的后验分布没有明显变化。
+From the comparison between Fig.
+\ref{fig_v_bd9_3_up_tau_add_new_rule} and Fig.
+\ref{fig_v_bd9_3_up_tau}, it can be seen that the secondary peak of $\tau_1$ posterior distribution in Fig.
+\ref{fig_v_bd9_3_up_tau} is effectively suppressed, which is more conducive to the identification of the primary change point.
+There is no significant change in the posterior distribution of $\tau_2$, $\mu$, and  $\sigma$.
+The data in field experiment 2 is also reprocessed with the new Bayesian model, and the results are shown in Figs.
+\ref{fig_v_bd9_4_up_tau_add_new_rule}, \ref{fig_v_bd9_4_up_mu_add_new_rule}, and \ref{fig_v_bd9_4_up_sigma_add_new_rule}.
+
 \begin{figure}[htbp]
@@
 	\includegraphics[width=10 cm]{v_bd9_4_up_tau_add_new_rule}
-	\caption{Histogram of posterior estimation of displacement change points in field experiment 2 with an additional prior.}
+	\caption{Histogram of posterior estimation of displacement change points in field experiment 1 with an additional prior.}
 	\label{fig_v_bd9_4_up_tau_add_new_rule}
@@
 \end{figure}
+%与图12中变化点t1后验样本相比，图17所示中后验样本分布更加有利于变化点的识别。
+%尽管在1200秒附近还存在一些样本点，但几乎微乎其微，基本都在100以下。
+%t2的后验分布出现了些许变化，在1750s出现了少许样本点，不足以影响变化点的识别。
+%从图13和图18的对比中，可以看出均值后验分布的次峰基本消失。
+%但是依然存在，为了减小这些样本点的影响，采用样本的中位数作为均值的最终估值，得到的均值分别为1,2,3.
+%利用这些均值计算的位移分别为4,5.
+%而表格2中测量得到的位移分别为7,8.
+%主要是由于。。引起，从图2中可以看出存在明显浮动。
+
+%同理，从图19和图14的对比中，可以看出方差估值的次峰得到了显著削弱。
+
+%从以上的讨论中，可以看出添加的先验能够有效的提升辩护点的可识别性。
+%另一方面也说明，本文提出的基于贝叶斯推理方法足够灵活，可以根据需求添加先验的方式满足不同的分析需求。
 
@@
 \label{concl}
+This study set out to develop a Bayesian model for displacement identification and extraction. 
+The second aim of this study was to investigate the effects of various parameters and models on the performance of the proposed algorithm. 
+State models and measurement models under different state parameters are designed for the IMM-KF algorithm, and the verification schemes based on vision and segmental integration are proposed.
+Four sets of experiments were carried out to verify the effectiveness of the designed algorithm. 
+These experiments confirmed the effectiveness of the algorithm in displacement extraction and vibration detection.
+
+For obvious vibration, the IMM Kalman filter based on the CP + DV model set can be effectively performed for online displacement extraction and vibration detection.
+The CV, CA, and CJ models are not conducive to displacement extraction due to the displacement drift, although this drift can be suppressed by the virtual measurement model.
+For slight vibration, the performance of the IMM Kalman filter with CP + DV model set is poor.
+But the performance of the IMM-SIS with the CP+CA model set is good.
+These findings have significant implications for the understanding of how to carry out online displacement extraction and vibration detection.
+This study provides the first comprehensive assessment of interactive multiple models for displacement extraction and vibration detection in SHM.
 

### 2020-11-21 code/proc/gnss_handler_9_3_add_new_rule.py

@@ -1,0 +1,62 @@
+# coding:utf-8
+import arviz as az
+import matplotlib.pyplot as plt
+import numpy as np
+import pymc3 as pm
+from pymc3 import save_trace
+from theano import tensor as T
+import scipy.io as io
+
+from config.configutil import getpath
+from ioext.gnss_sol_handler import loadsol
+
+
+def bayes_multiple_detector_each_sigma(t, s, n):
+    scala = 1000
+    with pm.Model() as abrupt_model:
+        sigma = pm.Normal('sigma', mu=0.02 * scala, sigma=0.015 * scala)
+        # sigma = pm.Uniform('sigma', 5, 15)
+        mu = pm.Uniform("mu1", -1.5 * scala, -1.4 * scala)
+        tau = pm.DiscreteUniform("tau" + "1", t.min(), t.max())
+
+        for i in np.arange(2, n + 2):
+            _mu = pm.Uniform("mu" + str(i), -1.5 * scala, -1.4 * scala)
+            mu = T.switch(tau >= t, mu, _mu)
+            if i < (n + 1):
+                ttau = pm.DiscreteUniform("tau" + str(i), tau, t.max())
+                tau = ttau
+
+        tau1 = abrupt_model["tau1"]
+        tau2 = abrupt_model["tau2"]
+        dtau = pm.DiscreteUniform('dtau', tau1 + 500, tau2)
+
+        s_obs = pm.Normal("s_obs", mu=mu, sigma=sigma, observed=s)
+    g = pm.model_to_graphviz(abrupt_model)
+    g.view()
+    with abrupt_model:
+        # pm.find_MAP()
+        trace = pm.sample(20000, tune=5000)
+        az.plot_trace(trace)
+        az.to_netcdf(trace, getpath('tracepath') + 'bd9_3_add_new_rule')
+        plt.show()
+        pm.summary(trace)
+    return trace
+
+
+if __name__ == '__main__':
+    df = loadsol('rover_bd9_3_enu.pos')
+    t = df.loc[:, 'tow'] - df.loc[0, 'tow']
+    t = t.to_numpy()
+    scala = 1000
+    plt.subplot(3, 1, 1)
+    plt.plot(t, df.loc[:, 'north'] * scala)
+    plt.subplot(3, 1, 2)
+    plt.plot(t, df.loc[:, 'east'] * scala)
+    plt.subplot(3, 1, 3)
[…]

### 2020-11-21 paper/manuscript.tex
add discussion

@@
 %与图12中变化点t1后验样本相比，图17所示中后验样本分布更加有利于变化点的识别。
-%尽管在1200秒附近还存在一些样本点，但几乎微乎其微，基本都在100以下。
+%尽管在1200秒附近还存在一些样本点，但几乎微乎其微，基本都在1000以下。
 %t2的后验分布出现了些许变化，在1750s出现了少许样本点，不足以影响变化点的识别。
@@
 %主要是由于。。引起，从图2中可以看出存在明显浮动。
-
 %同理，从图19和图14的对比中，可以看出方差估值的次峰得到了显著削弱。
-
 %从以上的讨论中，可以看出添加的先验能够有效的提升辩护点的可识别性。
 %另一方面也说明，本文提出的基于贝叶斯推理方法足够灵活，可以根据需求添加先验的方式满足不同的分析需求。
+Compared with the posterior sample distribution of change point $\tau_1$ in Fig.
+\ref{fig_v_bd9_4_up_tau}, the posterior sample distribution in Fig.
+\ref{fig_v_bd9_4_up_tau_add_new_rule} is more conducive to the identification of the change point.
+Although there are still some sample points around 1200 seconds, most of them are below 1000, which has little effect.
+The posterior distribution of $\tau_2$ has slightly changed. A few sample points appear around 1750 s, but it is not enough to affect the identification of the change point.
+From the comparison between Fig. \ref{fig_v_bd9_4_up_mu} and Fig. \ref{fig_v_bd9_4_up_mu_add_new_rule}, it can be seen that the secondary peak of $\mu_1$ almost disappears.
+However, there are still some sample points which deviate from the main peak.
+In order to reduce the influence of these sampling points, the median value of the sample is used as the final estimation of \textbf{$\mu$}, and $\mu_0$, $\mu_1$ and $\mu_2$ are obtained as -1461.18 mm, -1482.37 mm and -1509.09 mm respectively.
+The two displacements obtained by these means are -21.19 mm and -26.72 mm, respectively, and the displacements measured in Table \ref{tab_measured_height} are -21.3 mm and -19.6 mm respectively.
+The displacement difference between the two methods at the two change points is 0.11 mm and 7.12 mm, respectively.
+The larger displacement error at $\tau_2$ is mainly due to the incompletely controllable experimental equipment.
+But on the whole, using the proposed method, the displacement extraction accuracy in the experiment can reach less than 2 mm.
+However, as mentioned in the simulation experiment, the accuracy of displacement extraction in practical application also depends on the number of available samples near the change point.
 

### 2020-11-21 code/ioext/trace_io_handler.py

@@ -22,5 +22,5 @@ def trace_export_4_mat(srcname, destname, n):
 
 if __name__ == '__main__':
     # trace_export_4_mat(getpath('tracepath') + 'sim_simple', getpath('data4origin') + 'sim_simple_posterior.mat', 3)
-    trace_export_4_mat(getpath('tracepath') + 'bd9_4_add_new_rule_1', getpath('data4origin') + 'bd9_4_up_posterior_add_new_rule_.mat', 2)
+    trace_export_4_mat(getpath('tracepath') + 'bd9_3_add_new_rule', getpath('data4origin') + 'bd9_3_up_posterior_add_new_rule_.mat', 2)
 

### 2020-11-21 paper/manuscript.tex
add Conclusions

@@
 However, as mentioned in the simulation experiment, the accuracy of displacement extraction in practical application also depends on the number of available samples near the change point.
+It can be seen from Fig. \ref{fig_v_bd9_4_up_sigma_add_new_rule} and Fig. \ref{fig_v_bd9_4_up_sigma} that the secondary peak of $\sigma$ posterior distribution has been significantly weakened.
+From the above discussion, we can see that the added prior can effectively improve the identifiability of change points.
+On the other hand, it also shows that the Bayesian inference-based displacement detection method proposed in this paper is flexible enough to meet different analysis needs by adding a priori.
 
@@
 \label{concl}
-This study set out to develop a Bayesian model for displacement identification and extraction. 
-The second aim of this study was to investigate the effects of various parameters and models on the performance of the proposed algorithm. 
-State models and measurement models under different state parameters are designed for the IMM-KF algorithm, and the verification schemes based on vision and segmental integration are proposed.
-Four sets of experiments were carried out to verify the effectiveness of the designed algorithm. 
-These experiments confirmed the effectiveness of the algorithm in displacement extraction and vibration detection.
+This study set out to develop a Bayesian model for displacement detection from GNSS kinematic positioning in a short time. 
+The definition of multiple displacements is given, and the Bayesian model for multiple displacement detection is proposed.
+The principle of Bayesian inference and its implementation based on MCMC sampling are presented.
+To provide epoch by epoch coordinate time series for displacement detection, the principle of GNSS kinematic positioning mode RTK is introduced.
+The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
+Simulation experiments and field experiments were carried out to verify the effectiveness of the proposed method. 
+These experiments confirmed the effectiveness of the method in displacement identification and extraction.
 
-For obvious vibration, the IMM Kalman filter based on the CP + DV model set can be effectively performed for online displacement extraction and vibration detection.
-The CV, CA, and CJ models are not conducive to displacement extraction due to the displacement drift, although this drift can be suppressed by the virtual measurement model.
-For slight vibration, the performance of the IMM Kalman filter with CP + DV model set is poor.
-But the performance of the IMM-SIS with the CP+CA model set is good.
-These findings have significant implications for the understanding of how to carry out online displacement extraction and vibration detection.
-This study provides the first comprehensive assessment of interactive multiple models for displacement extraction and vibration detection in SHM.
+Significant displacements can be effectively detected by the displacement Bayesian inference model.
+The displacement is obtained by the difference of the mean of the coordinates before and after the change point, which can be obtained by the mean of the posterior sample.
+The accuracy of the final displacement is determined by the number of available samples before and after the change point.
+The more samples are, the higher the accuracy is.
+When the amplitude of displacement is small, the posterior distribution of change points appears multiple peaks, which is not conducive to the effective identification of change points.
+By adding an additional prior, that is, it is impossible to have two change points in a certain time interval, which can effectively weaken the influence of secondary change points.
+To reduce the influence of the sample points of the secondary change point on the displacement extraction, the coordinate mean before and after the change point can be estimated by the median of the posterior sample.
+
+The displacement detection based on Bayesian inference can add priors to meet different analysis needs, which is flexible enough.
+In addition, the Bayesian inference implementation based on MCMC sampling used in this paper provides posterior samples, which is more conducive to problem analysis.
+This study provides the first comprehensive assessment of the Bayesian inference model for displacement identification and extraction from GNSS kinematic positioning.
 

### 2020-11-21 paper/manuscript.tex
初稿完成

@@
 \begin{abstract}
-
-\keywords{GNSS\and unmodeled error\and machine learning\and convolutional neural network\and wavelet coherence}
+For decades, displacement detection base on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
+Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
+With the development of Internet of Things (IOT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
+However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
+To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning in a short time.
+Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
+The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
+Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
+By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
+Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
+Results from simulation experiments and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
+For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding additional prior.
+The accuracy of up-displacement extraction from  GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
+\keywords{GNSS\and displacement detection \and Bayesian inference \and Markov Chain Monte Carlo \and real-time kinematic positioning}
 % \PACS{PACS code1 \and PACS code2 \and more}
@@
 \end{figure}
-%与图12中变化点t1后验样本相比，图17所示中后验样本分布更加有利于变化点的识别。
-%尽管在1200秒附近还存在一些样本点，但几乎微乎其微，基本都在1000以下。
-%t2的后验分布出现了些许变化，在1750s出现了少许样本点，不足以影响变化点的识别。
-%从图13和图18的对比中，可以看出均值后验分布的次峰基本消失。
-%但是依然存在，为了减小这些样本点的影响，采用样本的中位数作为均值的最终估值，得到的均值分别为1,2,3.
-%利用这些均值计算的位移分别为4,5.
-%而表格2中测量得到的位移分别为7,8.
-%主要是由于。。引起，从图2中可以看出存在明显浮动。
-%同理，从图19和图14的对比中，可以看出方差估值的次峰得到了显著削弱。
-%从以上的讨论中，可以看出添加的先验能够有效的提升辩护点的可识别性。
-%另一方面也说明，本文提出的基于贝叶斯推理方法足够灵活，可以根据需求添加先验的方式满足不同的分析需求。
 Compared with the posterior sample distribution of change point $\tau_1$ in Fig.

### 2020-11-21 paper/manuscript-iot.tex
add iot format

--- 2020-11-21 paper/manuscript.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%% bare_jrnl.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% see http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[journal]{IEEEtran}
 %
-% This is a general template file for the LaTeX package SVJour3
-% for Springer journals.          Springer Heidelberg 2010/09/16
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[journal]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
 %
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
 %
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
+\usepackage{cite}
+
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\ifCLASSINFOpdf
+\usepackage[pdftex]{graphicx}
+% declare the path(s) where your graphic files are
+% \graphicspath{{../pdf/}{../jpeg/}}
+% and their extensions so you won't have to specify these with
+% every instance of \includegraphics
+% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+% or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+% will default to the driver specified in the system graphics.cfg if no
+% driver is specified.
+% \usepackage[dvips]{graphicx}
+% declare the path(s) where your graphic files are
+% \graphicspath{{../eps/}}
+% and their extensions so you won't have to specify these with
+% every instance of \includegraphics
+% \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
 %
-% First comes an example EPS file -- just ignore it and
-% proceed on the \documentclass line
-% your LaTeX will extract the file if required
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+%\usepackage{graphicx}
 
+% *** MATH PACKAGES ***
 %
-\RequirePackage{fix-cm}
+%\usepackage{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
 %
-\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
-\usepackage{moreverb,url}
-\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=blue,urlcolor=blue]{hyperref}
-\usepackage{graphicx}
-\usepackage{natbib}
-\usepackage{lineno}
-\usepackage[misc]{ifsym}
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
 \usepackage{bm}
 \usepackage{amsmath} 
+\usepackage{amssymb}
 \usepackage{float}
+\usepackage{threeparttable}  
 \usepackage{multirow}
-\usepackage{threeparttable}  
 \usepackage{booktabs}
-\usepackage{color}
-\usepackage{amssymb}
-\definecolor{revision_switch}{RGB}{255,0,0}
+\usepackage{lipsum}
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a larger sans serif font
+% than the serif footnote size font used in traditional IEEE formatting
+% and thus the need to invoke different subfig.sty package options depending
+% on whether compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+%\ifCLASSOPTIONcaptionsoff
+%  \usepackage[nomarkers]{endfloat}
+% \let\MYoriglatexcaption\caption
+% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
+%\fi
+% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
+% Axel Sommerfeldt. This package may be useful when used in conjunction with 
+% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
+% submissions have lists of figures/tables at the end of the paper and that
+% figures/tables without any captions are placed on a page by themselves at
+% the end of the document. If needed, the draftcls IEEEtran class option or
+% \CLASSINPUTbaselinestretch interface can be used to increase the line
+% spacing as well. Be sure and use the nomarkers option of endfloat to
+% prevent endfloat from "marking" where the figures would have been placed
+% in the text. The two hack lines of code above are a slight modification of
+% that suggested by in the endfloat docs (section 8.4.1) to ensure that
+% the full captions always appear in the list of figures/tables - even if
+% the user used the short optional argument of \caption[]{}.
+% IEEE papers do not typically make use of \caption[]'s optional argument,
+% so this should not be an issue. A similar trick can be used to disable
+% captions of packages such as subfig.sty that lack options to turn off
+% the subcaptions:
+% For subfig.sty:
+% \let\MYorigsubfloat\subfloat
+% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
+% However, the above trick will not work if both optional arguments of
+% the \subfloat command are used. Furthermore, there needs to be a
+% description of each subfigure *somewhere* and endfloat does not add
+% subfigure captions to its list of figures. Thus, the best approach is to
+% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
+% and instead reference/explain all the subfigures within the main caption.
+% The latest version of endfloat.sty and its documentation can obtained at:
+% http://www.ctan.org/pkg/endfloat
+%
+% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
+% later in the document, say, to conditionally put the References on a 
+% page by themselves.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
 \graphicspath{{./fig/}}
 
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
+\begin{document}
 	%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+	% paper title
+	% Titles are generally capitalized except for words such as a, an, and, as,
+	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+	% not capitalized unless they are the first or last word of the title.
+	% Linebreaks \\ can be used within to get better formatting as desired.
+	% Do not put math or special symbols in the title.
+	\title{GNSS-based displacement detection using Bayesian inference for deformation monitoring}
 	%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
 	%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
+	% author names and IEEE memberships
+	% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+	% a structure at a ~ so this keeps an author's name from being broken across
+	% two lines.
+	% use \thanks{} to gain access to the first footnote area
+	% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+	% was not built to handle multiple paragraphs
 	%
-% Insert the name of "your journal" with
-\journalname{Journal of Geodesy}
-%
-\begin{document}
-\linenumbers
-\title{GNSS-based displacement detection using Bayesian inference
-%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
+
+	\author{Nan Shen, Liang Chen\textsuperscript{*}, and Ruizhi Chen% <-this % stops a space
+		\thanks{This research was funded by the National Key Research and Development Program (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No.
+2018CFA007, and the Zhejiang Lab’s International Talent Fund for Young Professionals.}% <-this % stops a space
 	}
 
-%\titlerunning{Short form of title}        % if too long for running head
+	% note the % following the last \IEEEmembership and also \thanks - 
+	% these prevent an unwanted space from occurring between the last author name
+	% and the end of the author line. i.e., if you had this:
+	% 
+	% \author{....lastname \thanks{...} \thanks{...} }
+	%                     ^------------^------------^----Do not want these spaces!
+	%
+	% a space would be appended to the last name and could cause every name on that
+	% line to be shifted left slightly. This is one of those "LaTeX things". For
+	% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
+	% "AB" then you have to do: "\textbf{A}\textbf{B}"
+	% \thanks is no different in this regard, so shield the last } of each \thanks
+	% that ends a line with a % and do not let a space in before the next \thanks.
+	% Spaces after \IEEEmembership other than the last one are OK (and needed) as
+	% you are supposed to have spaces between the names. For what it is worth,
+	% this is a minor point as most people would not even notice if the said evil
+	% space somehow managed to creep in.
 
-\author{Nan Shen\textsuperscript{1}\and
-		Liang Chen\textsuperscript{12*}\and        
-		Ruizhi Chen\textsuperscript{12} %etc.
-}
+	% The paper headers
+	\markboth{IEEE INTERNET OF THINGS JOURNAL,~Vol.~14, No.~8, August~2020}%
+	{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
+	% The only time the second header will appear is for the odd numbered pages
+	% after the title page when using the twoside option.
+	% 
+	% *** Note that you probably will NOT want to include the author's ***
+	% *** name in the headers of peer review papers.                   ***
+	% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+	% you desire.
 
-%\authorrunning{Short form of author list} % if too long for running head
+	% If you want to put a publisher's ID mark on the page you can do it like
+	% this:
+	%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+	% Remember, if you use this you must call \IEEEpubidadjcol in the second
+	% column for its text to clear the IEEEpubid mark.
 
-\institute{
-	\Letter Liang Chen\\
-	{l.chen@whu.edu.cn}\\       
-	\at
-    {1} State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, 129 Luoyu Road, Wuhan 430079, China
-    \at
-    {2} Collaborative Innovation Center for Geospatial Technology,  129 Luoyu Road, Wuhan 430079, China
-    \\
-}
+	% use for special paper notices
+	%\IEEEspecialpapernotice{(Invited Paper)}
 
-\date{Received: date }
-% The correct dates will be entered by the editor
-
+	% make the title area
 	\maketitle
 
+	% As a general rule, do not put math, special symbols or citations
+	% in the abstract or keywords.
 	\begin{abstract}
-For decades, displacement detection base on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
+For decades, deformation monitoring base on the global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
 Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
@@
 Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
-The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
-Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
+%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
+%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
 By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
@@
 The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
-\keywords{GNSS\and displacement detection \and Bayesian inference \and Markov Chain Monte Carlo \and real-time kinematic positioning}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
 	\end{abstract}
 
+	% Note that keywords are not normally used for peerreview papers.
+	\begin{IEEEkeywords}
+		GNSS, displacement detection, Bayesian inference, Markov Chain Monte Carlo, real-time kinematic positioning
+	\end{IEEEkeywords}
+
+	% For peer review papers, you can put extra information on the cover
+	% page as needed:
+	% \ifCLASSOPTIONpeerreview
+	% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+	% \fi
+	%
+	% For peerreview papers, this IEEEtran command inserts a page break and
+	% creates the second title. It will be ignored for other modes.
+	\IEEEpeerreviewmaketitle
+
 	\section{Introduction}
+	% The very first letter is a 2 line initial drop letter followed
+	% by the rest of the first word in caps.
+	% 
+	% form to use if the first word consists of a single letter:
+	% \IEEEPARstart{A}{demo} file is ....
+	% 
+	% form to use if you need the single drop letter followed by
+	% normal text (unknown if ever used by the IEEE):
+	% \IEEEPARstart{A}{}demo file is ....
+	% 
+	% Some journals put the first two words in caps:
+	% \IEEEPARstart{T}{his demo} file is ....
+	% 
+	% Here we have the typical use of a "T" for an initial drop letter
+	% and "HIS" in caps to complete the first word.
 	\label{intro}
@@
 	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
-In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\citep{teunissen2017springer}. 
-Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\citep{awange2012environmental}, industrial measurement\citep{pavasovic2011application}, and other fields.
-Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\citep{shen2019a}. 
+	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
+	Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields.
+	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\cite{shen2019a}. 
 	Displacement detection involves automatic identification of the time of displacement and determination of displacement. 
@@
 	The first category is about the research of measurement technology in GNSS-based displacement detection.
-In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\citep{wang2011gps}.The results showed that NRTK has advantages in accuracy and robustness.
-A displacement monitoring system was designed to evaluate NRTK for displacement detection\citep{GUMUS2019131}.
+	In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.The results showed that NRTK has advantages in accuracy and robustness.
+	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}.
 The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
 	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection using PPP has been studied.
-There are also some studies using the time-differenced carrier phases (TDCP) technique\citep{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection.
+There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection.
 This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
@@
 The results showed that the accuracy of Global positioning system (GPS) measurement was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
-A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\citep{rs12203375}.
+	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}.
 The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement is obtained by the direct difference between the coordinates of the start and end periods.
-In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\citep{atanasova2018ground,fuhrmann2015estimation}.
+	In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
 	In these studies, the GNSS static positioning mode is usually adopted.
@@
 In addition, epoch by epoch displacement detection is easily affected by observation noise.
-A modified real-time Chow test approach was proposed for fast deformation monitoring\citep{bellone2016real}.
-This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\citep{pirotti2015micro}.
+	A modified real-time Chow test approach was proposed for fast deformation monitoring\cite{bellone2016real}.
+This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\cite{pirotti2015micro}.
 Besides, \cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.
@@
 Bayesian inference deduces the posterior probability as the result of a priori probability and likelihood function.
-Bayesian inference calculates the posterior probability according to the Bayesian theorem\citep{chen2009modulation,chen2013bayesian}
+Bayesian inference calculates the posterior probability according to the Bayesian theorem\cite{chen2009modulation,chen2013bayesian}
 
@@
 \end{equation}
-where ${\bf{\theta }}=({{\mu_0},{\mu_1},} \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma) $; Assuming that the displacement observations are independent of each other, the likelihood probability can be expressed as
+where ${\bf{\theta }}=({{\mu_0},{\mu_1},} \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma) $; Assuming that the displacement observations are independent of each other, the likelihood probability can be expressed as in (\ref{eq_likelihoodfunc}).
+Combine \ref{eq_ts_cps} and \ref{eq_likelihoodfunc} to get the likelihood function as in (\ref{eq_likelihoodfunc_detail}).
 
+\begin{figure*}
 \begin{equation}\label{eq_likelihoodfunc}
@@
 \end{equation}
-Combine \ref{eq_ts_cps} and \ref{eq_likelihoodfunc} to get the likelihood function as follows
-
+\end{figure*}
+\begin{figure*}
 \begin{equation}\label{eq_likelihoodfunc_detail}
@@
 \end{equation}
+\end{figure*}
 
@@
 \ref{fig_v_simple_p_model}.
-\begin{figure}[H]
+\begin{figure*}[htpb]
 	\centering
-	\includegraphics[width=8 cm]{v_simple_p_model}
+	\includegraphics[scale=0.5]{v_workflow}
 	\caption{Bayesian model for displacement detection.}
 	\label{fig_v_simple_p_model}
-\end{figure} 
+\end{figure*} 
 As shown in Fig.
@@
 In this work, the Markov chain Monte Carlo technique is used to approximate the integral or sum value.
-Monte Carlo sampling is to construct the integral or sum function as the expectation under a certain distribution, and then approximate the expectation by the corresponding average value\citep{goodfellow2016deep}.
+Monte Carlo sampling is to construct the integral or sum function as the expectation under a certain distribution, and then approximate the expectation by the corresponding average value\cite{goodfellow2016deep}.
 
@@
 However, the implementation of MCMC also needs to consider other factors such as constructing the state transition matrix according to the target distribution, which is beyond the scope of this work.
-Two implementations of MCMC,  the Metropolis-Hasting sampler\citep{chib1995understanding} and the No-U-Turn sampler\citep{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively.
+Two implementations of MCMC,  the Metropolis-Hasting sampler\cite{chib1995understanding} and the No-U-Turn sampler\cite{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively.
 Next, the data source of the proposed method: GNSS real-time kinematic positioning is introduced.
@@
 \subsubsection{Observation model}
-The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\citep{teunissen2017springer}.
+The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
 \begin{figure*}
@@
 \end{equation}
-where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\citep{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.
+where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\cite{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.
 After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method.
@@
 The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively.
-Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\citep{teunissen1995the}.
+Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\cite{teunissen1995the}.
 \begin{figure*}
@@
 \end{figure*}
-There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\citep{teunissen1995the} method is the most widely used one.
+There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\cite{teunissen1995the} method is the most widely used one.
 The integer ambiguity is obtained by the integer least square method.
@@
 \subsubsection{Extended Kalman filtering}
-Kalman filtering includes two processes: prediction update and measurement update\citep{grewal2001kalman}. The prediction process is as follows:
+Kalman filtering includes two processes: prediction update and measurement update\cite{grewal2001kalman}. The prediction process is as follows:
 \begin{equation}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_sim_simple_gauss_ts}
+	\includegraphics[width=8 cm]{v_sim_simple_gauss_ts}
 	\caption{Simulation data with multiple displacement change points.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_tau_sim_simple}
+	\includegraphics[width=8 cm]{v_tau_sim_simple}
 	\caption{Histogram of posterior estimation of displacement change points in the simulation experiment.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_mu_sim_simple}
+	\includegraphics[width=8 cm]{v_mu_sim_simple}
 	\caption{Histogram of posterior estimation of the mean in the simulation experiment.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_sigma_sim_simple}
+	\includegraphics[width=8 cm]{v_sigma_sim_simple}
 	\caption{Histogram of posterior estimation of the observation noise in the simulation experiment.}
@@
 The displacement amplitude of the second experiment is smaller than that of the first experiment.
-The GNSS observation data collected above are processed by the open-source software RTKLIB\citep{takasu2011rtklib}. 
+The GNSS observation data collected above are processed by the open-source software RTKLIB\cite{takasu2011rtklib}. 
 \begin{figure}[htbp]
 	\centering
-	\includegraphics[width=10 cm]{v_field_exp_config}
+	\includegraphics[width=8 cm]{v_field_exp_config}
 	\caption{Filed experiment configuration. (a) Overview; (b) Working platform; (c) Displacement control platform; (d) Displacement measurement by tape. }
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_3_up_ts}
+	\includegraphics[width=8 cm]{v_bd9_3_up_ts}
 	\caption{The vertical component of coordinates obtained by RTK positioning in field experiment 1.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_3_up_tau}
+	\includegraphics[width=8 cm]{v_bd9_3_up_tau}
 	\caption{Histogram of posterior estimation of displacement change points in field experiment 1.}
@@
 The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
-In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\citep{teunissen2017springer}. 
+In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{teunissen2017springer}. 
 The posterior sample histogram of the mean value of each segment divided by the change point and the displacement measured by the tape are shown in Fig.
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_3_up_mu}
+	\includegraphics[width=8 cm]{v_bd9_3_up_mu}
 	\caption{Histogram of posterior estimation of the mean in field experiment 1.}
@@
 \end{figure} 
-\begin{table*}[htbp]
+\begin{table}[htbp]
 	\centering
@@
 	\end{threeparttable}
-\end{table*}
+\end{table}
 The $\mu_0$, $\mu_1$, and $\mu_2$ obtained by the mean of the posterior samples are -1446.03 mm, -1474.11 mm, and -1489.83 mm, respectively, and the two displacements obtained by the difference of these mean values are -28.08 mm, -15.72 mm, respectively.
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_3_up_sigma}
+	\includegraphics[width=8 cm]{v_bd9_3_up_sigma}
 	\caption{Histogram of posterior estimation of the observation noise in field experiment 1.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_4_up_ts}
+	\includegraphics[width=8 cm]{v_bd9_4_up_ts}
 	\caption{The vertical component of coordinates obtained by RTK positioning in field experiment 2.}
@@
 \end{figure} 
-\begin{table*}[h!t]
+\begin{table}[h!t]
 	\centering
@@
 	\end{threeparttable}
-\end{table*}
+\end{table}
 As can be seen from Fig.
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_4_up_tau}
+	\includegraphics[width=8 cm]{v_bd9_4_up_tau}
 	\caption{Histogram of posterior estimation of displacement change points in field experiment 2.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_4_up_mu}
+	\includegraphics[width=8 cm]{v_bd9_4_up_mu}
 	\caption{Histogram of posterior estimation of the mean in field experiment 2.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_4_up_sigma}
+	\includegraphics[width=8 cm]{v_bd9_4_up_sigma}
 	\caption{Histogram of posterior estimation of the observation noise in field experiment 2.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_3_up_tau_add_new_rule}
+	\includegraphics[width=8 cm]{v_bd9_3_up_tau_add_new_rule}
 	\caption{Histogram of posterior estimation of displacement change points in field experiment 2 with an additional prior.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_4_up_tau_add_new_rule}
+	\includegraphics[width=8 cm]{v_bd9_4_up_tau_add_new_rule}
 	\caption{Histogram of posterior estimation of displacement change points in field experiment 1 with an additional prior.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_4_up_mu_add_new_rule}
+	\includegraphics[width=8 cm]{v_bd9_4_up_mu_add_new_rule}
 	\caption{Histogram of posterior estimation of the mean in field experiment 2 with an additional prior.}
@@
 	\centering
-	\includegraphics[width=10 cm]{v_bd9_4_up_sigma_add_new_rule}
+	\includegraphics[width=8 cm]{v_bd9_4_up_sigma_add_new_rule}
 	\caption{Histogram of posterior estimation of the observation noise in field experiment 2 with an additional prior.}
@@
 
-\begin{acknowledgements}
-This research was funded by the National Key Research and Development Programs 2018YFB0505400, the Natural Science Fund of Hubei Province 2018CFA007.
-\end{acknowledgements}
+	% use section* for acknowledgment
+	%\section*{Acknowledgment}
+	%This research was funded by the National Key Research and Development Program (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No.
+2018CFA007, and the Zhejiang Lab’s International Talent Fund for Young Professionals.
 
+	% Can use something like this to put references on a page
+	% by themselves when using endfloat and the captionsoff option.
+	\ifCLASSOPTIONcaptionsoff
+	\newpage
+	\fi
+
+	% trigger a \newpage just before the given reference
+	% number - used to balance the columns on the last page
+	% adjust value as needed - may need to be readjusted if
+	% the document is modified later
+	%\IEEEtriggeratref{8}
+	% The "triggered" command can be changed if desired:
+	%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+	% references section
+
+	% can use a bibliography generated by BibTeX as a .bbl file
+	% BibTeX documentation can be easily obtained at:
+	% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+	% The IEEEtran BibTeX style support page is at:
+	% http://www.michaelshell.org/tex/ieeetran/bibtex/
+	%\bibliographystyle{IEEEtran}
+	% argument is your BibTeX string definitions and bibliography database(s)
+	%\bibliography{IEEEabrv,../bib/paper}
 	%
-\section*{Conflict of Interest}
-The authors declare that they have no conflict of interest.
-\section*{Author Contributions}
-Conceptualization: Nan Shen, Liang Chen; Methodology: Nan Shen, Liang Chen; Writing - original draft preparation: Nan Shen; Writing - review and editing: Liang Chen, Ruizhi Chen; Supervision: Liang Chen.
- \section*{Data Availability}
-
-% BibTeX users please use one of
-\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
+	% <OR> manually copy in the resultant .bbl file
+	% set second argument of \begin to the number of references
+	% (used to reserve space for the reference number labels box)
+	%\begin{thebibliography}{1}
+	%
+	%\bibitem{IEEEhowto:kopka}
+	%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+	%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+	%
+	%\end{thebibliography}
+	\bibliographystyle{IEEEtran}
 	\bibliography{ref}
 
+	% biography section
+	% 
+	% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+	% needed around the contents of the optional argument to biography to prevent
+	% the LaTeX parser from getting confused when it sees the complicated
+	% \includegraphics command within an optional argument. (You could create
+	% your own custom macro containing the \includegraphics command to make things
+	% simpler here.)
+	%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+	% or if you just want to reserve a space for a photo:
+
+	%\begin{IEEEbiography}{Michael Shell}
+	%Biography text here.
+	%\end{IEEEbiography}
+
+	% if you will not have a photo at all:
+	\begin{IEEEbiography}
+		[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/NanShen.jpg}}] 
+		{Nan Shen}
+		is currently a Ph.D. student at State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing at Wuhan University.
+		His research interests focus on GNSS high-precision navigation and positioning technology, real-time mitigation of site-specific errors, intelligent mitigation of GNSS unmodeled errors, interactive multi-model vibration detection, and extraction technology; software-defined receiver design, and integrated navigation and positioning technology of GNSS, INS, and vision.
+
+	\end{IEEEbiography}
+	\begin{IEEEbiography}
+		[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/LiangChen.png}}] 
+		{Liang Chen}
+		was a Senior Research Scientist with the Department of Navigation and Positioning, Finnish Geodetic Institute, Finland.
+He is currently a Professor with the State Key Laboratory of Information Engineering in Surveying, Mapping, and Remote Sensing, Wuhan University, China.
+He has published over 70 scientific articles and five book chapters.
+His current research interests include indoor positioning, wireless positioning, sensor fusion, and location-based services.
+He is currently an Associate Editor of Journal of Navigation, Navigation, and Journal of Institute of Navigation.
+	\end{IEEEbiography}
+	\begin{IEEEbiography}
+		[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/RuizhiChen.jpg}}] 
+		{Ruizhi Chen}
+		is currently a Professor and the Director of the State Key Laboratory of Information Engineering in Surveying, Mapping, and Remote Sensing, Wuhan University.
+Prior to that, he was an Endowed Chair Professor with Texas A\&M University–Corpus Christi, USA, the Head and a Professor of the Department of Navigation and Positioning, Finnish Geodetic Institute, Finland, and the Engineering Manager of Nokia, Finland.
+He has published two books and more than 200 scientific articles.
+His current research interests include indoor positioning, satellite navigation, and location-based services.
+	\end{IEEEbiography}
+
+	% insert where needed to balance the two columns on the last page with
+	% biographies
+	\newpage
+
+	% You can push biographies down or up by placing
+	% a \vfill before or after them. The appropriate
+	% use of \vfill depends on what kind of text is
+	% on the last page and whether or not the columns
+	% are being equalized.
+
+	\vfill
+
+	% Can be used to pull up biographies so that the bottom of the last one
+	% is flush with the other column.
+	%\enlargethispage{-5in}
+
+	% that's all folks
 \end{document}

### 2020-11-21 paper/manuscript.tex
add iot format

@@
 \linenumbers
-\title{GNSS-based displacement detection using Bayesian inference
+\title{GNSS-based displacement detection using Bayesian inference for deformation monitoring
 %\thanks{Grants or other notes
@@
 \begin{abstract}
-For decades, displacement detection base on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
+For decades, deformation monitoring base on the global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
 Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.

### 2020-11-22 paper/manuscript-iot.tex
modify introduction

@@
 	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
-	Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields.
-	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\cite{shen2019a}. 
-	Displacement detection involves automatic identification of the time of displacement and determination of displacement. 
+	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to natural disaster monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields.
+	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
+	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
+	With the improvement of the Internet of things (IOT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time.
+	%Displacement detection involves displacement identification and extraction. 
 	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. 

### 2020-11-22 paper/manuscript-iot.tex
proof reading 01

@@
 	In another category of GNSS-based displacement detection research, GNSS is only used as a long-term monitoring method.
-	\cite{gili2000using} was one of the first landslide monitoring studies using GNSS displacement detection technology, in which traditional measurement data are used as a comparison.
+	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data are used as a comparison.
 The results showed that the accuracy of Global positioning system (GPS) measurement was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
@@
 This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\cite{pirotti2015micro}.
-Besides, \cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.
+Besides, Dabove and Manzino\cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.
 
@@
 
-The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$,  and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate displacements.
-The time of displacement changes is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.
+The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$,  and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate.
+The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.
 The time corresponding to the $n$ change points satisfies the following relationship:$ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
-The problem of displacement detection is defined as finding out the change points of displacement and giving the effective estimation of displacement.
+The problem of displacement detection is to find out the time of displacement and estimate the displacement effectively.
 
@@
 where ${\bf{\theta }}=({{\mu_0},{\mu_1},} \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma) $; Assuming that the displacement observations are independent of each other, the likelihood probability can be expressed as in (\ref{eq_likelihoodfunc}).
-Combine \ref{eq_ts_cps} and \ref{eq_likelihoodfunc} to get the likelihood function as in (\ref{eq_likelihoodfunc_detail}).
+Combine (\ref{eq_ts_cps}) and (\ref{eq_likelihoodfunc}) to get the likelihood function as in (\ref{eq_likelihoodfunc_detail}).
 
@@
 \end{equation}
-Through \ref{eq_bayesian_prior_tau_basic} and \ref{eq_bayesian_prior_tau_5}, the joint probability of all change points can be determined.
-Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula \ref{eq_bayesian_prior}, \ref{eq_bayesian_prior_sigma}, \ref{eq_bayesian_prior_mu_sum}, \ref{eq_bayesian_prior_tau_5}.
-The graphical representation of the Bayesian model of displacement detection is shown in Fig.
-\ref{fig_v_simple_p_model}.
-\begin{figure*}[htpb]
-	\centering
-	\includegraphics[scale=0.5]{v_workflow}
-	\caption{Bayesian model for displacement detection.}
-	\label{fig_v_simple_p_model}
-\end{figure*} 
-As shown in Fig.
-\ref{fig_v_simple_p_model}, green represents the independent distribution, blue denotes the distribution dependent on other random variables, and red is the distribution of observations.
+Through (\ref{eq_bayesian_prior_tau_basic}) and (\ref{eq_bayesian_prior_tau_5}), the joint probability of all change points can be determined.
+Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula (\ref{eq_bayesian_prior}), (\ref{eq_bayesian_prior_sigma}), (\ref{eq_bayesian_prior_mu_sum}), (\ref{eq_bayesian_prior_tau_5}).
 After the Bayesian model of displacement detection is given, MCMC, one of the implementation methods of Bayesian inference, is introduced.
@@
 \subsection{Relative real-time kinematic (RTK)}
-RTK is widely used in structural health monitoring, landslide monitoring, and other fields due to its high positioning accuracy and real-time efficiency.
-The observation model, the state model, and the extended Kalman filtering process of RTK are introduced below.
+There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
+Kalman filter is used in the implementation of  RTK, and the corresponding observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
 \subsubsection{Observation model}
-The double-difference (DD) observation equation of relative positioning among base receiver, rover receiver, and satellites $j$, $k$ is defined in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
+The double-difference(DD) observation model is usually used in RTK, and its definition is shown in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
 \begin{figure*}
@@
 \end{figure*}
-In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; $\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; $\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; $\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD observation error of pseudo-range and carrier-phase, respectively; $\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites.
+In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $j$ and $k$ represent the satellites;
+$\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; 
+$\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; 
+$\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; 
+$\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD measurement noise of pseudo-range and carrier-phase, respectively; 
+$\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites.
 For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
@@
 \end{figure*}
-By ignoring the influence of multipath, linearizing equation (\ref{eq_dd_obs_simplified}), we get
+Ignoring the influence of multipath, the linearization form of formula (\ref{eq_dd_obs_simplified}) is expressed as
 \begin{equation}
@@
 where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\cite{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.
+
 After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method.
@@
 
+\subsection{Workflow of displacement detection }  
+In the previous paragraphs, the displacement detection using Bayesian inference is proposed, and the principle of relative real-time kinematic positioning is given.
+The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.
+\begin{figure*}[htpb]
+	\centering
+	\includegraphics[scale=0.45]{v_workflow}
+	\caption{Bayesian model for displacement detection.}
+	\label{fig_v_workflow}
+\end{figure*}
+
+As shown in Fig. \ref{fig_v_workflow}, to begin this process, the kinematic positioning is carried out to obtain the coordinates time series to form the data source of Bayesian inference. 
+Before the displacement detection, based on the coordinate time series and MCMC sampling, the posterior samples of model parameters are obtained by Bayesian inference.
+After obtaining the posterior distribution of the parameters, the displacement identification is achieved by the posterior distribution of the change points.
+On getting the change points, the displacement is extracted by the posterior sample distribution of the coordinate mean.
+Finally, according to the analysis of the posterior samples, the original Bayesian model is optimized as needed.
+The middle of Fig. \ref{fig_v_workflow} is a graphical description of the Bayesian model of displacement detection and its implementation described above.
+
 \section{Experiments and Results}
@@
 To verify the feasibility of the proposed method, we carried out a series of experiments, including simulation and field experiments. 
-In the simulation experiment, the data affected by different noises are simulated.
-In the field experiment, several displacement changes were triggered manually, and the relative real-time kinematic model is used to process the GNSS observations.
-\subsection{Simulation experiment}
-In the experiment, we only simulate the position measurement.
-In this simulation data, Gaussian white noise with mean 0 mm and standard deviation 30 mm is added.
-At 1000 s, 2500 s, and 3200 s, the displacements of -50 mm, -50 mm, and 100 mm are added, respectively.
-The simulation results are shown in Fig.
-\ref{fig_v_sim_simple_gauss_ts}.
+In the simulation experiment, the data is composed of designed displacement and noise.
+In the field experiment, the displacement is controlled manually by the designed displacement control platform.
+
+\subsection{Simulation Experiment}
+In the experiment, we only simulate the up coordinate component, in which Gaussian white noise with the mean of 0 mm and the standard deviation of 30 mm is added.
+ At 1000 s, 2500 s, and 3200 s, the displacements of -50 mm, -50 mm, and 100 mm are added, respectively. The simulation results are shown in Fig. \ref{fig_v_sim_simple_gauss_ts}.
 
@@
 \ref{fig_v_sim_simple_gauss_ts}, the whole time series is divided into four segments by three displacement change points.
-Using the model designed above, Bayesian inference is realized by MCMC sampling.
-The histogram of posterior estimation of displacement change points is shown in Fig.
-\ref{fig_v_tau_sim_simple}.
+Using the model designed above, Bayesian inference is implemented by MCMC sampling.
+The histogram of the posterior sample of $\bf{\tau}$ is shown in Fig. \ref{fig_v_tau_sim_simple}.
 
@@
 $\tau_3$ is the easiest to be identified, mainly due to the largest displacement amplitude.
-Due to the small displacement amplitude and fewer sample points for Bayesian estimation on the right, the estimation accuracy at $\tau_2$ is worse than the other two points.
-The histogram of the posterior estimation of the mean is shown in Fig.
-\ref{fig_v_mu_sim_simple}.
+Since the displacement amplitude at $\tau_2$ is small and there are fewer sample points on the right side, the estimated accuracy is worse than the other two points.
+The histogram of the posterior sample of $\bf{\mu}$ is shown in Fig. \ref{fig_v_mu_sim_simple}.
 
@@
 \end{figure} 
-The blue curve in Fig.
-\ref{fig_v_mu_sim_simple} is the fitting result of the histogram.
-It can be seen that although we assume that the prior distribution of the mean in the model obeys a uniform distribution, the posterior estimate of the mean approximately obeys normal distribution.
+The blue curve in Fig. \ref{fig_v_mu_sim_simple} is the fitting result of Gaussian distribution of the histogram.
+It can be seen that although we assume that the prior distribution of $\bf{\mu}$ in the model obeys a uniform distribution, the posterior sample approximately obeys normal distribution. 
 The vertical green dashed line in Fig.
-\ref{fig_v_mu_sim_simple} represents the mean value of \textbf{$\mu$} posterior samples, and the mean values of the four segments are 1.17 mm, -49.58 mm, -98.9 mm, and -3.65 mm.
+\ref{fig_v_mu_sim_simple} represents the mean value of posterior samples, and the mean values of the four segments are 1.17 mm, -49.58 mm, -98.9 mm, and -3.65 mm.
 Among these means, $\mu_2$ has the highest estimation accuracy, and its corresponding posterior sample coverage is the narrowest. 
@@
 These are mainly due to the fact that the most observation samples are used for $\mu_2$ estimation, while the least observation samples are used for $\mu_4$ estimation. 
-As shown in Fig.
-\ref{fig_v_sigma_sim_simple}, the standard deviation of the observations is also accurately estimated.
+As shown in Fig. \ref{fig_v_sigma_sim_simple}, $\sigma$ is also accurately estimated.
 
@@
 \end{figure} 
-\subsection{Field experiment}
-The experiment was carried out on the roof of a building on the campus of Wuhan University.
-In the experiment, the equipment deployment is shown in Fig.
-\ref{fig_v_field_exp_config}.
-A hard plank is pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank.
-One receiver antenna is fixed on the plank as a rover; the other receiver antenna is fixed on a tripod beside it as the base station.
-Both antennas are connected to BD992 OEM boards on the table, and the OEM boards are connected to the laptops for data collection.
-As shown in subgraphs (c) and (d), the height of the antenna is measured with a tape before and after each movement of the object hanging on the plank.
-Five readings are taken for each measurement to ensure data reliability.
-Besides, markers are made on the ground and on the antenna respectively to ensure that the same position is referenced for each measurement.
+\subsection{Field Experiments}
+The experiments were carried out on the roof of a building on the campus of Wuhan University, and the equipment deployment is shown in Fig. \ref{fig_v_field_exp_config}. 
+A hard plank was pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank. 
+One receiver antenna was fixed on the plank as a rover, and the other receiver antenna was installed on a tripod beside it as the base station. 
+Both antennas were connected to BD992 OEM boards on the table, and the OEM boards were connected to the laptops for data collection. 
+As shown in subgraphs (c) and (d), the height of the antenna was measured with a tape before and after each movement of the object hanging on the plank. 
+Five readings were taken for each measurement to ensure data reliability.
+Besides, markers are made on the ground and on the antenna respectively to ensure that the same position was referenced for each measurement. 
 The sampling frequency of the GNSS receiver is set to 1 Hz. 
 We did two experiments, each lasting nearly 45 minutes. 
-In the experiment, the objects hanging on the board were manually moved several times.
+During the experiment, the object hanging on the board was manually moved several times.
 The displacement amplitude of the second experiment is smaller than that of the first experiment.
@@
 
-\subsubsection{Field experiment 1}
-In this data processing, GNSS data were processed epoch by epoch using RTK mode.
-The coordinate output of the positioning mode is the only input of the proposed method.
-In the experiment, only the vertical displacement is triggered, so only the up-coordinate component is displayed.
-The results of RTK positioning are shown in Fig.
-\ref{fig_v_bd9_3_up_tau}.
+\subsubsection{Field Experiment 1}
+In GNSS data processing,  the data was processed epoch by epoch by using RTK mode, and the corresponding coordinate output was the only input of the proposed displacement detection method.
+In the experiment, only the vertical displacement was triggered, so only the up coordinate component is displayed. 
+The results of RTK positioning are shown in Fig. \ref{fig_v_bd9_3_up_tau}.
 \begin{figure}[htbp]
@@
 	\includegraphics[width=8 cm]{v_bd9_3_up_ts}
-	\caption{The vertical component of coordinates obtained by RTK positioning in field experiment 1.}
+	\caption{The up component of coordinates obtained by RTK positioning in field experiment 1.}
 	\label{fig_v_bd9_3_up_ts}
@@
 For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
-As can be seen from Fig.
-\ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as multipath that have not been eliminated.
+As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as multipath error that have not been eliminated. 
 The RTK positioning results are processed by the proposed model, and Bayesian inference is implemented by MCMC sampling. 
-The histogram of posterior estimation of displacement change points is shown in Fig.
-\ref{fig_v_bd9_3_up_tau}.
+The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
 
@@
 	\includegraphics[width=8 cm]{v_bd9_3_up_tau}
-	\caption{Histogram of posterior estimation of displacement change points in field experiment 1.}
+	\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
 	\label{fig_v_bd9_3_up_tau}
 \end{figure} 
-From the posterior sample distribution of $\tau_2$ in Fig.
-\ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s.
-The change point determined according to the maximum value of the posterior sample histogram of $\tau_1$ is 781 s.
-However, as can be seen from Fig.
-\ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample histogram of change point $\tau_1$, and the posterior distribution is not as obvious as in the simulation experiment.
+From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
+According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
+However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
 The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
 In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{teunissen2017springer}. 
-The posterior sample histogram of the mean value of each segment divided by the change point and the displacement measured by the tape are shown in Fig.
-\ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height}, respectively.
+The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig.
+\ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
 
@@
 	\includegraphics[width=8 cm]{v_bd9_3_up_mu}
-	\caption{Histogram of posterior estimation of the mean in field experiment 1.}
+	\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
 	\label{fig_v_bd9_3_up_mu}
@@
 		\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
-		\label{tab_measured_height}
+		\label{tab_measured_height_9_3}
 		\begin{tabular}{ccccccccc}
@@
 The main reason is that the displacement control device is not fully controllable. 
-It can be seen from Fig.
-\ref{fig_v_bd9_3_up_ts} that before the second displacement change, the plank appears obvious floating when measuring with the tape.
-As shown in Fig.
-\ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
+It can be seen from Fig. \ref{fig_v_bd9_3_up_ts} that before the second displacement change, the plank appears obvious floating when measuring with the tape. 
+As shown in Fig. \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
 %我们发现此处变点后验样本中的两个峰值对于均值和标准差中没有出现。
@@
 	\includegraphics[width=8 cm]{v_bd9_3_up_sigma}
-	\caption{Histogram of posterior estimation of the observation noise in field experiment 1.}
+	\caption{Histogram of posterior sample of $\sigma$ in field experiment 1.}
 	\label{fig_v_bd9_3_up_sigma}
 \end{figure} 
-The two peaks in the posterior sample of the change point do not appear in $\mu$ and $\sigma$. 
-The main reason is that the peak interval of change points is very close, which has no obvious influence on the segments divided, so it has little influence on the posterior mean and standard deviation.
-In reality, this kind of situation exists, for example, in the process of landslide or subsidence, multiple displacements occur in a short time, so there are multiple change points. 
-However, people pay more attention to the main change points.
-By adding additional priors to improve the identification of major change points, weakening secondary change points will be discussed later.
-
-\subsubsection{Field experiment 2}
-This experiment is similar to the previous one except that the displacement amplitude is smaller than that of the last one.
+The two peaks in the posterior sample of $\tau$ do not appear in $\mu$ and $\sigma$. 
+The main reason is that the interval of the two peaks is very close, which has no obvious influence on the segments divided, so it has little influence on the posterior mean and standard deviation.
+But in reality, this kind of situation exists, for example, in the process of landslide or subsidence, multiple displacements occur in a short time, so there are multiple change points. 
+However, more attention is paid to the primary change points.
+By adding a prior to the model to improve the identification of the primary change points, and weaken the secondary change points will be discussed later.
+
+\subsubsection{Field Experiment 2}
+This experiment is similar to the previous one except that the displacement amplitude is smaller. 
 For the data collected in this experiment,  the coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experimrnt, and the up component of the time series is shown in Fig.

### 2020-11-22 paper/manuscript-iot.tex
complete proof reading 1

@@
 	\centering
-	\includegraphics[width=8 cm]{v_sim_simple_gauss_ts}
+	\includegraphics[scale=0.35]{v_sim_simple_gauss_ts}
 	\caption{Simulation data with multiple displacement change points.}
@@
 Using the model designed above, Bayesian inference is implemented by MCMC sampling.
-The histogram of the posterior sample of $\bf{\tau}$ is shown in Fig. \ref{fig_v_tau_sim_simple}.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=8 cm]{v_tau_sim_simple}
-	\caption{Histogram of posterior estimation of displacement change points in the simulation experiment.}
+The posterior sample distribution of $\bf{\tau}$ is shown in Fig. \ref{fig_v_tau_sim_simple}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.35]{v_tau_sim_simple}
+	\caption{Posterior sample distribution of $\tau$ in the simulation experiment.}
 	\label{fig_v_tau_sim_simple}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_mu_sim_simple}
-	\caption{Histogram of posterior estimation of the mean in the simulation experiment.}
+	\includegraphics[scale=0.35]{v_mu_sim_simple}
+	\caption{Histogram of posterior estimation of $\mu$ in the simulation experiment.}
 	\label{fig_v_mu_sim_simple}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_sigma_sim_simple}
+	\includegraphics[scale=0.3]{v_sigma_sim_simple}
 	\caption{Histogram of posterior estimation of the observation noise in the simulation experiment.}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_field_exp_config}
+	\includegraphics[scale=0.5]{v_field_exp_config}
 	\caption{Filed experiment configuration. (a) Overview; (b) Working platform; (c) Displacement control platform; (d) Displacement measurement by tape. }
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_3_up_ts}
+	\includegraphics[scale=0.35]{v_bd9_3_up_ts}
 	\caption{The up component of coordinates obtained by RTK positioning in field experiment 1.}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_3_up_tau}
+	\includegraphics[scale=0.35]{v_bd9_3_up_tau}
 	\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_3_up_mu}
+	\includegraphics[scale=0.35]{v_bd9_3_up_mu}
 	\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_3_up_sigma}
+	\includegraphics[scale=0.3]{v_bd9_3_up_sigma}
 	\caption{Histogram of posterior sample of $\sigma$ in field experiment 1.}
@@
 This experiment is similar to the previous one except that the displacement amplitude is smaller. 
-For the data collected in this experiment,  the coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experimrnt, and the up component of the time series is shown in Fig.
+For the data collected in this experiment,  the coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig.
 \ref{fig_v_bd9_4_up_ts}.
-In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height}.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=8 cm]{v_bd9_4_up_ts}
-	\caption{The vertical component of coordinates obtained by RTK positioning in field experiment 2.}
+In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.35]{v_bd9_4_up_ts}
+	\caption{The up component of coordinates obtained by RTK positioning in field experiment 2.}
 	\label{fig_v_bd9_4_up_ts}
@@
 		\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 2, unit (mm).}
-		\label{tab_measured_height}
+		\label{tab_measured_height_9_4}
 		\begin{tabular}{ccccccccc}
@@
 \end{table}
-As can be seen from Fig.
-\ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height}, the amplitude of the two displacements is smaller than that of the previous experiment.
+As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
 The time series are processed by the proposed model, and Bayesian inference is implemented by MCMC sampling.
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_4_up_tau}
-	\caption{Histogram of posterior estimation of displacement change points in field experiment 2.}
+	\includegraphics[scale=0.35]{v_bd9_4_up_tau}
+	\caption{Posterior sample distribution of $\tau$ in field experiment 2.}
 	\label{fig_v_bd9_4_up_tau}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_4_up_mu}
-	\caption{Histogram of posterior estimation of the mean in field experiment 2.}
+	\includegraphics[scale=0.35]{v_bd9_4_up_mu}
+	\caption{Histogram of posterior sample of $\mu$ in field experiment 2.}
 	\label{fig_v_bd9_4_up_mu}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_4_up_sigma}
-	\caption{Histogram of posterior estimation of the observation noise in field experiment 2.}
+	\includegraphics[scale=0.3]{v_bd9_4_up_sigma}
+	\caption{Histogram of posterior sample of $\sigma$ in field experiment 2.}
 	\label{fig_v_bd9_4_up_sigma}
@@
 It can be seen from Fig.
-\ref{fig_v_bd9_4_up_tau} that there are two peaks in the posterior sample histogram of $\tau_1$.
+\ref{fig_v_bd9_4_up_tau} that there are two peaks in the posterior sample distribution of $\tau_1$.
 Unlike Fig.
@@
 In addition, we found that the second peak of $\tau_1$ is very close to the peak of $\tau_2$, which is not what we want because we do not want to get very short segments. 
-In the next section, we will discuss adding an additional prior to the model to improve the performance of Bayesian inference.
+In the next section, we will discuss adding a prior to the model to improve the performance of Bayesian inference.
 \section{Discussion}
@@
 In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
-The interval between adjacent change points is constrained by adding an additional prior. 
+The interval between adjacent change points is constraint by adding a prior. 
 The random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.
@@
 \end{equation}
-where $d$ is the shortest time interval to be restricted. The new Bayesian probability model with additional prior is shown in Fig. \ref{fig_v_simple_p_model_add_new_rule}.
+where $d$ is the shortest time interval to be constraint. The new Bayesian probability model with the prior is shown in Fig. \ref{fig_v_simple_p_model_add_new_rule}.
 
@@
 	\centering
-	\includegraphics[width=8 cm]{v_simple_p_model_add_new_rule}
-	\caption{Bayesian model for displacement detection with an additional prior.}
+	\includegraphics[scale=0.35]{v_simple_p_model_add_new_rule}
+	\caption{Bayesian model for displacement detection with an interval constraint prior.}
 	\label{fig_v_simple_p_model_add_new_rule}
 \end{figure} 
-As shown in Formula \ref{eq_bayesian_prior_d_tau} and Fig.
-\ref{fig_v_simple_p_model_add_new_rule}, the distribution of newly added random variables depends on the change points and the constrained interval.
+As shown in (\ref{eq_bayesian_prior_d_tau}) and Fig.
+\ref{fig_v_simple_p_model_add_new_rule}, the prior distribution of newly added random variables depends on the change points and the constraint interval.
 In the following data processing, the interval $d$ is set to 300.
-The data in field experiment 1 is reprocessed with the new Bayesian model, and the posterior distribution of displacement change points is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=8 cm]{v_bd9_3_up_tau_add_new_rule}
-	\caption{Histogram of posterior estimation of displacement change points in field experiment 2 with an additional prior.}
+The data in field experiment 1 is reprocessed with the new Bayesian model, and the posterior distribution of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.35]{v_bd9_3_up_tau_add_new_rule}
+	\caption{Posterior sample distribution of $\tau$ in field experiment 1 with an interval constraint prior.}
 	\label{fig_v_bd9_3_up_tau_add_new_rule}
@@
 There is no significant change in the posterior distribution of $\tau_2$, $\mu$, and  $\sigma$.
-The data in field experiment 2 is also reprocessed with the new Bayesian model, and the results are shown in Figs.
+The data in field experiment 2 is also reprocessed with the new Bayesian model, and the results are shown in Fig.
 \ref{fig_v_bd9_4_up_tau_add_new_rule}, \ref{fig_v_bd9_4_up_mu_add_new_rule}, and \ref{fig_v_bd9_4_up_sigma_add_new_rule}.
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_4_up_tau_add_new_rule}
-	\caption{Histogram of posterior estimation of displacement change points in field experiment 1 with an additional prior.}
+	\includegraphics[scale=0.35]{v_bd9_4_up_tau_add_new_rule}
+	\caption{Posterior sample distribution of $\tau$ in field experiment 2 with an interval constraint prior.}
 	\label{fig_v_bd9_4_up_tau_add_new_rule}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_4_up_mu_add_new_rule}
-	\caption{Histogram of posterior estimation of the mean in field experiment 2 with an additional prior.}
+	\includegraphics[scale=0.35]{v_bd9_4_up_mu_add_new_rule}
+	\caption{Histogram of posterior sample of $\mu$ in field experiment 2 with an interval constraint prior.}
 	\label{fig_v_bd9_4_up_mu_add_new_rule}
@@
 	\centering
-	\includegraphics[width=8 cm]{v_bd9_4_up_sigma_add_new_rule}
-	\caption{Histogram of posterior estimation of the observation noise in field experiment 2 with an additional prior.}
+	\includegraphics[scale=0.3]{v_bd9_4_up_sigma_add_new_rule}
+	\caption{Histogram of posterior sample of $\sigma$ in field experiment 2 with an interval constraint prior.}
 	\label{fig_v_bd9_4_up_sigma_add_new_rule}
 \end{figure}
-Compared with the posterior sample distribution of change point $\tau_1$ in Fig.
+Compared with the posterior sample distribution of $\tau_1$ in Fig.
 \ref{fig_v_bd9_4_up_tau}, the posterior sample distribution in Fig.
 \ref{fig_v_bd9_4_up_tau_add_new_rule} is more conducive to the identification of the change point.
-Although there are still some sample points around 1200 seconds, most of them are below 1000, which has little effect.
-The posterior distribution of $\tau_2$ has slightly changed. A few sample points appear around 1750 s, but it is not enough to affect the identification of the change point.
+Although there are still some sampling points around 1200 seconds, most of the sample number is below 1000, which has little effect.
+The posterior distribution of $\tau_2$ has slightly changed. 
+There are a few sampling points around 1750 s, which are not enough to affect the identification of change points.
 From the comparison between Fig. \ref{fig_v_bd9_4_up_mu} and Fig. \ref{fig_v_bd9_4_up_mu_add_new_rule}, it can be seen that the secondary peak of $\mu_1$ almost disappears.
@@
 In order to reduce the influence of these sampling points, the median value of the sample is used as the final estimation of \textbf{$\mu$}, and $\mu_0$, $\mu_1$ and $\mu_2$ are obtained as -1461.18 mm, -1482.37 mm and -1509.09 mm respectively.
-The two displacements obtained by these means are -21.19 mm and -26.72 mm, respectively, and the displacements measured in Table \ref{tab_measured_height} are -21.3 mm and -19.6 mm respectively.
+The two displacements obtained by these means are -21.19 mm and -26.72 mm, respectively, and the displacements measured in Table \ref{tab_measured_height_9_4} are -21.3 mm and -19.6 mm respectively.  
 The displacement difference between the two methods at the two change points is 0.11 mm and 7.12 mm, respectively. 
@@
 It can be seen from Fig. \ref{fig_v_bd9_4_up_sigma_add_new_rule} and Fig. \ref{fig_v_bd9_4_up_sigma} that the secondary peak of $\sigma$ posterior distribution has been significantly weakened.
-From the above discussion, we can see that the added prior can effectively improve the identifiability of change points.
+As can be seen from the above discussion that the interval constraint prior can effectively improve the identifiability of change points.
 On the other hand, it also shows that the Bayesian inference-based displacement detection method proposed in this paper is flexible enough to meet different analysis needs by adding a priori.
@@
 This study set out to develop a Bayesian model for displacement detection from GNSS kinematic positioning in a short time. 
-The definition of multiple displacements is given, and the Bayesian model for multiple displacement detection is proposed.
+The description of multiple displacements is given, and the Bayesian model for multiple displacement detection is proposed.
 The principle of Bayesian inference and its implementation based on MCMC sampling are presented.
@@
 The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
-Simulation experiments and field experiments were carried out to verify the effectiveness of the proposed method. 
+Simulation and field experiments were carried out to verify the effectiveness of the proposed method. 
 These experiments confirmed the effectiveness of the method in displacement identification and extraction.
@@
 The more samples are, the higher the accuracy is.
+
 When the amplitude of displacement is small, the posterior distribution of change points appears multiple peaks, which is not conducive to the effective identification of change points.
-By adding an additional prior, that is, it is impossible to have two change points in a certain time interval, which can effectively weaken the influence of secondary change points.
+By adding an interval constraint prior, the influence of secondary change points can be effectively weakened.
 To reduce the influence of the sample points of the secondary change point on the displacement extraction, the coordinate mean before and after the change point can be estimated by the median of the posterior sample.
 
-The displacement detection based on Bayesian inference can add priors to meet different analysis needs, which is flexible enough.
+The displacement detection based on Bayesian inference can meet different needs by adding a priori, and has sufficient flexibility.
 In addition, the Bayesian inference implementation based on MCMC sampling used in this paper provides posterior samples, which is more conducive to problem analysis.

### 2020-11-23 paper/manuscript-iot.tex
proof reading 2

@@
 		\thanks{This research was funded by the National Key Research and Development Program (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No.
-2018CFA007, and the Zhejiang Lab’s International Talent Fund for Young Professionals.}% <-this % stops a space
+2018CFA007.}% <-this % stops a space
 	}
@@
 	\begin{abstract}
-For decades, deformation monitoring base on the global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
+For decades, deformation monitoring based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
 Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
@@
 Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
-Results from simulation experiments and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
-For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding additional prior.
+Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
+For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior.
 The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
@@
 	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
-	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to natural disaster monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields.
+	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to natural landslide monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields.
 	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
@@
 	%Displacement detection involves displacement identification and extraction. 
-	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. 
+	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. 
 	There are many researches on displacement detection based on GNSS, which can be divided into two categories.
@@
 	The first category is about the research of measurement technology in GNSS-based displacement detection.
-	In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.The results showed that NRTK has advantages in accuracy and robustness.
+	In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.
+The results showed that NRTK has advantages in accuracy and robustness.
 	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}.
 The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
-	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection using PPP has been studied.
+	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using PPP has been studied.
+The results showed that PPP can be capable of detecting large landslides.
 	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection.
 This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
-	This kind of method mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.
-
-	In another category of GNSS-based displacement detection research, GNSS is only used as a long-term monitoring method.
+	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.
+
+	In another category of GNSS-based displacement detection research, GNSS is only used as a static positioning method.
 	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data are used as a comparison. 
-The results showed that the accuracy of Global positioning system (GPS) measurement was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
+	The results showed that the accuracy of the Global positioning system (GPS) measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
 	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
-The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement is obtained by the direct difference between the coordinates of the start and end periods.
-	In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
+	The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
+	In addition, GNSS was also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements were used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
 	In these studies, the GNSS static positioning mode is usually adopted.
@@
 	This study utilized Bayesian inference to identify and extract displacement, and the Markov Chain Monte Carlo (MCMC) technique is adopted to implement the Bayesian inference. 
-Simulation experiments and field experiments were carried out to verify the feasibility of the proposed method.
+	Simulation and field experiments were carried out to verify the feasibility of the proposed method. 
 	The posterior sample distribution of parameters is used to analyze the reliability of displacement detection. 
@@
 The time corresponding to the $n$ change points satisfies the following relationship:$ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
-The problem of displacement detection is to find out the time of displacement and estimate the displacement effectively.
+The problem of displacement detection is to find out the time of displacement and estimate the displacement.
 
 \subsubsection{Bayesian Inference}
-Bayesian inference is one of the most important skills in statistics.
-Bayesian inference deduces the posterior probability as the result of a priori probability and likelihood function.
+Bayesian inference is one of the most important skills in statistics, and deduces the posterior probability as the result of a priori probability and likelihood function\cite{robert2014machine}.
 Bayesian inference calculates the posterior probability according to the Bayesian theorem\cite{chen2009modulation,chen2013bayesian}
@@
 \end{equation}
-where $\bf{\theta }$ is the parameter to be estimated and $\bf{x}$ is the observation;$P({\bf{\theta }}\left| {\bf{x}} \right.)$ denotes the posterior probability; $P({\bf{\theta }})$ represents a priori probability, which refers to the probability obtained from previous experience and analysis;
+where $\bf{\theta }$ is the parameter to be estimated and $\bf{x}$ is the observation; $P({\bf{\theta }}\left| {\bf{x}} \right.)$ denotes the posterior probability; $P({\bf{\theta }})$ represents a priori probability, which refers to the probability obtained from previous experience and analysis;
 $P({\bf{x}}\left| {\bf{\theta }} \right.)$ is the likelihood function, which represents the probability of $x$ when a priori is established.
@@
 \subsubsection{Likelihood Function}
-It is assumed that the displacement obtained by GNSS obeys Gaussian normal distribution.
-The displacement of each segment segmented by the change point obeys the Gaussian distribution of different mean and same variance, which is expressed as follows
+It is assumed that the displacement obtained by GNSS kinematic positioning obeys Gaussian normal distribution.
+The displacement of each segment segmented by the change points obeys the Gaussian distribution of different mean and same variance, which is expressed as follows
 
@@
 	{\begin{array}{*{20}{c}}
-		{N({\mu _n},\sigma ),}
+		{N({\mu _{n-1}},\sigma ),}
 		\end{array}}&{{\tau _{n - 1}} \le t < {\tau _n}}\\
-	{N({\mu _{n + 1}},\sigma ),}&{{\tau _n} \le t}
+	{N({\mu _{n}},\sigma ),}&{{\tau _n} \le t}
 	\end{array}} \right.
@@
 \subsubsection{Prior Distribution}
-Assuming that the parameters ${\bf{\tau }}=(\tau_1,\mu_2,\cdots,\tau_n)$, ${\bf{\mu }}=(\mu_0,\mu_1,\cdots,\mu_n)$ and $\sigma$ are independent of each other, then:
+Assuming that the parameters ${\bf{\tau }}=(\tau_1,\tau_2,\cdots,\tau_n)$, ${\bf{\mu }}=(\mu_0,\mu_1,\cdots,\mu_n)$ and $\sigma$ are independent of each other, then:
 
@@
 \end{equation}
-The posterior distribution consists of three parts, including the prior distribution of change point, mean value and standard deviation.
+The prior distribution consists of three parts, including the prior distribution of change point, mean value and standard deviation.
 It is assumed that the standard deviation $\sigma$ obeys the Gaussian normal distribution and is expressed as follows
@@
 \begin{equation}\label{eq_bayesian_prior_mu}
-{\mu _i} \sim U({x_l },{x_u })(i = 0,1, \cdots ,n)
-\end{equation}
-where $x_l$ and $x_u$ represent the lower limit and  upper limit of the uniform distribution, which are determined by the mean value of the coordinate time series and the possible range of variation.
+{\mu _i} \sim U({\mu_l },{\mu_u })(i = 0,1, \cdots ,n)
+\end{equation}
+where $\mu_l$ and $\mu_u$ represent the lower limit and  upper limit of the uniform distribution, which are determined by the mean value of the coordinate time series and the possible range of variation.
 Assuming that the mean values of each segment are independent of each other, then
@@
 The posterior distribution of the parameters depends on the prior distribution and the likelihood function.
-Obtaining the posterior probability of parameters by direct integration or sum requires a lot of operations, which is difficult to achieve.
+Obtaining the posterior probability of parameters by direct integration or sum requires a lot of operations, which is difficult to achieve\cite{robert2013monte}.
 In this work, the Markov chain Monte Carlo technique is used to approximate the integral or sum value.
@@
 The integral or summation problem of $g(x)$ is transformed into the mathematical expectation problem of $f(x)$ under the distribution $p(x)$.
-This mathematical expectation can be approximated by sampling from $p(x)$.
+This mathematical expectation can be approximated by sampling from $p(x)$\cite{goodfellow2016deep}.
 
@@
 At present, the most popular solution is to use Markov chain Monte Carlo sampling, which provides a general way to construct a sequence that converges to the target distribution.
-According to Markov chain, the probability of state transition at a certain time only depends on its previous state, which is expressed as follows
+According to Markov chain, the probability of state transition at a certain time only depends on its previous state, which is expressed as follows\cite{robert2013monte}
 
@@
 If a Markov process is neither periodic nor irreducible, then the Markov process is ergodic, that is, each state appears with a certain probability.
-The Markov process of ergodic states has an important property: no matter what the initial state probability is, the Markov process of the ergodic state tends to be a stable distribution after enough state transitions.
+The Markov process of ergodic states has an important property: no matter what the initial state probability is, the Markov process of the ergodic state tends to be a stable distribution after enough state transitions\cite{robert2013monte}.
 That is, for the initial probability distribution is $\pi_0(x)$, the probability distribution after several rounds of state transition is as follows
@@
 Sample $(x_{n},x_{n+1},x_{n+2}\cdots)$ is the corresponding sample set of the target distribution.
-However, the implementation of MCMC also needs to consider other factors such as constructing the state transition matrix according to the target distribution, which is beyond the scope of this work.
+However, the implementation of MCMC also needs to consider other factors such as constructing the state transition matrix according to the target distribution\cite{robert2013monte}, which is beyond the scope of this work.
 Two implementations of MCMC,  the Metropolis-Hasting sampler\cite{chib1995understanding} and the No-U-Turn sampler\cite{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively.
@@
 There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
-Kalman filter is used in the implementation of  RTK, and the corresponding observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
+Kalman filter is used in the implementation of  RTK, and the observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
 \subsubsection{Observation model}
@@
 $\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD measurement noise of pseudo-range and carrier-phase, respectively; 
-$\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites.
+$\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations\cite{teunissen2017springer}; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites.
 For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
@@
 After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method. 
+The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively. 
 To obtain high precision positioning results, it is necessary to fix the integer ambiguity. 
-The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively.
 Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\cite{teunissen1995the}.
@@
 	\begin{equation}
-	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{\tilde N}} - \Delta \nabla {\bf{\hat N}})^T})
+	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{N}} - \Delta  {\bf{\tilde N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{N}} - \Delta \nabla {\bf{\tilde N}})^T})
 	\label{eq_lamda}
@@
 The integer ambiguity is obtained by the integer least square method.
-Then, the test process is executed to determine whether to accept or reject the integer ambiguity.
+Then, the test process is executed to determine whether to accept or reject the integer ambiguity\cite{teunissen2003integer,teunissen2005gnss}.
 If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.
@@
 	{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
-	\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station; Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed.
+	\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station;
+Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed. 
 $\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$. 
@@
 \subsection{Workflow of displacement detection }  
-In the previous paragraphs, the displacement detection using Bayesian inference is proposed, and the principle of relative real-time kinematic positioning is given.
+In the previous paragraphs, the displacement detection model using Bayesian inference is proposed, and the principle of relative real-time kinematic positioning is presented.
 The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.
@@
 As shown in Fig. \ref{fig_v_workflow}, to begin this process, the kinematic positioning is carried out to obtain the coordinates time series to form the data source of Bayesian inference. 
-Before the displacement detection, based on the coordinate time series and MCMC sampling, the posterior samples of model parameters are obtained by Bayesian inference.
-After obtaining the posterior distribution of the parameters, the displacement identification is achieved by the posterior distribution of the change points.
-On getting the change points, the displacement is extracted by the posterior sample distribution of the coordinate mean.
+Before the displacement detection,  the posterior samples of model parameters are obtained by Bayesian inference based on the MCMC sampling.
+After obtaining the posterior sample distribution of the parameters, the displacement identification is achieved by the posterior sample distribution of the change points.
+On getting the change points, the displacement is extracted by the posterior sample distribution of  the 'mean' parameters.
 Finally, according to the analysis of the posterior samples, the original Bayesian model is optimized as needed.
@@
 In the simulation experiment, the data is composed of designed displacement and noise.
-In the field experiment, the displacement is controlled manually by the designed displacement control platform.
+In the field experiment, the displacement is controlled manually by the  the self-built displacement control platform.
 
@@
 In the experiment, we only simulate the up coordinate component, in which Gaussian white noise with the mean of 0 mm and the standard deviation of 30 mm is added.
- At 1000 s, 2500 s, and 3200 s, the displacements of -50 mm, -50 mm, and 100 mm are added, respectively. The simulation results are shown in Fig. \ref{fig_v_sim_simple_gauss_ts}.
+At 1000 s, 2500 s, and 3200 s, the displacements of -50 mm, -50 mm, and 100 mm are added, respectively. 
+The simulation results are shown in Fig. \ref{fig_v_sim_simple_gauss_ts}.
 
@@
 \end{figure} 
-As shown in Fig.
-\ref{fig_v_sim_simple_gauss_ts}, the whole time series is divided into four segments by three displacement change points.
+As shown in Fig. \ref{fig_v_sim_simple_gauss_ts}, the whole time series is divided into four segments by three displacement change points. 
 Using the model designed above, Bayesian inference is implemented by MCMC sampling. 
@@
 \end{figure} 
-As can be seen from Fig.
-\ref{fig_v_tau_sim_simple}, all the designed displacement change points are identified.
+As can be seen from Fig. \ref{fig_v_tau_sim_simple}, all the designed displacement change points are identified. 
 $\tau_3$ is the easiest to be identified, mainly due to the largest displacement amplitude. 
-Since the displacement amplitude at $\tau_2$ is small and there are fewer sample points on the right side, the estimated accuracy is worse than the other two points.
+Since the displacement amplitude at $\tau_2$ is small and there are fewer sample points on the right side, the estimated accuracy is worse than the other two change points.
 The histogram of the posterior sample of $\bf{\mu}$ is shown in Fig. \ref{fig_v_mu_sim_simple}.
@@
 The blue curve in Fig. \ref{fig_v_mu_sim_simple} is the fitting result of Gaussian distribution of the histogram.
-It can be seen that although we assume that the prior distribution of $\bf{\mu}$ in the model obeys a uniform distribution, the posterior sample approximately obeys normal distribution. 
+Although we assume that the prior distribution of $\bf{\mu}$ in the model obeys a uniform distribution, the posterior sample approximately obeys normal distribution. 
 The vertical green dashed line in Fig.
 \ref{fig_v_mu_sim_simple} represents the mean value of posterior samples, and the mean values of the four segments are 1.17 mm, -49.58 mm, -98.9 mm, and -3.65 mm.
-Among these means, $\mu_2$ has the highest estimation accuracy, and its corresponding posterior sample coverage is the narrowest. 
+Among these means, $\mu_2$ has the highest accuracy, and its corresponding posterior sample coverage is the narrowest. 
 The estimation accuracy of $\mu_4$ is the lowest, and the corresponding posterior sample coverage is the widest. 
@@
 	\includegraphics[scale=0.3]{v_sigma_sim_simple}
-	\caption{Histogram of posterior estimation of the observation noise in the simulation experiment.}
+	\caption{Histogram of posterior sample of $\sigma$ in the simulation experiment.}
 	\label{fig_v_sigma_sim_simple}
@@
 In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
-The interval between adjacent change points is constraint by adding a prior. 
+The interval between adjacent change points is constrained by adding a prior. 
 The random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.
@@
 \end{equation}
-where $d$ is the shortest time interval to be constraint. The new Bayesian probability model with the prior is shown in Fig. \ref{fig_v_simple_p_model_add_new_rule}.
+where $d$ is the shortest time interval to be constrained. The new Bayesian probability model with the prior is shown in Fig. \ref{fig_v_simple_p_model_add_new_rule}.
 

### 2020-11-23 paper/manuscript-iot.tex
proof reading 2

@@
 As shown in Fig. \ref{fig_v_sim_simple_gauss_ts}, the whole time series is divided into four segments by three displacement change points. 
-Using the model designed above, Bayesian inference is implemented by MCMC sampling. 
+Using the model designed above, Bayesian inference is implemented by the MCMC sampling. 
 The posterior sample distribution of $\bf{\tau}$ is shown in Fig. \ref{fig_v_tau_sim_simple}.
@@
 \subsubsection{Field Experiment 1}
-In GNSS data processing,  the data was processed epoch by epoch by using RTK mode, and the corresponding coordinate output was the only input of the proposed displacement detection method.
-In the experiment, only the vertical displacement was triggered, so only the up coordinate component is displayed. 
+GNSS observations were processed epoch by epoch by using RTK mode, and the corresponding coordinate output was the only input of the proposed displacement detection method.
 The results of RTK positioning are shown in Fig. \ref{fig_v_bd9_3_up_tau}.
+Only the vertical displacement was triggered in the experiment, so only the up coordinate component is displayed. 
 \begin{figure}[htbp]
@@
 For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
-As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as multipath error that have not been eliminated. 
-The RTK positioning results are processed by the proposed model, and Bayesian inference is implemented by MCMC sampling. 
+As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
+The RTK positioning results are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. 
 The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
@@
 The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
-In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{teunissen2017springer}. 
+In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}.
 The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig.
@@
 \end{figure} 
-The two peaks in the posterior sample of $\tau$ do not appear in $\mu$ and $\sigma$. 
-The main reason is that the interval of the two peaks is very close, which has no obvious influence on the segments divided, so it has little influence on the posterior mean and standard deviation.
-But in reality, this kind of situation exists, for example, in the process of landslide or subsidence, multiple displacements occur in a short time, so there are multiple change points. 
+Different from the posterior sample distribution of $\tau$, there is only one peak value in the posterior sample distribution of $\mu$ and $\sigma$.
+The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
+In reality, multiple change points exist, such as multiple displacements in a short period of time in the process of landslide or settlement.
 However, more attention is paid to the primary change points.
-By adding a prior to the model to improve the identification of the primary change points, and weaken the secondary change points will be discussed later.
+By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
 
@@
 This experiment is similar to the previous one except that the displacement amplitude is smaller. 
-For the data collected in this experiment,  the coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig.
-\ref{fig_v_bd9_4_up_ts}.
+The coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig. \ref{fig_v_bd9_4_up_ts}. 
 In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.
@@
 As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
-The time series are processed by the proposed model, and Bayesian inference is implemented by MCMC sampling.
+The time series are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling.
 The results are shown in Fig.

### 2020-11-23 paper/manuscript-iot.tex
proof reading2 complete

@@
 	\begin{abstract}
-For decades, deformation monitoring based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
+For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
 Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
-With the development of Internet of Things (IOT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
+With the development of Internet of Things (IoT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
 However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
@@
 	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
-	\IEEEPARstart{I}{n}  recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\cite{teunissen2017springer}. 
-	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to natural landslide monitoring\cite{awange2012environmental}, industrial measurement\cite{pavasovic2011application}, and other fields.
+	\IEEEPARstart{I}{n}  recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying\cite{barry2011surveying}, and civil aviation\cite{iatsouk2004development}, and autonomous vehicle\cite{kuutti2018survey} as a positioning method.
+	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}, and other fields.
 	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
 	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
-	With the improvement of the Internet of things (IOT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time.
+	With the development of the Internet of things (IoT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time\cite{mei2019survey}.
 	%Displacement detection involves displacement identification and extraction. 
@@
 In addition, in field experiment 2, the posterior distribution interval of two different change points is close.
-The interval between adjacent change points is constrained by adding a prior. 
-The random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.
+Here, the interval between adjacent change points is constrained by adding a prior. 
+A random variable $d\tau$, the distance between continuous change points, is added, which obeys the  discrete uniform distribution.
 

### 2020-11-23 paper/manuscript-iot.tex
proof reading 3 complete

@@
 However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
-To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning in a short time.
+To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
 Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
@@
 	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
-	\IEEEPARstart{I}{n}  recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying\cite{barry2011surveying}, and civil aviation\cite{iatsouk2004development}, and autonomous vehicle\cite{kuutti2018survey} as a positioning method.
+	\IEEEPARstart{I}{n}  recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying\cite{barry2011surveying}, civil aviation\cite{iatsouk2004development}, and autonomous vehicle\cite{kuutti2018survey} as a positioning method.
 	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}, and other fields.
@@
 	The first category is about the research of measurement technology in GNSS-based displacement detection.
-	In order to evaluate the performance of single base station real time kinematic(RTK) and network RTK(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.
+	In order to evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.
 The results showed that NRTK has advantages in accuracy and robustness.
@@
 The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
-	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using PPP has been studied.
+	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied.
 The results showed that PPP can be capable of detecting large landslides.
@@
 The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.
-The time corresponding to the $n$ change points satisfies the following relationship:$ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
+The time corresponding to the $n$ change points satisfies the following relationship: $ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
 The problem of displacement detection is to find out the time of displacement and estimate the displacement.
@@
 \begin{equation}\label{eq_monte_carlo_2}
-s =\int {g(x)}= \int {p(x)f(x)dx}  = {E_p}[f(x)]
+s =\int {g(x)dx}= \int {p(x)f(x)dx}  = {E_p}[f(x)]
 \end{equation}
@@
 
-\subsection{Relative real-time kinematic (RTK)}
+\subsection{Relative Real-time Kinematic (RTK)}
 There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
 Kalman filter is used in the implementation of  RTK, and the observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
-\subsubsection{Observation model}
+\subsubsection{Observation Model}
 The double-difference(DD) observation model is usually used in RTK, and its definition is shown in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
@@
 	\left. \begin{array}{l}
-	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla \delta I_{\Phi {i_{br}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
-	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \delta _{tro{p_{br}}}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
+	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla I_{\Phi {i_{br}}}^{jk} + \Delta \nabla  T_{br}^{jk} + \Delta \nabla  M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
+	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla T_{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla  M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
 	\end{array} \right\}
@@
 $\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; 
-$\Delta \nabla \delta M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \delta M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; 
+$\Delta \nabla  M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla  M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; 
 $\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD measurement noise of pseudo-range and carrier-phase, respectively; 
-$\Delta \nabla \delta I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations\cite{teunissen2017springer}; $\Delta \nabla \delta _{tro{{p}_{br}}}^{jk}$is the DD tropospheric delay between receivers and satellites.
+$\Delta \nabla  I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations\cite{teunissen2017springer}; $\Delta \nabla T_{br}^{jk}$is the DD tropospheric delay between receivers and satellites.
 For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
@@
 	\left. \begin{array}{l}
-	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla \delta M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
-	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla \delta M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
+	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla  M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
+	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla  M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
 	\label{eq_dd_obs_simplified}
@@
 To obtain high precision positioning results, it is necessary to fix the integer ambiguity. 
-Then the problem of ambiguity fixing can be described as (\ref{eq_lamda})\cite{teunissen1995the}.
+The problem of ambiguity fixing can be described as (\ref{eq_lamda})\cite{teunissen1995the}.
 \begin{figure*}
@@
 
-\subsubsection{State model}
+\subsubsection{State Model}
 The state model is defined as follows (Takasu 2013)
@@
 \begin{equation}
-{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}(k){{\bf{\hat x}}_{k|k - 1}}
+{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}_k{{\bf{\hat x}}_{k|k - 1}}
 \end{equation}
 \begin{equation}
-{{\bf{S}}_k} = {\bf{H}}(k){{\bf{Q}}_{k|k - 1}}{\bf{H}}{(k)^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
+{{\bf{S}}_k} = {\bf{H}}_k{{\bf{Q}}_{k|k - 1}}{\bf{H}}{_k^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
 \end{equation}
@@
 It can be seen from Fig. \ref{fig_v_bd9_4_up_sigma_add_new_rule} and Fig. \ref{fig_v_bd9_4_up_sigma} that the secondary peak of $\sigma$ posterior distribution has been significantly weakened.
+
 As can be seen from the above discussion that the interval constraint prior can effectively improve the identifiability of change points.

### 2020-12-13 paper/manuscript-iot.tex
submit to supervisor
add poofeading 2.0

@@
 	% Do not put math or special symbols in the title.
-	\title{GNSS-based displacement detection using Bayesian inference for deformation monitoring}
+	\title{GNSS-based Displacement Detection Using Bayesian Inference for Deformation Monitoring}
 	%
@@
 	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}.
-The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
+The results showed that NRTK can achieve an accuracy of 4.7mm and 7.9mm in the horizontal and vertical directions respectively.
 	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied.
@@
 	In another category of GNSS-based displacement detection research, GNSS is only used as a static positioning method.
-	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data are used as a comparison. 
+	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
 	The results showed that the accuracy of the Global positioning system (GPS) measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
@@
 \end{equation}
+where ${\bf{\hat x}}_{k|k - 1}$ is the predicted value and ${\bf{Q}}_{k|k - 1}$ is the corresponding covariance.
 According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged.
@@
 \end{equation}
-where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the proposed method.
+where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the Bayesian inference.
 

### 2020-12-20 paper/manuscript-iot.tex
sub 2 iot version

@@
 	\author{Nan Shen, Liang Chen\textsuperscript{*}, and Ruizhi Chen% <-this % stops a space
-		\thanks{This research was funded by the National Key Research and Development Program (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No.
-2018CFA007.}% <-this % stops a space
+		\thanks{This research was funded by the National Key R&D Program of China (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No. 2018CFA007.}% <-this % stops a space
 	}

### 2021-03-21 paper/manuscript-cmame.tex
revise fig

--- 2020-12-20 paper/manuscript-iot.tex
@@
-%% bare_jrnl.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
 %% 
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
+%% Copyright 2007-2019 Elsevier Ltd
 %% 
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
+%% This file is part of the 'Elsarticle Bundle'.
+%% ---------------------------------------------
+%% 
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%% 
+%% The list of all files belonging to the 'Elsarticle Bundle' is
+%% given in the file `manifest.txt'.
+%%
 
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
+%% Template article for Elsevier's document class `elsarticle'
+%% with numbered style bibliographic references
+%% SP 2008/03/01
 %%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
 %% 
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
+%%
+%% $Id: elsarticle-template-num.tex 168 2019-02-25 07:15:41Z apu.v $
+%%
+%%
+\documentclass[final,3p,times]{elsarticle}
 
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. The IEEE's font choices and paper sizes can   ***
-% *** trigger bugs that do not appear when using other class files.       ***                          ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
+%% Use the option review to obtain double line spacing
+%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
 
-\documentclass[journal]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
+%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
+%% for a journal layout:
+%% \documentclass[final,1p,times]{elsarticle}
+%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+%% \documentclass[final,3p,times]{elsarticle}
+%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+%% \documentclass[final,5p,times]{elsarticle}
+%% \documentclass[final,5p,times,twocolumn]{elsarticle}
 
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
+%% For including figures, graphicx.sty has been loaded in
+%% elsarticle.cls. If you prefer to use the old commands
+%% please give \usepackage{epsfig}
 
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/pkg/ifpdf
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
+%% The amssymb package provides various useful mathematical symbols
+\usepackage{amssymb}
+%% The amsthm package provides extended theorem environments
+%% \usepackage{amsthm}
 
-% *** CITATION PACKAGES ***
-%
-\usepackage{cite}
+%% The lineno packages adds line numbers. Start line numbering with
+%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
+%% for the whole article with \linenumbers.
+%% \usepackage{lineno}
 
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of the IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 5.0 (2009-03-20) and later if using hyperref.sty.
-% The latest version can be obtained at:
-% http://www.ctan.org/pkg/cite
-% The documentation is contained in the cite.sty file itself.
+\usepackage{moreverb,url}
 
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-\usepackage[pdftex]{graphicx}
-% declare the path(s) where your graphic files are
-% \graphicspath{{../pdf/}{../jpeg/}}
-% and their extensions so you won't have to specify these with
-% every instance of \includegraphics
-% \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-% or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-% will default to the driver specified in the system graphics.cfg if no
-% driver is specified.
-% \usepackage[dvips]{graphicx}
-% declare the path(s) where your graphic files are
-% \graphicspath{{../eps/}}
-% and their extensions so you won't have to specify these with
-% every instance of \includegraphics
-% \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/pkg/graphicx
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/pkg/epslatex
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-%\usepackage{graphicx}
+\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
 
-% *** MATH PACKAGES ***
-%
-%\usepackage{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics.
-%
-% Note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/amsmath
 \usepackage{bm}
@@
 \usepackage{lipsum}
+\usepackage{stfloats}
+\usepackage{graphicx}      % insert graphic
+\usepackage{subcaption}
+\usepackage{lineno}
+\linenumbers
 
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/pkg/algorithms
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/pkg/algorithmicx
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/array
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/pkg/subfig
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure.
-% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
-% corrections already built into the system in which case a warning will
-% be issued if an attempt is made to load fixltx2e.sty as it is no longer
-% needed.
-% The latest version and documentation can be found at:
-% http://www.ctan.org/pkg/fixltx2e
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/pkg/stfloats
-% Do not use the stfloats baselinefloat ability as the IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that the IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/pkg/dblfloatfix
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/pkg/endfloat
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/pkg/url
-% Basically, \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
 \graphicspath{{./fig/}}
 
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
+\journal{Computer Methods in Applied Mechanics and Engineering}
 
 \begin{document}
-	%
-	% paper title
-	% Titles are generally capitalized except for words such as a, an, and, as,
-	% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-	% not capitalized unless they are the first or last word of the title.
-	% Linebreaks \\ can be used within to get better formatting as desired.
-	% Do not put math or special symbols in the title.
+
+	\begin{frontmatter}
+
+		%% Title, authors and addresses
+
+		%% use the tnoteref command within \title for footnotes;
+		%% use the tnotetext command for theassociated footnote;
+		%% use the fnref command within \author or \address for footnotes;
+		%% use the fntext command for theassociated footnote;
+		%% use the corref command within \author for corresponding author footnotes;
+		%% use the cortext command for theassociated footnote;
+		%% use the ead command for the email address,
+		%% and the form \ead[url] for the home page:
+		%\title{Title\tnoteref{label1}}
+		%% \tnotetext[label1]{}
+		%% \author{Name\corref{cor1}\fnref{label2}}
+		%% \ead{email address}
+		%% \ead[url]{home page}
+		%% \fntext[label2]{}
+		%% \cortext[cor1]{}
+		%% \address{Address\fnref{label3}}
+		%% \fntext[label3]{}
+
 		\title{GNSS-based Displacement Detection Using Bayesian Inference for Deformation Monitoring}
-	%
-	%
-	% author names and IEEE memberships
-	% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-	% a structure at a ~ so this keeps an author's name from being broken across
-	% two lines.
-	% use \thanks{} to gain access to the first footnote area
-	% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-	% was not built to handle multiple paragraphs
-	%
 
-	\author{Nan Shen, Liang Chen\textsuperscript{*}, and Ruizhi Chen% <-this % stops a space
-		\thanks{This research was funded by the National Key R&D Program of China (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No. 2018CFA007.}% <-this % stops a space
-	}
+		%% use optional labels to link authors explicitly to addresses:
+		%% \author[label1,label2]{}
+		%% \address[label1]{}
+		%% \address[label2]{}
 
-	% note the % following the last \IEEEmembership and also \thanks - 
-	% these prevent an unwanted space from occurring between the last author name
-	% and the end of the author line. i.e., if you had this:
-	% 
-	% \author{....lastname \thanks{...} \thanks{...} }
-	%                     ^------------^------------^----Do not want these spaces!
-	%
-	% a space would be appended to the last name and could cause every name on that
-	% line to be shifted left slightly. This is one of those "LaTeX things". For
-	% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-	% "AB" then you have to do: "\textbf{A}\textbf{B}"
-	% \thanks is no different in this regard, so shield the last } of each \thanks
-	% that ends a line with a % and do not let a space in before the next \thanks.
-	% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-	% you are supposed to have spaces between the names. For what it is worth,
-	% this is a minor point as most people would not even notice if the said evil
-	% space somehow managed to creep in.
-
-	% The paper headers
-	\markboth{IEEE INTERNET OF THINGS JOURNAL,~Vol.~14, No.~8, August~2020}%
-	{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
-	% The only time the second header will appear is for the odd numbered pages
-	% after the title page when using the twoside option.
-	% 
-	% *** Note that you probably will NOT want to include the author's ***
-	% *** name in the headers of peer review papers.                   ***
-	% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-	% you desire.
-
-	% If you want to put a publisher's ID mark on the page you can do it like
-	% this:
-	%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-	% Remember, if you use this you must call \IEEEpubidadjcol in the second
-	% column for its text to clear the IEEEpubid mark.
-
-	% use for special paper notices
-	%\IEEEspecialpapernotice{(Invited Paper)}
-
-	% make the title area
-	\maketitle
-
-	% As a general rule, do not put math, special symbols or citations
-	% in the abstract or keywords.
+		\author[a]{Nan Shen}
+		\author[a]{Liang Chen\corref{mycorrespondingauthor}}
+		\cortext[mycorrespondingauthor]{Corresponding author}
+		\ead{l.chen@whu.edu.cn}
+		\author[a]{Ruizhi Chen}
+		\address[a]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430000, PR China}
 		\begin{abstract}
@@
 
-	% Note that keywords are not normally used for peerreview papers.
-	\begin{IEEEkeywords}
+		%%Graphical abstract
+		%\begin{graphicalabstract}
+		%%\includegraphics{grabs}
+		%\end{graphicalabstract}
+
+		%%Research highlights
+		%\begin{highlights}
+		%\item Research highlight 1
+		%\item Research highlight 2
+		%\end{highlights}
+
+		\begin{keyword}
 		GNSS, displacement detection, Bayesian inference, Markov Chain Monte Carlo, real-time kinematic positioning
-	\end{IEEEkeywords}
+		\end{keyword}
 
-	% For peer review papers, you can put extra information on the cover
-	% page as needed:
-	% \ifCLASSOPTIONpeerreview
-	% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-	% \fi
-	%
-	% For peerreview papers, this IEEEtran command inserts a page break and
-	% creates the second title. It will be ignored for other modes.
-	\IEEEpeerreviewmaketitle
+	\end{frontmatter}
 
+	%% \linenumbers
+
+	%% main text
 	\section{Introduction}
-	% The very first letter is a 2 line initial drop letter followed
-	% by the rest of the first word in caps.
-	% 
-	% form to use if the first word consists of a single letter:
-	% \IEEEPARstart{A}{demo} file is ....
-	% 
-	% form to use if you need the single drop letter followed by
-	% normal text (unknown if ever used by the IEEE):
-	% \IEEEPARstart{A}{}demo file is ....
-	% 
-	% Some journals put the first two words in caps:
-	% \IEEEPARstart{T}{his demo} file is ....
-	% 
-	% Here we have the typical use of a "T" for an initial drop letter
-	% and "HIS" in caps to complete the first word.
+
 	\label{intro}
@@
 	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
-	\IEEEPARstart{I}{n}  recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying\cite{barry2011surveying}, civil aviation\cite{iatsouk2004development}, and autonomous vehicle\cite{kuutti2018survey} as a positioning method.
+	In recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying\cite{barry2011surveying}, civil aviation\cite{iatsouk2004development}, and autonomous vehicle\cite{kuutti2018survey} as a positioning method.
 	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}, and other fields.
@@
 	\end{equation}
-where ${\bf{\theta }}=({{\mu_0},{\mu_1},} \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma) $; Assuming that the displacement observations are independent of each other, the likelihood probability can be expressed as in (\ref{eq_likelihoodfunc}).
-Combine (\ref{eq_ts_cps}) and (\ref{eq_likelihoodfunc}) to get the likelihood function as in (\ref{eq_likelihoodfunc_detail}).
-
-\begin{figure*}
+	where ${\bf{\theta }}=({{\mu_0},{\mu_1},} \cdots {\mu_n},{\tau _1},{\tau _2}, \cdots ,{\tau _n},\sigma) $; Assuming that the displacement observations are independent of each other, the likelihood probability can be expressed as
 	\begin{equation}\label{eq_likelihoodfunc}
@@
 	\end{equation}
-\end{figure*}
-\begin{figure*}
+	Combine (\ref{eq_ts_cps}) and (\ref{eq_likelihoodfunc}) to get the likelihood function as follows
 	\begin{equation}\label{eq_likelihoodfunc_detail}
@@
 	\end{equation}
-\end{figure*}
-
 	\subsubsection{Prior Distribution}
@@
 	\subsubsection{Observation Model}
-The double-difference(DD) observation model is usually used in RTK, and its definition is shown in (\ref{eq_dd_obs})\cite{teunissen2017springer}.
-\begin{figure*}
+	The double-difference(DD) observation model is usually used in RTK, and its definition is as follows\cite{teunissen2017springer}.
 	\begin{equation}
@@
 	\end{equation}
-\end{figure*}
 	In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $j$ and $k$ represent the satellites;
@@
 	$\Delta \nabla  I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations\cite{teunissen2017springer}; $\Delta \nabla T_{br}^{jk}$is the DD tropospheric delay between receivers and satellites.
-For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as (\ref{eq_dd_obs_simplified}).
-\begin{figure*}
+	For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as
 	\begin{equation}
@@
 	\end{equation}
-
-\end{figure*}
 	Ignoring the influence of multipath, the linearization form of formula (\ref{eq_dd_obs_simplified}) is expressed as
@@
 	To obtain high precision positioning results, it is necessary to fix the integer ambiguity. 
-The problem of ambiguity fixing can be described as (\ref{eq_lamda})\cite{teunissen1995the}.
-\begin{figure*}
+	The problem of ambiguity fixing can be described as\cite{teunissen1995the}.
 	\begin{equation}
@@
 	\end{equation}
-\end{figure*}
 	There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\cite{teunissen1995the} method is the most widely used one.
@@
 		\centering
-	\includegraphics[scale=0.35]{v_sim_simple_gauss_ts}
+		\includegraphics[scale=0.45]{v_sim_simple_gauss_ts}
 		\caption{Simulation data with multiple displacement change points.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_tau_sim_simple}
+		\includegraphics[scale=0.45]{v_tau_sim_simple}
 		\caption{Posterior sample distribution of $\tau$ in the simulation experiment.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_mu_sim_simple}
+		\includegraphics[scale=0.45]{v_mu_sim_simple}
 		\caption{Histogram of posterior estimation of $\mu$ in the simulation experiment.}
@@
 		\centering
-	\includegraphics[scale=0.3]{v_sigma_sim_simple}
+		\includegraphics[scale=0.45]{v_sigma_sim_simple}
 		\caption{Histogram of posterior sample of $\sigma$ in the simulation experiment.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_bd9_3_up_ts}
+		\includegraphics[scale=0.45]{v_bd9_3_up_ts}
 		\caption{The up component of coordinates obtained by RTK positioning in field experiment 1.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_bd9_3_up_tau}
+		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
 		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_bd9_3_up_mu}
+		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
 		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
@@
 		\centering
-	\includegraphics[scale=0.3]{v_bd9_3_up_sigma}
+		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
 		\caption{Histogram of posterior sample of $\sigma$ in field experiment 1.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_bd9_4_up_ts}
+		\includegraphics[scale=0.45]{v_bd9_4_up_ts}
 		\caption{The up component of coordinates obtained by RTK positioning in field experiment 2.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_bd9_4_up_tau}
+		\includegraphics[scale=0.45]{v_bd9_4_up_tau}
 		\caption{Posterior sample distribution of $\tau$ in field experiment 2.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_bd9_4_up_mu}
+		\includegraphics[scale=0.45]{v_bd9_4_up_mu}
 		\caption{Histogram of posterior sample of $\mu$ in field experiment 2.}
@@
 		\centering
-	\includegraphics[scale=0.3]{v_bd9_4_up_sigma}
+		\includegraphics[scale=0.45]{v_bd9_4_up_sigma}
 		\caption{Histogram of posterior sample of $\sigma$ in field experiment 2.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_simple_p_model_add_new_rule}
+		\includegraphics[scale=0.45]{v_simple_p_model_add_new_rule}
 		\caption{Bayesian model for displacement detection with an interval constraint prior.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_bd9_3_up_tau_add_new_rule}
+		\includegraphics[scale=0.45]{v_bd9_3_up_tau_add_new_rule}
 		\caption{Posterior sample distribution of $\tau$ in field experiment 1 with an interval constraint prior.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_bd9_4_up_tau_add_new_rule}
+		\includegraphics[scale=0.45]{v_bd9_4_up_tau_add_new_rule}
 		\caption{Posterior sample distribution of $\tau$ in field experiment 2 with an interval constraint prior.}
@@
 		\centering
-	\includegraphics[scale=0.35]{v_bd9_4_up_mu_add_new_rule}
+		\includegraphics[scale=0.45]{v_bd9_4_up_mu_add_new_rule}
 		\caption{Histogram of posterior sample of $\mu$ in field experiment 2 with an interval constraint prior.}
@@
 		\centering
-	\includegraphics[scale=0.3]{v_bd9_4_up_sigma_add_new_rule}
+		\includegraphics[scale=0.45]{v_bd9_4_up_sigma_add_new_rule}
 		\caption{Histogram of posterior sample of $\sigma$ in field experiment 2 with an interval constraint prior.}
@@
 
-	% use section* for acknowledgment
-	%\section*{Acknowledgment}
-	%This research was funded by the National Key Research and Development Program (2018YFB0505400), the Natural Science Fund of Hubei Province with Project No.
-2018CFA007, and the Zhejiang Lab’s International Talent Fund for Young Professionals.
+%	\section*{Acknowledgement}
 
-	% Can use something like this to put references on a page
-	% by themselves when using endfloat and the captionsoff option.
-	\ifCLASSOPTIONcaptionsoff
-	\newpage
-	\fi
-
-	% trigger a \newpage just before the given reference
-	% number - used to balance the columns on the last page
-	% adjust value as needed - may need to be readjusted if
-	% the document is modified later
-	%\IEEEtriggeratref{8}
-	% The "triggered" command can be changed if desired:
-	%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-	% references section
-
-	% can use a bibliography generated by BibTeX as a .bbl file
-	% BibTeX documentation can be easily obtained at:
-	% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-	% The IEEEtran BibTeX style support page is at:
-	% http://www.michaelshell.org/tex/ieeetran/bibtex/
-	%\bibliographystyle{IEEEtran}
-	% argument is your BibTeX string definitions and bibliography database(s)
-	%\bibliography{IEEEabrv,../bib/paper}
-	%
-	% <OR> manually copy in the resultant .bbl file
-	% set second argument of \begin to the number of references
-	% (used to reserve space for the reference number labels box)
-	%\begin{thebibliography}{1}
-	%
-	%\bibitem{IEEEhowto:kopka}
-	%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-	%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-	%
-	%\end{thebibliography}
-	\bibliographystyle{IEEEtran}
+	\section*{Fundings}
+This research was funded by the National Key Research and Development Programs 2018YFB0505400
+	\section*{Conflict of interest}
+	The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+	\section*{References} 
+	\bibliographystyle{elsarticle-num}
 	\bibliography{ref}
 
-	% biography section
-	% 
-	% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-	% needed around the contents of the optional argument to biography to prevent
-	% the LaTeX parser from getting confused when it sees the complicated
-	% \includegraphics command within an optional argument. (You could create
-	% your own custom macro containing the \includegraphics command to make things
-	% simpler here.)
-	%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-	% or if you just want to reserve a space for a photo:
-
-	%\begin{IEEEbiography}{Michael Shell}
-	%Biography text here.
-	%\end{IEEEbiography}
-
-	% if you will not have a photo at all:
-	\begin{IEEEbiography}
-		[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/NanShen.jpg}}] 
-		{Nan Shen}
-		is currently a Ph.D. student at State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing at Wuhan University.
-		His research interests focus on GNSS high-precision navigation and positioning technology, real-time mitigation of site-specific errors, intelligent mitigation of GNSS unmodeled errors, interactive multi-model vibration detection, and extraction technology; software-defined receiver design, and integrated navigation and positioning technology of GNSS, INS, and vision.
-
-	\end{IEEEbiography}
-	\begin{IEEEbiography}
-		[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/LiangChen.png}}] 
-		{Liang Chen}
-		was a Senior Research Scientist with the Department of Navigation and Positioning, Finnish Geodetic Institute, Finland.
-He is currently a Professor with the State Key Laboratory of Information Engineering in Surveying, Mapping, and Remote Sensing, Wuhan University, China.
-He has published over 70 scientific articles and five book chapters.
-His current research interests include indoor positioning, wireless positioning, sensor fusion, and location-based services.
-He is currently an Associate Editor of Journal of Navigation, Navigation, and Journal of Institute of Navigation.
-	\end{IEEEbiography}
-	\begin{IEEEbiography}
-		[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/RuizhiChen.jpg}}] 
-		{Ruizhi Chen}
-		is currently a Professor and the Director of the State Key Laboratory of Information Engineering in Surveying, Mapping, and Remote Sensing, Wuhan University.
-Prior to that, he was an Endowed Chair Professor with Texas A\&M University–Corpus Christi, USA, the Head and a Professor of the Department of Navigation and Positioning, Finnish Geodetic Institute, Finland, and the Engineering Manager of Nokia, Finland.
-He has published two books and more than 200 scientific articles.
-His current research interests include indoor positioning, satellite navigation, and location-based services.
-	\end{IEEEbiography}
-
-	% insert where needed to balance the two columns on the last page with
-	% biographies
-	\newpage
-
-	% You can push biographies down or up by placing
-	% a \vfill before or after them. The appropriate
-	% use of \vfill depends on what kind of text is
-	% on the last page and whether or not the columns
-	% are being equalized.
-
-	\vfill
-
-	% Can be used to pull up biographies so that the bottom of the last one
-	% is flush with the other column.
-	%\enlargethispage{-5in}
-
-	% that's all folks
 \end{document}
+\endinput
+%%
+%% End of file `elsarticle-template-num.tex'.

### 2021-03-22 paper/manuscript-cmame.tex

@@
 		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
-		With the development of Internet of Things (IoT), high-precision GNSS positioning, and GNSS related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
+		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
 		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.

### 2021-03-22 paper/manuscript-cmame.tex
add comparsion methods

@@
 	%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
-	In recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying\cite{barry2011surveying}, civil aviation\cite{iatsouk2004development}, and autonomous vehicle\cite{kuutti2018survey} as a positioning method.
-	Besides, as a displacement detection method in deformation monitoring, GNSS has been applied to landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}, and other fields.
+	In recent decades, the Global navigation satellite system (GNSS) has been widely used in surveying, civil aviation, and autonomous vehicle as a positioning method\cite{barry2011surveying,iatsouk2004development}.
+	Besides, as a displacement detection method in deformation monitoring, GNSS has been widely applied to engineering fields such as landslide monitoring\cite{awange2012environmental}, subsidence survey\cite{bian2014monitoring}, industrial measurement\cite{pavasovic2011application}.
+	Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics\cite{TASORA2020112635,BIGONI2020113315}.
 	Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high precision, and weather independence\cite{shen2019a}. 
 	%随着物联网通信技术标准的制订和创新，高精度定位技术，例如RTK，PPP，以及GNSS传输协议NTRIP的发展，GNSS定位结果可以被实时传输到云端。
-	With the development of the Internet of things (IoT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time\cite{mei2019survey}.
+	With the development of the Internet of things (IoT), GNSS high-precision positioning technology, and GNSS enhanced information transmission protocol, high-precision GNSS positioning results can be transmitted to the cloud in real-time.
 	%Displacement detection involves displacement identification and extraction. 
@@
 	The first category is about the research of measurement technology in GNSS-based displacement detection.
-	In order to evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.
+	To evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.
 The results showed that NRTK has advantages in accuracy and robustness.
@@
 	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
-	The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
+	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
 	In addition, GNSS was also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements were used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
@@
 Different filters in the model represent different displacement models, which need to be defined in advance.
-In addition, epoch by epoch displacement detection is easily affected by observation noise.
+	In addition, the index-based is also widely used, but it is easily affected by the observation noise, so further measures need to be taken\cite{shen_shortterm2021}.
 	A modified real-time Chow test approach was proposed for fast deformation monitoring\cite{bellone2016real}.
@@
 	%Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情
-	Previous studies provide an important information for the application of displacement detection based on GNSS, but most of them focus on the detection of long term displacement. 
+	Previous studies provide important information for the application of displacement detection based on GNSS, but most of them focus on the detection of long-term displacement. 
 	Few studies have explored the use of GNSS kinematic positioning for short-term displacement detection. 
@@
 	In the field experiment, the displacement is controlled manually by the  the self-built displacement control platform.
+	Moreover, the results of some commonly used index-based abrupt detection methods including the Buishand U test(BUT), Pettitt’s test (PETT), standard normal homogeneity test (SNHT), Z test(ZT), are given for comparison.
 

### 2021-03-22 code/matlab/demo.m

@@ -1,0 +1,11 @@
+clc
+clear
+% dp= './data/sim_ts.txt';
+% out4origin='sim_idx.mat';
+% fetch_idx(dp,out4origin)
+% dp= './data/exp1_ts.txt';
+% out4origin='exp1_idx.mat';
+% fetch_idx(dp,out4origin)
+dp= './data/exp2_ts.txt';
+out4origin='exp2_idx.mat';
+fetch_idx(dp,out4origin)

### 2021-03-22 code/matlab/detector/Buishand_U_change_point_detection.m

@@ -1,0 +1,16 @@
+function [I,Skk] = Buishand_U_change_point_detection(inputdata)
+%UNTITLED 此处显示有关此函数的摘要
+%   此处显示详细说明
+    inputdata_mean = mean(inputdata);
+    n  = length(inputdata);
+    Sk=zeros(n,1);
+    for i=0:n-1
+        Sk(i+1)=sum(inputdata(1:i+1) - inputdata_mean);
+    end
+    sigma = sqrt(sum((inputdata-mean(inputdata)).^2)/(n-1));
+    U = sum((Sk(1:(n - 1))/sigma).^2)/(n * (n + 1));
+    Ska = abs(Sk);
+    [~,I] = max(Ska);
+    Skk = (Sk/sigma);
+end
+

### 2021-03-22 code/matlab/detector/SNHT.m

@@ -1,0 +1,15 @@
+function [means,stds,ipt,Tk] = SNHT(data)
+%SNHT 此处显示有关此函数的摘要
+%   此处显示详细说明
+    inputdata_mean = mean(data);
+    n  = length(data);
+    sigma = sqrt(sum((data-mean(data)).^2)/(n-1));
+    Tk=zeros(n,1);
+    for i=1:n
+        Tk(i)=i*(sum((data(1:i)-inputdata_mean)/sigma)/i).^2 + (n-i)*(sum((data(i+1:n)-inputdata_mean)/sigma)/(n-i)).^2;
+    end
+    [~,ipt] = max(Tk);
+    means=[mean(data(1:ipt));mean(data(ipt+1:end))];
+    stds=[std(data(1:ipt));std(data(ipt+1:end))];
+end
+

### 2021-03-22 code/matlab/detector/pettitt_change.m

@@ -1,0 +1,59 @@
+function [means,stds,ipt,U] = pettitt_change(data)
+% This code is used to find the change point in a univariate continuous time series
+
+% using Pettitt Test.
+
+%
+
+%
+
+% The test here assumed is two-tailed test. The hypothesis are as follow:
+
+%  H (Null Hypothesis): There is no change point in the series
+
+%  H(Alternative Hypothesis): There is a change point in the series
+
+% 
+
+% Input: univariate data series
+
+% Output:
+
+% The output of the answer in row wise respectively,
+
+% loc: location of the change point in the series, index value in
+
+% the data set
+
+% K: Pettitt Test Statistic for two tail test
+
+% pvalue: p-value of the test
+
+%
+
+%Reference: Pohlert, Thorsten. "Non-Parametric Trend Tests and Change-Point Detection." (2016).
+
+% 
+n=length(data);
+s=0;
+U=zeros(n-1,0);
+for i=1:n-1
+    for j=i+1:n
+      s=s+sign(data(i)-data(j));
+    end
+    U(i)=s;
+end
+
+ipt=find(abs(U)==max(abs(U)));
+
+K=max(abs(U));
+pvalue=2*exp((-6*K^2)/(n^3+n^2));
+if length(ipt)>1
+    ipt=floor(mean(ipt));
+end
+means=[mean(data(1:ipt-1));mean(data(ipt:end))];
+stds=[std(data(1:ipt-1));std(data(ipt:end))];
+
+U=U';
+end
+

### 2021-03-22 code/matlab/detector/z_test.m

@@ -1,0 +1,19 @@
+function [means,stds,ipt,z] = z_test(data)
+%SNHT 此处显示有关此函数的摘要
+%   此处显示详细说明
+    n  = length(data);
+    z =zeros(n-1,1);
+    for i=1:n-1
+        seg0=data(1:i);
+        seg1=data(i+1:n);
+        mean0=mean(seg0);
+        mean1=mean(seg1);
+        std0=std(seg0);
+        std1=std(seg1);
+        z(i)=(mean1-mean0)/sqrt(std0^2/i+std1^2/(n-i));
+    end
+    [~,ipt] = max(z);
+    means=[mean(data(1:ipt-1));mean(data(ipt:end))];
+    stds=[std(data(1:ipt-1));std(data(ipt:end))];
+end
+

### 2021-03-22 code/matlab/fetch_idx.m

@@ -1,0 +1,14 @@
+function [] = fetch_idx(dp,out4origin)
+%FETCH_IDX 此处显示有关此函数的摘要
+%   此处显示详细说明
+addpath('./detector')
+[t,x]=loadGnssTs(dp);
+[~,Skk] = Buishand_U_change_point_detection(x);
+[~,~,~,U] = pettitt_change(x);
+[~,~,~,Tk] = SNHT(x);
+[~,~,~,z] = z_test(x);
+l=min([length(Skk),length(U),length(Tk),length(z)]);
+out=[t(1:l),Skk(1:l),U(1:l),Tk(1:l),z(1:l)];
+save(out4origin,'out');
+end
+

### 2021-03-22 code/matlab/loadGnssTs.m

@@ -1,0 +1,39 @@
+function [t,x] = loadGnssTs(filename, dataLines)
+%IMPORTFILE 从文本文件中导入数据
+%  SIMTS = IMPORTFILE(FILENAME)读取文本文件 FILENAME 中默认选定范围的数据。  以表形式返回数据。
+%
+%  SIMTS = IMPORTFILE(FILE, DATALINES)按指定行间隔读取文本文件 FILENAME
+%  中的数据。对于不连续的行间隔，请将 DATALINES 指定为正整数标量或 N×2 正整数标量数组。
+%
+%  示例:
+%  simts = importfile("D:\Softs-Data\vs-workspace\paper\Hoegaarden\code\matlab\data\sim_ts.txt", [1, Inf]);
+%
+%  另请参阅 READTABLE。
+%
+% 由 MATLAB 于 2021-03-22 12:01:18 自动生成
+
+%% 输入处理
+
+% 如果不指定 dataLines，请定义默认范围
+if nargin < 2
+    dataLines = [1, Inf];
+end
+
+%% 设置导入选项
+opts = delimitedTextImportOptions("NumVariables", 2);
+
+% 指定范围和分隔符
+opts.DataLines = dataLines;
+opts.Delimiter = ",";
+
+% 指定列名称和类型
+opts.VariableNames = ["t", "x"];
+opts.VariableTypes = ["double", "double"];
+opts.ExtraColumnsRule = "ignore";
+opts.EmptyLineRule = "read";
+
+% 导入数据
+simts = readtable(filename, opts);
+t = simts{:,1};
+x = simts{:,2};
+end

### 2021-03-22 paper/manuscript-cmame.tex
manucript for cmame

@@
 		\begin{abstract}
+		Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics.
 		For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement.
-		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
-		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
+%		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
+%		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
 		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
@@
 
+	% 仿真实验中不同基于索引检测方法的指标值如图6所示。
+	% 从中可以看出不同探测方法所采用的指标的数值范围不一致，但在所设计的突变处很明显。
+	%  然而，想基于这些指标值自动将这些突变点识别出来，还需要额外的工作。
+	%  另外，这些方法设计之初为了探测突变点，并未涉及位移提取。
+	%  有学者，基于设计了基于这些指标的突变探测和位移提取方法，但实时过程复杂。
+	%  相比而言，本文提出的方法是一种简单直接易于实现的一站式方法。
+	The index values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
+	It can be seen that the numerical range of indicators used by different detection methods is not consistent, but all are obvious at the designed abrupt point.
+	However, to automatically identify these abrupt points based on these index values, additional work is required, such as setting a certain threshold.
+	In addition, these methods were originally designed to detect abrupt points without involving displacement extraction.
+	There are abrupt detection and displacement extraction methods based on these indicators, but the implementation process is complex\cite{shen_shortterm2021}.
+	In contrast, the method proposed in this work is a simple, straightforward, and easy-to-implement one-stop method.
 	\begin{figure}[htbp]
@@
 		\label{fig_v_sigma_sim_simple}
+	\end{figure} 
+	\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.45]{v_sim_idx}
+	\caption{Index values of different index-based detection methods in simulation experiments.}
+	\label{fig_v_sim_idx}
 	\end{figure} 
@@
 	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
-
 	\begin{figure}[htbp]
@@
 	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}.
+	The index values of different index-based detection methods in field experiment 1 are shown in Fig.
+\ref{fig_v_exp1_idx}.
+At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
 	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig.
 \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
-
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[scale=0.45]{v_exp1_idx}
+		\caption{Index values of different index-based detection methods in field experiment 1.}
+		\label{fig_v_exp1_idx}
+	\end{figure} 
 	\begin{figure}[htbp]
@@
 	\end{table}
+
 	The $\mu_0$, $\mu_1$, and $\mu_2$ obtained by the mean of the posterior samples are -1446.03 mm, -1474.11 mm, and -1489.83 mm, respectively, and the two displacements obtained by the difference of these mean values are -28.08 mm, -15.72 mm, respectively.
@@
 	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
-
 	\subsubsection{Field Experiment 2}
@@
 	The data in field experiment 2 is also reprocessed with the new Bayesian model, and the results are shown in Fig.
-\ref{fig_v_bd9_4_up_tau_add_new_rule}, \ref{fig_v_bd9_4_up_mu_add_new_rule}, and \ref{fig_v_bd9_4_up_sigma_add_new_rule}.
+\ref{fig_v_bd9_4_up_tau_add_new_rule}, \ref{fig_v_exp2_idx}, \ref{fig_v_bd9_4_up_mu_add_new_rule}, and \ref{fig_v_bd9_4_up_sigma_add_new_rule}.
 
@@
 		\label{fig_v_bd9_4_up_tau_add_new_rule}
+	\end{figure} 
+	\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.45]{v_exp2_idx}
+	\caption{Index values of different index-based detection methods in field experiment 2.}
+	\label{fig_v_exp2_idx}
 	\end{figure} 

### 2021-09-03 paper/r1/manuscript-mssp.tex
r1 initial 参考文献 EKF

--- 2021-03-22 paper/manuscript-cmame.tex
@@
 \usepackage{lineno}
+\usepackage{color}
+\definecolor{r_s}{RGB}{255,0,0}
 \linenumbers
@@
 
-\journal{Computer Methods in Applied Mechanics and Engineering}
+\journal{Mechanical Systems and Signal Processing}
 
@@
 	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}.
-The results showed that NRTK can achieve an accuracy of 4.7mm and 7.9mm in the horizontal and vertical directions respectively.
+The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
 	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied.
 The results showed that PPP can be capable of detecting large landslides.
+	\textcolor{r_s}{
+		Moschas et al.\cite{Moschas_2014} studied the extraction of strong motion displacement waveform by PPP and evaluated it through free vibration experiments.
+These results show that 10 Hz PPP-GPS is very useful for seismic engineering and can be safely used to reconstruct the deflection waveforms of various points on the ground and structure during strong motion.}
+	\textcolor{r_s}{Zhang et al.\cite{Meng_2019} introduced Galileo augmenting GPS single-frequency single-epoch precise positioning method with baseline constrain for bridge dynamic monitoring, to improve the positioning availability and reliability, as well as narrow the search space, and increase the success rate of ambiguity resolution and positioning.
+	Xue et al.\cite{Xue2021} comprehensively evaluated multi-GNSS low-cost receivers for deformation monitoring and concluded that the potential improvement of the precision of the low-cost receiver by using multi-GNSS measurements and a GNSS base station with a geodetic antenna.}
 	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection.
@@
 
-	In another category of GNSS-based displacement detection research, GNSS is only used as a static positioning method.
+	\textcolor{r_s}{
+	The other category is about displacement detection research based on GNSS.
+	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
+	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection.
+Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
+	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges.
+Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific.
+Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
+	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
+	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
+	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz.
+Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS.
+There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
 	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
-	The results showed that the accuracy of the Global positioning system (GPS) measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
+	The results showed that the accuracy of the GPS measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
 	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
@@
 	There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
-	Kalman filter is used in the implementation of  RTK, and the observation model, the state model, and the extended Kalman filtering process of RTK are introduced below. 
-	\subsubsection{Observation Model}
-	The double-difference(DD) observation model is usually used in RTK, and its definition is as follows\cite{teunissen2017springer}.
-	\begin{equation}
-	\left. \begin{array}{l}
-	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - \Delta \nabla I_{\Phi {i_{br}}}^{jk} + \Delta \nabla  T_{br}^{jk} + \Delta \nabla  M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
-	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla I_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla T_{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla  M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}
-	\end{array} \right\}
-	\label{eq_dd_obs}
-	\end{equation}
-	In this observation equation, $\Delta \nabla $ denotes the DD operator, $i$ denotes the frequency; $b$ and $r$ denote base station and rover station respectively; $j$ and $k$ represent the satellites;
-	$\Delta \nabla P_{{{i}_{br}}}^{jk}$ and $\Delta \nabla \Phi _{{{i}_{br}}}^{jk}$ denote pseudo-range and carrier-phase DD observations, respectively; 
-	$\Delta \nabla \rho _{br}^{jk}$ is the DD geometric distance between receivers and satellites; 
-	$\Delta \nabla  M_{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla  M_{{{\Phi }_{{{i}_{br}}}}}^{jk}$ denote pseudo-range and carrier-phase multipath error, respectively; 
-	$\Delta \nabla \varepsilon _{{{P}_{{{i}_{br}}}}}^{jk}$ and $\Delta \nabla \varepsilon _{{{\Phi }_{{{i}_{br}}}}}^{jk}$ represent DD measurement noise of pseudo-range and carrier-phase, respectively; 
-	$\Delta \nabla  I_{\Phi {{i}_{br}}}^{jk}$is the DD ionospheric delay between receivers and satellites, and the ionospheric error has the same absolute value but the opposite sign on pseudo-range and carrier-phase observations\cite{teunissen2017springer}; $\Delta \nabla T_{br}^{jk}$is the DD tropospheric delay between receivers and satellites.
-	For the short baseline, the atmospheric error can be ignored, so the above DD observation equation is simplified as
-	\begin{equation}
-	\left. \begin{array}{l}
-	\Delta \nabla P_{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} + \Delta \nabla  M_{{P_{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{P_{{i_{br}}}}}^{jk}\\
-	\Delta \nabla \Phi _{{i_{br}}}^{jk} = \Delta \nabla \rho _{br}^{jk} - {\lambda _i}\Delta \nabla N_{{i_{br}}}^{jk} + \Delta \nabla  M_{{\Phi _{{i_{br}}}}}^{jk} + \Delta \nabla \varepsilon _{{\Phi _{{i_{br}}}}}^{jk}\end{array} \right\}
-	\label{eq_dd_obs_simplified}
-	\end{equation}
-	Ignoring the influence of multipath, the linearization form of formula (\ref{eq_dd_obs_simplified}) is expressed as
-	\begin{equation}
-	\label{eq_rtk_measure}
-	{\bf{y}} = {\bf{Hx}} + {\bf{\varepsilon }}
-	\end{equation}
-	where $\bf{y}$ is the observation minus the computed,  $\bf{H} $ is the linearized design matrix\cite{hofmann-wellenhof2007gnss}, $\bf{x}\triangleq {{[{{\mathbf{r}}_{r}},\Delta \nabla \mathbf{N}]}^{T}}$, is the state vector, which contains the rover station coordinate ${{\mathbf{r}}_{r}}$ and the DD integer ambiguity $\Delta \nabla \mathbf{N}$;  $\mathbf{\varepsilon } $ is the observation noise, and its covariance matrix is expressed as  ${{\mathbf{R}}_{\varepsilon }} $.
-
-	After forming the observation equation, the ‘float’ solution of the parameter can be obtained by the standard least square method. 
-	The 'float' solution and variance of integer ambiguity are expressed as  $\Delta \nabla \mathbf{\tilde{N}} $,  ${{\mathbf{Q}}_{\Delta \nabla \mathbf{\tilde{N}}}} $, respectively. 
-	To obtain high precision positioning results, it is necessary to fix the integer ambiguity. 
-	The problem of ambiguity fixing can be described as\cite{teunissen1995the}.
-	\begin{equation}
-	\Delta \nabla {\bf{\hat N}} = \mathop {\arg min}\limits_{\Delta \nabla {\bf{N}} \in {\bf{Z}}} ((\Delta \nabla {\bf{N}} - \Delta  {\bf{\tilde N}}){\bf{Q}}_{\Delta \nabla {\bf{\tilde N}}}^{ - 1}{(\Delta \nabla {\bf{N}} - \Delta \nabla {\bf{\tilde N}})^T})
-	\label{eq_lamda}
-	\end{equation}
-	There are many methods referring to integer ambiguity resolution, among which LAMBDA (Least-squares Ambiguity Decorrelation Adjustment)\cite{teunissen1995the} method is the most widely used one.
-The integer ambiguity is obtained by the integer least square method.
-Then, the test process is executed to determine whether to accept or reject the integer ambiguity\cite{teunissen2003integer,teunissen2005gnss}.
-If the test is passed, the fixed integer ambiguity can be substituted into (\ref{eq_rtk_measure}) to resolve the fixed solution, otherwise, the ‘float’ solution will be maintained.
-
-	\subsubsection{State Model}
-	The state model is defined as follows (Takasu 2013)
-	\begin{equation}
-	{{\bf{x}}_k} = {\bf{F}}{{\bf{x}}_{k - 1}} + {\bf{w}}
-	\end{equation}
-	where ${\bf{F}} \buildrel \Delta \over = \left[ {\begin{array}{*{20}{c}}
-		{{{\bf{I}}_{3 \times 3}}}&{\bf{0}}\\
-		{\bf{0}}&{{{\bf{I}}_{(2n - 2)(2n - 2)}}}
-		\end{array}} \right]$ , is the transition matrix from $k-1$ to $k$; $\mathbf{I}$ denotes the identity matrix; $n$ represents the number of satellites observed simultaneously by the base station and the rover station;
-	Only GPS ${{L}_{1}}$ and ${{L}_{2}}$ frequency observations are considered, so $2n-2$ DD ambiguities are formed. 
-	$\mathbf{w}$ is the process noise, and its covariance matrix is expressed as ${{\mathbf{G}}_{w}}$. 
-	For kinematic positioning, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning.
-	\subsubsection{Extended Kalman filtering}
-	Kalman filtering includes two processes: prediction update and measurement update\cite{grewal2001kalman}. The prediction process is as follows:
-	\begin{equation}
-	{{\bf{\hat x}}_{k|k - 1}} = {\bf{F}}{{\bf{\hat x}}_{k - 1}}
-	\end{equation}
-	\begin{equation}
-	{{\bf{Q}}_{k|k - 1}} = {\bf{F}}{{\bf{Q}}_{k - 1}}{{\bf{F}}^T} + {{\bf{G}}_w}(k)
-	\end{equation}
-	where ${\bf{\hat x}}_{k|k - 1}$ is the predicted value and ${\bf{Q}}_{k|k - 1}$ is the corresponding covariance.
-According to the definition of the state transition matrix above, it can be seen that the state value of the previous epoch remains unchanged.
-However, the coordinate covariance component becomes larger, while the ambiguity covariance component remains unchanged.
-The measurement update process is as follows:
-	\begin{equation}
-	{{\bf{v}}_k} = {\bf{y}}(k) - {\bf{H}}_k{{\bf{\hat x}}_{k|k - 1}}
-	\end{equation}
-	\begin{equation}
-	{{\bf{S}}_k} = {\bf{H}}_k{{\bf{Q}}_{k|k - 1}}{\bf{H}}{_k^{\rm{T}}} + {{\bf{R}}_\varepsilon }(k)
-	\end{equation}
-	\begin{equation}
-	{\bf{K}} = {{\bf{Q}}_{k|k - 1}}{\bf{H}}_k^T{\bf{S}}_k^{ - 1}
-	\end{equation}
-	where ${{\mathbf{v}}_{k}}$ denotes the innovation vector, and ${{\mathbf{S}}_{k}}$ is the covariance matrix of the innovation vector; $\mathbf{K}$ is the state estimation gain matrix.
-The final state is estimated as follows:
-	\begin{equation}
-	{{\bf{\hat x}}_k} = {{\bf{\hat x}}_{k|k - 1}} + {\bf{K}}{{\bf{v}}_k}
-	\end{equation}
-	\begin{equation}
-	{{\bf{Q}}_k} = {{\bf{Q}}_{k|k - 1}} - {\bf{K}}{{\bf{S}}_k}{{\bf{K}}^T}
-	\end{equation}
-	where ${{\mathbf{\hat{x}}}_{k}}$ is the final estimate, and ${{\mathbf{Q}}_{k}}$ is the corresponding covariance matrix; ${{\mathbf{\hat{x}}}_{k}}$ is the only input of the Bayesian inference.
-
+	\textcolor{r_s}{Therefore, in this work, RTK is adopted as the kinematic positioning model.
+	RTK is implemented by extended Kalman filtering, where the design matrix is derived from the double-difference observation model, and the state transition matrix is the identity matrix.
+For the covariance matrix of process noise, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning\cite{takasu2011rtklib}.
+}
 	\subsection{Workflow of displacement detection }  
-	In the previous paragraphs, the displacement detection model using Bayesian inference is proposed, and the principle of relative real-time kinematic positioning is presented.
+	In the previous paragraphs, the displacement detection model using Bayesian inference is proposed, and the \textcolor{r_s}{ kinematic positioning model is described.}
 	The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.

### 2021-09-12 paper/r1/manuscript-mssp.tex
add ndop_snrmp_analysis

@@
 
-		\title{GNSS-based Displacement Detection Using Bayesian Inference for Deformation Monitoring}
+		\title{GNSS-based \textcolor{r_s}{Short-term} Displacement Detection Using Bayesian Inference for Deformation Monitoring}
 
@@
 	%Displacement detection involves displacement identification and extraction. 
-	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}. 
 	There are many researches on displacement detection based on GNSS, which can be divided into two categories.
@@
 	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
-	In addition, GNSS was also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements were used as references\cite{atanasova2018ground,fuhrmann2015estimation}.
-	In these studies, the GNSS static positioning mode is usually adopted.
+	\textcolor{r_s}{
+		Betti et al.\cite{betti2001deformation,betti2011deformation} studied the use of the Bayesian approach to evaluating deformation from GPS time series, in which a test procedure was constructed under the Bayesian framework.
+However, in this method, only specific epochs are tested, and how to identify these epochs is not involved.
+		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test, and the control network processing results are generally based on repeated static adjustment.
+	}
 
 	%目前针对GNSS动态定位时间序列的位移识别和提取的研究还很少。目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
+	%基于GNSS的位移监测通常是可以通过时域差分来完成
+	%GNSS定位结果可以来源于重复的静态测量结果，重复测量周期一般为一天到几个月，这类叫监测被称作长周期监测。
+	%另外，也可以利用实时定位结果进行探测，已获得实时或者近实时的探测结果，这类被称作短周期探测。
+	\textcolor{r_s}{
+	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}.
+The positioning results can be obtained from repeated GNSS static measurements, and the repetition period is generally one day to several months.
+This kind of displacement detection is called long-term displacement detection.
+In addition, real-time or near real-time detection can be obtained by using GNSS kinematic positioning results, which is called short-term detection.}
 	At present, there are few studies on displacement identification and extraction of GNSS kinematic positioning time series.
@@
 In this work, the Markov chain Monte Carlo technique is used to approximate the integral or sum value.
-Monte Carlo sampling is to construct the integral or sum function as the expectation under a certain distribution, and then approximate the expectation by the corresponding average value\cite{goodfellow2016deep}.
-
-	\begin{equation}\label{eq_monte_carlo_1}
-	s =\sum\limits_x g(x)= \sum\limits_x {p(x)f(x) = {E_p}[f(x)]}
-	\end{equation}
-	\begin{equation}\label{eq_monte_carlo_2}
-	s =\int {g(x)dx}= \int {p(x)f(x)dx}  = {E_p}[f(x)]
-	\end{equation}
-	where $g(x)$ is the function to be integrated or summated; $p(x)$ is the probability distribution or probability density function of $x$.
-The integral or summation problem of $g(x)$ is transformed into the mathematical expectation problem of $f(x)$ under the distribution $p(x)$.
-This mathematical expectation can be approximated by sampling from $p(x)$\cite{goodfellow2016deep}.
-
-	\begin{equation}\label{eq_monte_carlo_3}
-	\hat s = \frac{1}{n}\sum\limits_{i = 1}^n {f({x_i})}
-	\end{equation}
-	where $x_i$ is the sample with the distribution of $p(x)$.
-As can be seen from the above, Monte Carlo method as a general sampling simulation sum or integration method, depends on sampling from the distribution of $p(x)$.
-However, it is not easy to directly sample from the target distribution of $p(x)$.
-At present, the most popular solution is to use Markov chain Monte Carlo sampling, which provides a general way to construct a sequence that converges to the target distribution.
-According to Markov chain, the probability of state transition at a certain time only depends on its previous state, which is expressed as follows\cite{robert2013monte}
-
-	\begin{equation}\label{eq_markov_chain_1}
-	P({x_{n + 1}}\left| {{x_n},{x_{n - 1}}} \right.,{x_{n - 2}}, \cdots ,{x_2},{x_1}) = P({x_{n + 1}}\left| {{x_n}} \right.)
-	\end{equation}
-	If a Markov process is neither periodic nor irreducible, then the Markov process is ergodic, that is, each state appears with a certain probability.
-The Markov process of ergodic states has an important property: no matter what the initial state probability is, the Markov process of the ergodic state tends to be a stable distribution after enough state transitions\cite{robert2013monte}.
-	That is, for the initial probability distribution is $\pi_0(x)$, the probability distribution after several rounds of state transition is as follows
-
-	\begin{equation}\label{eq_markov_chain_2}
-	\pi_{0}(x),\pi_{1}(x),\pi_{2}(x),\cdots \pi_{n}(x),\pi_{n+1}(x),\pi_{n+2}(x)\cdots
-	\end{equation}
-	There exists $n$ which satisfies the following conditions
-
-	\begin{equation}\label{eq_markov_chain_3}
-	\pi_{n}(x)=\pi_{n+1}(x)=\pi_{n+2}(x)\cdots
-	\end{equation}
-	This is the target distribution we want to construct.
-Based on the initial arbitrary simple probability distribution such as Gaussian distribution $\pi_{0}(x)$, the state value $x_0$ is obtained by sampling.
-Based on the probability distribution $\pi_{1}(x)=\pi_{0}(x)P(x\left| {{x_0}} \right.)$ sampling state value $x_1$, using the same method, execute $n$ times.
-Sample $(x_{n},x_{n+1},x_{n+2}\cdots)$ is the corresponding sample set of the target distribution.
-However, the implementation of MCMC also needs to consider other factors such as constructing the state transition matrix according to the target distribution\cite{robert2013monte}, which is beyond the scope of this work.
 Two implementations of MCMC,  the Metropolis-Hasting sampler\cite{chib1995understanding} and the No-U-Turn sampler\cite{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively.
@@
 
-	\subsubsection{Field Experiment 1}
+	\subsubsection{Field Experiment 1}%rover_bd9_3
 	GNSS observations were processed epoch by epoch by using RTK mode, and the corresponding coordinate output was the only input of the proposed displacement detection method.
@@
 	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}.
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
+		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
+		\label{fig_v_ndop_snrmp_9_3}
+	\end{figure} 
 	The index values of different index-based detection methods in field experiment 1 are shown in Fig.
@@
 	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
-	\subsubsection{Field Experiment 2}
+	\subsubsection{Field Experiment 2}%rover_bd9_4 part(650)
 	This experiment is similar to the previous one except that the displacement amplitude is smaller. 
@@
 	\end{table}
+
+	\begin{figure}[htbp]
+	\centering
+	\includegraphics[scale=0.45]{ndop_snrmp_9_4}
+	\caption{Number of satellites, GDOP, SNR, multipath of experiment 2.}
+	\label{fig_v_ndop_snrmp_9_4}
+	\end{figure} 
 	As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 

### 2021-09-21 paper/r1/manuscript-mssp.tex
basic revision

@@
 
-		\title{GNSS-based \textcolor{r_s}{Short-term} Displacement Detection Using Bayesian Inference for Deformation Monitoring}
+		\title{\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference for Deformation Monitoring}}
 
@@
 		%% \address[label2]{}
-
 		\author[a]{Nan Shen}
@@
 %		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
-		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
+		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results.
 		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
@@
 	The first category is about the research of measurement technology in GNSS-based displacement detection.
-	To evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.
+	To evaluate the performance of single base station \textcolor{r_s}{real-time} kinematic(RTK) and network \textcolor{r_s}{real-time} kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.
 The results showed that NRTK has advantages in accuracy and robustness.
@@
 	\textcolor{r_s}{
-	The other category is about displacement detection research based on GNSS.
+	The other category is displacement detection research based on GNSS.
 	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
@@
 	As shown in subgraphs (c) and (d), the height of the antenna was measured with a tape before and after each movement of the object hanging on the plank. 
-	Five readings were taken for each measurement to ensure data reliability.
+	\textcolor{r_s}{
+		The minimum scale of the tape is 1 mm, that is, the accuracy of the tape is 1 mm, and the estimated reading is 0.1 mm.
+		Take five readings for each measurement to ensure the accuracy and reliability of the data.
+	}
 	Besides, markers are made on the ground and on the antenna respectively to ensure that the same position was referenced for each measurement. 
@@
 	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}.
-	\begin{figure}[htbp]
-		\centering
-		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
-		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
-		\label{fig_v_ndop_snrmp_9_3}
-	\end{figure} 
 	The index values of different index-based detection methods in field experiment 1 are shown in Fig.
@@
 	The main reason is that the displacement control device is not fully controllable.
-	It can be seen from Fig. \ref{fig_v_bd9_3_up_ts} that before the second displacement change, the plank appears obvious floating when measuring with the tape. 
+\textcolor{r_s}{
+	As can be seen from Fig.
+\ref{fig_v_bd9_3_up_ts}, the time series fluctuates obviously near the abrupt displacement.
+To explore the possible causes, the number of satellites, geometric dilution of precision(GDOP), signal-to-noise ratio(SNR), and multipath are shown in Fig.
+\ref{fig_v_ndop_snrmp_9_3}.
+The number of satellites and GDOP changed when the displacement took place, which may be caused by the shielding of the antenna during operation.
+The SNR and multipath have also changed when the displacement takes place, possibly due to antenna vibration caused by touch or wind.}
+
 	As shown in Fig. \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
@@
 	%然而，我们可能更加关注主要变化点，后面通过加入额外先验来提升主要变化点的识别，弱化次要变化点。
-
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
+		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
+		\label{fig_v_ndop_snrmp_9_3}
+	\end{figure} 
 	\begin{figure}[htbp]
@@
 
-	\begin{figure}[htbp]
-	\centering
-	\includegraphics[scale=0.45]{ndop_snrmp_9_4}
-	\caption{Number of satellites, GDOP, SNR, multipath of experiment 2.}
-	\label{fig_v_ndop_snrmp_9_4}
-	\end{figure} 
 	As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
@@
 	The larger displacement error at $\tau_2$ is mainly due to the incompletely controllable experimental equipment. 
+	\textcolor{r_s}{
+		 The number of satellites, GDOP, SNR, and multipath are shown in Fig.
+\ref{fig_v_ndop_snrmp_9_4}.
+The number of satellites and GDOP changed at $\tau_2$, which may be caused by the shielding of the antenna during operation.}
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[scale=0.45]{ndop_snrmp_9_4}
+		\caption{Number of satellites, GDOP, SNR, multipath of experiment 2.}
+		\label{fig_v_ndop_snrmp_9_4}
+	\end{figure} 
 	But on the whole, using the proposed method, the displacement extraction accuracy in the experiment can reach less than 2 mm.
@@
 	As can be seen from the above discussion that the interval constraint prior can effectively improve the identifiability of change points.
-	On the other hand, it also shows that the Bayesian inference-based displacement detection method proposed in this paper is flexible enough to meet different analysis needs by adding a priori.
+	\textcolor{r_s}{
+		This is the first time that Bayesian inference has been used for displacement detection based on GNSS kinematic positioning.
+		Compared with indicator-based detection methods, this method has high robustness and flexibility.
+		The method based on Bayesian inference uses multi-epoch observation data, which is more reliable.
+		On the other hand, the Bayesian inference-based displacement detection method proposed in this paper is flexible enough to meet different analysis needs by adding a priori.
+	}
 
@@
 	\label{concl}
-	This study set out to develop a Bayesian model for displacement detection from GNSS kinematic positioning in a short time. 
+	This study set out to develop a Bayesian model for displacement detection from GNSS kinematic positioning. 
 	The description of multiple displacements is given, and the Bayesian model for multiple displacement detection is proposed.
@@
 	This study provides the first comprehensive assessment of the Bayesian inference model for displacement identification and extraction from GNSS kinematic positioning.
+	\textcolor{r_s}{
+	Although the method is verified with GNSS kinematic data, the method is also suitable for long-term displacement detection.
+The main difference is the error model and influencing factors considered, which will be carried out in the follow-up work.
+	}
 

### 2021-09-22 paper/r1/manuscript-mssp.tex
gram

@@
 	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
-	The results showed that the accuracy of the GPS measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
+	The results showed that the accuracy of the GPS measurement \textcolor{r_s}{for} 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
 	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
-	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
+	The results of a nine-month field monitoring provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
 	\textcolor{r_s}{
@@
 However, in this method, only specific epochs are tested, and how to identify these epochs is not involved.
-		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test, and the control network processing results are generally based on repeated static adjustment.
+		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test and the control network processing results are generally based on repeated static adjustment.
 	}
@@
 	GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results\cite{abidin2004use,rs12203375}.
-The positioning results can be obtained from repeated GNSS static measurements, and the repetition period is generally one day to several months.
+The positioning results can be obtained from repeated GNSS static measurements and the repetition period is generally one day to several months.
 This kind of displacement detection is called long-term displacement detection.
@@
 In \cite{li2010deformation}, a multiple Kalman filters model was proposed for deformation detection in the GPS real-time series.
-Different filters in the model represent different displacement models, which need to be defined in advance.
+Different filters in the model represent different displacement models, which \textcolor{r_s}{needs} to be defined in advance.
 	In addition, the index-based is also widely used, but it is easily affected by the observation noise, so further measures need to be taken\cite{shen_shortterm2021}.
 	A modified real-time Chow test approach was proposed for fast deformation monitoring\cite{bellone2016real}.
-This kind of method based on statistical index is easily affected by observation noise, and is not suitable for small displacement detection\cite{pirotti2015micro}.
+This kind of method based on \textcolor{r_s}{a} statistical index is easily affected by observation noise, and is not suitable for small displacement detection\cite{pirotti2015micro}.
 Besides, Dabove and Manzino\cite{dabove2016fast} introduced a cluster-based method for dynamic deformation analysis, but this method did not perform well on real data.
@@
 
-	The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of coordinate.
+	The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of \textcolor{r_s}{coordinates}.
 The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.
@@
 	Through (\ref{eq_bayesian_prior_tau_basic}) and (\ref{eq_bayesian_prior_tau_5}), the joint probability of all change points can be determined.
-Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by formula (\ref{eq_bayesian_prior}), (\ref{eq_bayesian_prior_sigma}), (\ref{eq_bayesian_prior_mu_sum}), (\ref{eq_bayesian_prior_tau_5}).
+Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by \textcolor{r_s}{formulas} (\ref{eq_bayesian_prior}), (\ref{eq_bayesian_prior_sigma}), (\ref{eq_bayesian_prior_mu_sum}), (\ref{eq_bayesian_prior_tau_5}).
 After the Bayesian model of displacement detection is given, MCMC, one of the implementation methods of Bayesian inference, is introduced.
@@
 		\includegraphics[scale=0.45]{v_workflow}
-		\caption{Bayesian model for displacement detection.}
+		\caption{\textcolor{r_s}{Displacement detection process based on Bayesian inference.}}
 		\label{fig_v_workflow}
@@
 	In the simulation experiment, the data is composed of designed displacement and noise.
-	In the field experiment, the displacement is controlled manually by the  the self-built displacement control platform.
+	In the field experiment, the displacement is controlled manually by the self-built displacement control platform.
 	Moreover, the results of some commonly used index-based abrupt detection methods including the Buishand U test(BUT), Pettitt’s test (PETT), standard normal homogeneity test (SNHT), Z test(ZT), are given for comparison.
@@
 	\end{figure} 
-	The blue curve in Fig. \ref{fig_v_mu_sim_simple} is the fitting result of Gaussian distribution of the histogram.
+	The blue curve in Fig. \ref{fig_v_mu_sim_simple} is the fitting result of \textcolor{r_s}{the} Gaussian distribution of the histogram.
 	Although we assume that the prior distribution of $\bf{\mu}$ in the model obeys a uniform distribution, the posterior sample approximately obeys normal distribution. 
@@
 	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}.
-	The index values of different index-based detection methods in field experiment 1 are shown in Fig.
+	The index values of different index-based detection methods in \textcolor{r_s}{the} field experiment 1 are shown in Fig.
 \ref{fig_v_exp1_idx}.
@@
 		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
-		\caption{Histogram of posterior sample of $\sigma$ in field experiment 1.}
+		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 1.}
 		\label{fig_v_bd9_3_up_sigma}
@@
 	The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
-	In reality, multiple change points exist, such as multiple displacements in a short period of time in the process of landslide or settlement.
+	In reality, multiple change points exist, such as multiple displacements in a short period in the process of landslide or settlement.
 	However, more attention is paid to the primary change points.
@@
 		\includegraphics[scale=0.45]{v_bd9_4_up_sigma}
-		\caption{Histogram of posterior sample of $\sigma$ in field experiment 2.}
+		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 2.}
 		\label{fig_v_bd9_4_up_sigma}
@@
 		\includegraphics[scale=0.45]{v_simple_p_model_add_new_rule}
-		\caption{Bayesian model for displacement detection with an interval constraint prior.}
+		\caption{ \textcolor{r_s}{Probability} model for displacement detection with an interval constraint prior.}
 		\label{fig_v_simple_p_model_add_new_rule}
@@
 	In the following data processing, the interval $d$ is set to 300.
-	The data in field experiment 1 is reprocessed with the new Bayesian model, and the posterior distribution of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.
+	The data in \textcolor{r_s}{the} field experiment 1 is reprocessed with the new Bayesian model, and the posterior distribution of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.
 
@@
 	There is no significant change in the posterior distribution of $\tau_2$, $\mu$, and  $\sigma$.
-	The data in field experiment 2 is also reprocessed with the new Bayesian model, and the results are shown in Fig.
+	The data in field experiment 2 is also reprocessed with the new \textcolor{r_s}{probability} model, and the results are shown in Fig.
 \ref{fig_v_bd9_4_up_tau_add_new_rule}, \ref{fig_v_exp2_idx}, \ref{fig_v_bd9_4_up_mu_add_new_rule}, and \ref{fig_v_bd9_4_up_sigma_add_new_rule}.
@@
 		\includegraphics[scale=0.45]{v_bd9_4_up_sigma_add_new_rule}
-		\caption{Histogram of posterior sample of $\sigma$ in field experiment 2 with an interval constraint prior.}
+		\caption{Histogram of posterior \textcolor{r_s}{samples} of $\sigma$ in field experiment 2 with an interval constraint prior.}
 		\label{fig_v_bd9_4_up_sigma_add_new_rule}
@@
 	From the comparison between Fig. \ref{fig_v_bd9_4_up_mu} and Fig. \ref{fig_v_bd9_4_up_mu_add_new_rule}, it can be seen that the secondary peak of $\mu_1$ almost disappears.
-	However, there are still some sample points which deviate from the main peak.
-	In order to reduce the influence of these sampling points, the median value of the sample is used as the final estimation of \textbf{$\mu$}, and $\mu_0$, $\mu_1$ and $\mu_2$ are obtained as -1461.18 mm, -1482.37 mm and -1509.09 mm respectively.
+	However, there are still some sample points \textcolor{r_s}{that} deviate from the main peak.
+	To reduce the influence of these sampling points, the median value of the sample is used as the final estimation of \textbf{$\mu$}, and $\mu_0$, $\mu_1$ and $\mu_2$ are obtained as -1461.18 mm, -1482.37 mm and -1509.09 mm respectively.
 	The two displacements obtained by these means are -21.19 mm and -26.72 mm, respectively, and the displacements measured in Table \ref{tab_measured_height_9_4} are -21.3 mm and -19.6 mm respectively.

### 2021-09-23 paper/r1/manuscript-mssp.tex
methods

@@
 	\label{method}
-	In this section, the Bayesian model of displacement detection and its implementation based on MCMC are presented first. Then the GNSS  real-time kinematic positioning model is introduced.
-	\subsection{Bayesian Model for Displacement Detection}
+	\textcolor{r_s}{A displacement detection method for deformation monitoring is proposed, which detects displacement, thus probably landslide, subsidence behavior.
+The method mainly includes three steps: GNSS kinematic positioning, Bayesian inference, and posterior sample analysis.
+The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig.
+\ref{fig_v_workflow}.}
+	\begin{figure*}[htpb]
+		\centering
+		\includegraphics[scale=0.45]{v_workflow}
+		\caption{\textcolor{r_s}{Displacement detection method based on Bayesian inference.}}
+		\label{fig_v_workflow}
+	\end{figure*}
 
-	The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of \textcolor{r_s}{coordinates}.
-The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.
-	The time corresponding to the $n$ change points satisfies the following relationship: $ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
-	The problem of displacement detection is to find out the time of displacement and estimate the displacement.
-
-	\subsubsection{Bayesian Inference}
+	As shown in Fig. \ref{fig_v_workflow}, to begin this process, the kinematic positioning is carried out to obtain the coordinates time series to form the data source of Bayesian inference. 
+	Before the displacement detection,  the posterior samples of model parameters are obtained by Bayesian inference based on the MCMC sampling.
+	After obtaining the posterior sample distribution of the parameters, the displacement identification is achieved by the posterior sample distribution of the change points.
+	On getting the change points, the displacement is extracted by the posterior sample distribution of  the 'mean' parameters.
+	Finally, according to the analysis of the posterior samples, the \textcolor{r_s}{displacement detection probability model } is optimized as needed.
+\textcolor{r_s}{The center of Fig.
+\ref{fig_v_workflow} is a graphical description of the displacement detection probability model.}
+	\subsection{Relative Real-time Kinematic (RTK)}
+	There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
+	\textcolor{r_s}{Therefore, in this work, RTK is adopted as the kinematic positioning model.
+		RTK is implemented by extended Kalman filtering, where the design matrix is derived from the double-difference observation model, and the state transition matrix is the identity matrix.
+		For the covariance matrix of process noise, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning\cite{takasu2011rtklib}.
+	}
+	\subsection{Bayesian Inference}
+	\textcolor{r_s}{The data basis of Bayesian inference is introduced above, and a brief introduction to Bayesian inference is given here.}
 	Bayesian inference is one of the most important skills in statistics, and deduces the posterior probability as the result of a priori probability and likelihood function\cite{robert2014machine}.
@@
 ${P({\bf{x}})}$ is the total likelihood, which is a constant value.
+	\textcolor{r_s}{Before proceeding to Bayesian inference, it is must to define the probability model for displacement detection.}
+	\subsection{\textcolor{r_s}{Probability} Model for Displacement Detection}
+
+	The displacement time series is described as $\left[ {{x_1},{x_2}, \cdots {x_m}} \right]$, and the corresponding time is denoted as $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$, where $m$ is the number of \textcolor{r_s}{coordinates}.
+The displacement occurrence time is expressed as $\left[ {{\tau _1},{\tau _2}, \cdots {\tau _n}} \right]$, which is a subset of $\left[ {{t_1},{t_2}, \cdots {t_m}} \right]$.
+	The time corresponding to the $n$ change points satisfies the following relationship: $ {{\tau _1}<{\tau _2}<\cdots {\tau _{n-1}}<{\tau _n}} $.
+	The problem of displacement detection is to find out the time of displacement and estimate the displacement.
 
@@
 Finally, the prior distribution of parameter ${\bf{\theta }}$ can be determined by \textcolor{r_s}{formulas} (\ref{eq_bayesian_prior}), (\ref{eq_bayesian_prior_sigma}), (\ref{eq_bayesian_prior_mu_sum}), (\ref{eq_bayesian_prior_tau_5}).
-After the Bayesian model of displacement detection is given, MCMC, one of the implementation methods of Bayesian inference, is introduced.
+After the \textcolor{r_s}{probability model for} displacement detection is given, MCMC, one of the implementation methods of Bayesian inference, is introduced.
 
-	\subsubsection{Markov Chain Monte Carlo (MCMC)}
+	\subsection{Markov Chain Monte Carlo (MCMC)}
 	The posterior distribution of the parameters depends on the prior distribution and the likelihood function.
@@
 Two implementations of MCMC,  the Metropolis-Hasting sampler\cite{chib1995understanding} and the No-U-Turn sampler\cite{hoffman2014no}, are used to sample discrete random variables and continuous random variables, respectively.
-Next, the data source of the proposed method: GNSS real-time kinematic positioning is introduced.
-
-	\subsection{Relative Real-time Kinematic (RTK)}
-	There are many real-time kinematic positioning models, among which RTK is the most widely used model in deformation monitoring.
-	\textcolor{r_s}{Therefore, in this work, RTK is adopted as the kinematic positioning model.
-	RTK is implemented by extended Kalman filtering, where the design matrix is derived from the double-difference observation model, and the state transition matrix is the identity matrix.
-For the covariance matrix of process noise, the coordinate covariance component is set to be large to capture dynamic features, while the ambiguity covariance component is set to $\mathbf{0}$ to ensure the stability of positioning\cite{takasu2011rtklib}.
-}
-	\subsection{Workflow of displacement detection }  
-	In the previous paragraphs, the displacement detection model using Bayesian inference is proposed, and the \textcolor{r_s}{ kinematic positioning model is described.}
-	The workflow of the GNSS-based displacement detection using Bayesian inference is shown in Fig. \ref{fig_v_workflow}.
-	\begin{figure*}[htpb]
-		\centering
-		\includegraphics[scale=0.45]{v_workflow}
-		\caption{\textcolor{r_s}{Displacement detection process based on Bayesian inference.}}
-		\label{fig_v_workflow}
-	\end{figure*}
-
-	As shown in Fig. \ref{fig_v_workflow}, to begin this process, the kinematic positioning is carried out to obtain the coordinates time series to form the data source of Bayesian inference. 
-	Before the displacement detection,  the posterior samples of model parameters are obtained by Bayesian inference based on the MCMC sampling.
-	After obtaining the posterior sample distribution of the parameters, the displacement identification is achieved by the posterior sample distribution of the change points.
-	On getting the change points, the displacement is extracted by the posterior sample distribution of  the 'mean' parameters.
-	Finally, according to the analysis of the posterior samples, the original Bayesian model is optimized as needed.
-	The middle of Fig. \ref{fig_v_workflow} is a graphical description of the Bayesian model of displacement detection and its implementation described above.
-
 	\section{Experiments and Results}

### 2021-09-23 paper/r1/manuscript-mssp.tex
exp

@@
 	The simulation results are shown in Fig. \ref{fig_v_sim_simple_gauss_ts}.
-
 	\begin{figure}[htbp]
@@
 	As shown in Fig. \ref{fig_v_sim_simple_gauss_ts}, the whole time series is divided into four segments by three displacement change points. 
-	Using the model designed above, Bayesian inference is implemented by the MCMC sampling. 
+	\textcolor{r_s}{The time series is processed by the proposed method, and Bayesian inference is realized through MCMC sampling using the probability model designed above.} 
 	The posterior sample distribution of $\bf{\tau}$ is shown in Fig. \ref{fig_v_tau_sim_simple}.
-
 	\begin{figure}[htbp]
@@
 	\end{figure}
-	As can be seen from Fig. \ref{fig_v_tau_sim_simple}, all the designed displacement change points are identified. 
-	$\tau_3$ is the easiest to be identified, mainly due to the largest displacement amplitude. 
-	Since the displacement amplitude at $\tau_2$ is small and there are fewer sample points on the right side, the estimated accuracy is worse than the other two change points.
+
+	As can be seen from Fig. \ref{fig_v_tau_sim_simple}, \textcolor{r_s}{there are more samples at the displacement, and} all the designed displacement change points are identified. 
+	$\tau_3$ is the easiest to \textcolor{r_s}{identify}, mainly due to \textcolor{r_s}{its maximum} displacement amplitude. 
+	  \textcolor{r_s}{Due to the smaller displacement amplitude and fewer samples on the right at $\tau_2$}, the estimated accuracy is worse than the other two change points.
 	The histogram of the posterior sample of $\bf{\mu}$ is shown in Fig. \ref{fig_v_mu_sim_simple}.
@@
 	The estimation accuracy of $\mu_4$ is the lowest, and the corresponding posterior sample coverage is the widest. 
-	These are mainly due to the fact that the most observation samples are used for $\mu_2$ estimation, while the least observation samples are used for $\mu_4$ estimation. 
+	These are mainly due to the fact that most samples are used for $\mu_2$ estimation, while least samples are used for $\mu_4$ estimation. 
 	As shown in Fig. \ref{fig_v_sigma_sim_simple}, $\sigma$ is also accurately estimated.
@@
 	The index values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
-	It can be seen that the numerical range of indicators used by different detection methods is not consistent, but all are obvious at the designed abrupt point.
-	However, to automatically identify these abrupt points based on these index values, additional work is required, such as setting a certain threshold.
+	It can be seen that the numerical range of indicators used by different \textcolor{r_s}{index-based} detection methods is not consistent, but all are obvious at the designed abrupt point.
+	However, to automatically identify these abrupt points based on these index values, additional work is required, such as setting a certain threshold  \textcolor{r_s}{or detection window\cite{shen_shortterm2021}}.
 	In addition, these methods were originally designed to detect abrupt points without involving displacement extraction.
@@
 	\subsubsection{Field Experiment 1}%rover_bd9_3
-	GNSS observations were processed epoch by epoch by using RTK mode, and the corresponding coordinate output was the only input of the proposed displacement detection method.
-	The results of RTK positioning are shown in Fig. \ref{fig_v_bd9_3_up_tau}.
+	GNSS observations were processed epoch by epoch by using RTK mode, and the results are shown in Fig. \ref{fig_v_bd9_3_up_tau}.
 	Only the vertical displacement was triggered in the experiment, so only the up coordinate component is displayed. 
@@
 	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
-	The RTK positioning results are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. 
+	\textcolor{r_s}{The RTK positioning results are served as the input of displacement detection}, and Bayesian inference is implemented by the MCMC sampling. 
 	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
@@
 	As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
-	The time series are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling.
+	\textcolor{r_s}{The RTK positioning results are served as the input of displacement detection}, and Bayesian inference is implemented by the MCMC sampling.
 The results are shown in Fig.
@@
 	In the next section, we will discuss adding a prior to the model to improve the performance of Bayesian inference.
+	In the next section, we will discuss adding a prior to the \textcolor{r_s}{probability} model to improve the performance of the \textcolor{r_s}{displacement detection method}.
 	\section{Discussion}
@@
 	\end{equation}
-	where $d$ is the shortest time interval to be constrained. The new Bayesian probability model with the prior is shown in Fig. \ref{fig_v_simple_p_model_add_new_rule}.
+	where $d$ is the shortest time interval to be constrained. The new \textcolor{r_s}{probability} model with the prior is shown in Fig. \ref{fig_v_simple_p_model_add_new_rule}.
 
@@
 	In the following data processing, the interval $d$ is set to 300.
-	The data in \textcolor{r_s}{the} field experiment 1 is reprocessed with the new Bayesian model, and the posterior distribution of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau_add_new_rule}.
+	The data in \textcolor{r_s}{the} field experiment 1 is reprocessed with the new \textcolor{r_s}{probability} model, and the posterior distribution of $\tau$ is shown in Fig.
+\ref{fig_v_bd9_3_up_tau_add_new_rule}.
 
@@
 		On the other hand, the Bayesian inference-based displacement detection method proposed in this paper is flexible enough to meet different analysis needs by adding a priori.
+Although only the vertical direction has been verified due to the experimental equipment, the horizontal direction should also be adapted because the vertical direction is noisier.
 	}
@@
 	\label{concl}
-	This study set out to develop a Bayesian model for displacement detection from GNSS kinematic positioning. 
-	The description of multiple displacements is given, and the Bayesian model for multiple displacement detection is proposed.
+	This study set out to develop a \textcolor{r_s}{displacement detection approach} from GNSS kinematic positioning. 
+	\textcolor{r_s}{GNSS kinematic positioning is used to provide epoch by epoch coordinate time series for displacement detection.}
 	The principle of Bayesian inference and its implementation based on MCMC sampling are presented.
-	To provide epoch by epoch coordinate time series for displacement detection, the principle of GNSS kinematic positioning mode RTK is introduced.
+	The description of multiple displacements is given, and the \textcolor{r_s}{probability} model for multiple displacement detection is proposed.
 	The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
@@
 
-	Significant displacements can be effectively detected by the displacement Bayesian inference model.
-	The displacement is obtained by the difference of the mean of the coordinates before and after the change point, which can be obtained by the mean of the posterior sample.
+	Significant displacements can be effectively detected by the displacement \textcolor{r_s}{detection method}.
+	The displacement is obtained by the difference of the mean of the coordinates before and after the change point, which can be obtained by the mean of \textcolor{r_s}{posterior samples}.
 	The accuracy of the final displacement is determined by the number of available samples before and after the change point.
@@
 	By adding an interval constraint prior, the influence of secondary change points can be effectively weakened.
-	To reduce the influence of the sample points of the secondary change point on the displacement extraction, the coordinate mean before and after the change point can be estimated by the median of the posterior sample.
+	To reduce the influence of \textcolor{r_s}{samples} of the secondary change point on the displacement extraction, the coordinate mean before and after the change point can be estimated by the median of \textcolor{r_s}{posterior samples}.
 
-	The displacement detection based on Bayesian inference can meet different needs by adding a priori, and has sufficient flexibility.
+	The displacement detection \textcolor{r_s}{method} based on Bayesian inference can meet different needs by adding a priori, and has sufficient flexibility.
 	In addition, the Bayesian inference implementation based on MCMC sampling used in this paper provides posterior samples, which is more conducive to problem analysis.
-	This study provides the first comprehensive assessment of the Bayesian inference model for displacement identification and extraction from GNSS kinematic positioning.
+	This study provides the first comprehensive assessment of the Bayesian inference \textcolor{r_s}{based method} for displacement identification and extraction from GNSS kinematic positioning.
 	\textcolor{r_s}{
 	Although the method is verified with GNSS kinematic data, the method is also suitable for long-term displacement detection.
-The main difference is the error model and influencing factors considered, which will be carried out in the follow-up work.
+The main difference is the probability model and influencing factors considered, which will be carried out in the follow-up work.
 	}

### 2021-09-24 paper/r1/manuscript-mssp.tex
reponse to reviwer 2

@@
 
-		\title{\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference for Deformation Monitoring}}
+		\title{\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference}}
 
@@
 		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
-		Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
+		Specifically, we use the Bayesian inference to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
 		%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
@@
 	The first category is about the research of measurement technology in GNSS-based displacement detection.
-	To evaluate the performance of single base station \textcolor{r_s}{real-time} kinematic(RTK) and network \textcolor{r_s}{real-time} kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.
+	To evaluate the performance of single base station \textcolor{r_s}{real-time} kinematic (RTK) and network \textcolor{r_s}{real-time} kinematic (NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}.
 The results showed that NRTK has advantages in accuracy and robustness.
@@
 The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
-	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied.
+	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position (PPP) has been studied.
 The results showed that PPP can be capable of detecting large landslides.
@@
 	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
-	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
+	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop (PLL) bandwidth and noise in 100 Hz GPS measurement.
 	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz.
@@
 		\includegraphics[scale=0.45]{v_workflow}
-		\caption{\textcolor{r_s}{Displacement detection method based on Bayesian inference.}}
+		\caption{\textcolor{r_s}{Displacement detection based on Bayesian inference from GNSS Kinematic Positioning.}}
 		\label{fig_v_workflow}
@@
 	\textcolor{r_s}{
-		This is the first time that Bayesian inference has been used for displacement detection based on GNSS kinematic positioning.
+		This is the first time that Bayesian inference has been used for displacement detection from GNSS kinematic positioning.
 		Compared with indicator-based detection methods, this method has high robustness and flexibility.

### 2021-09-24 paper/r1/manuscript-mssp.tex
Response to Reviewers.docx

@@
 
-		\title{\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference}}
+		\title{\textcolor{r_s}{Displacement Detection Based on Bayesian Inference from GNSS Kinematic Positioning for Deformation Monitoring}}
 
@@
 		For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior.
-The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
+The accuracy of \textcolor{r_s}{vertical} displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.
 		\end{abstract}
@@
 	%  相比而言，本文提出的方法是一种简单直接易于实现的一站式方法。
-	The index values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
+	\textcolor{r_s}{
+		Detection values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
+	}
 	It can be seen that the numerical range of indicators used by different \textcolor{r_s}{index-based} detection methods is not consistent, but all are obvious at the designed abrupt point.
-	However, to automatically identify these abrupt points based on these index values, additional work is required, such as setting a certain threshold  \textcolor{r_s}{or detection window\cite{shen_shortterm2021}}.
+\textcolor{r_s}{These detection values can be obtained in real-time from the GNSS kinematic positioning results.} However, to automatically identify these abrupt points based on these \textcolor{r_s}{detection} values, additional work is required, such as setting a certain threshold  \textcolor{r_s}{or detection window\cite{shen_shortterm2021}}.
 In addition, these methods were originally designed to detect abrupt points without involving displacement extraction.
-	There are abrupt detection and displacement extraction methods based on these indicators, but the implementation process is complex\cite{shen_shortterm2021}.
-	In contrast, the method proposed in this work is a simple, straightforward, and easy-to-implement one-stop method.
+\textcolor{r_s}{
+	Although there are improved methods of abrupt detection and displacement extraction based on these indicators, the implementation process is complex\cite{shen_shortterm2021}.
+	} In contrast, the method proposed in this work is a simple, straightforward, and easy-to-implement one-stop method.
 	\begin{figure}[htbp]
@@
 	\includegraphics[scale=0.45]{v_sim_idx}
-	\caption{Index values of different index-based detection methods in simulation experiments.}
+	\caption{\textcolor{r_s}{Detection values of different index-based detection methods in the simulation experiment.}}
 	\label{fig_v_sim_idx}
@@
 		\includegraphics[scale=0.45]{v_exp1_idx}
-		\caption{Index values of different index-based detection methods in field experiment 1.}
+		\caption{\textcolor{r_s}{Detection values of different index-based detection methods in field experiment 1.}}
 		\label{fig_v_exp1_idx}
@@
 \ref{fig_v_bd9_3_up_ts}, the time series fluctuates obviously near the abrupt displacement.
-To explore the possible causes, the number of satellites, geometric dilution of precision(GDOP), signal-to-noise ratio(SNR), and multipath are shown in Fig.
+To explore the possible causes, the number of satellites, geometric dilution of precision (GDOP), signal-to-noise ratio (SNR), and multipath are shown in Fig.
 \ref{fig_v_ndop_snrmp_9_3}.
-The number of satellites and GDOP changed when the displacement took place, which may be caused by the shielding of the antenna during operation.
+When the displacement occurs, the number of satellites and GDOP change, especially at $\tau_2$, which may be the reason for the inconsistency between the reference displacement and the estimated displacement.
 	The SNR and multipath have also changed when the displacement takes place, possibly due to antenna vibration caused by touch or wind.}
@@
 		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
-		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
+		\caption{\textcolor{r_s}{Number of satellites, GDOP, SNR, multipath of experiment 1.}}
 		\label{fig_v_ndop_snrmp_9_3}
@@
 	\includegraphics[scale=0.45]{v_exp2_idx}
-	\caption{Index values of different index-based detection methods in field experiment 2.}
+	\caption{\textcolor{r_s}{Detection values of different index-based detection methods in field experiment 2.}}
 	\label{fig_v_exp2_idx}
@@
 	\textcolor{r_s}{
-		 The number of satellites, GDOP, SNR, and multipath are shown in Fig.
-\ref{fig_v_ndop_snrmp_9_4}.
-The number of satellites and GDOP changed at $\tau_2$, which may be caused by the shielding of the antenna during operation.}
+		 The number of satellites, GDOP, SNR, and multipath are shown in Fig. \ref{fig_v_ndop_snrmp_9_4}. 
+		 From the SNR and multipath, it can be seen that the quality of the observation data on the right side of $\tau_2$ is better than that on the left side.}
 	\begin{figure}[htbp]
@@
 		\includegraphics[scale=0.45]{ndop_snrmp_9_4}
-		\caption{Number of satellites, GDOP, SNR, multipath of experiment 2.}
+		\caption{\textcolor{r_s}{Number of satellites, GDOP, SNR, multipath of experiment 2.}}
 		\label{fig_v_ndop_snrmp_9_4}

### 2021-11-21 code/matlab/analysis/import_n_dop.m
nsfc

@@ -1,0 +1,54 @@
+function ndop1 = import_n_dop(filename, startRow, endRow)
+%IMPORTFILE 将文本文件中的数值数据作为矩阵导入。
+%   NDOP1 = IMPORTFILE(FILENAME) 读取文本文件 FILENAME 中默认选定范围的数据。
+%
+%   NDOP1 = IMPORTFILE(FILENAME, STARTROW, ENDROW) 读取文本文件 FILENAME 的
+%   STARTROW 行到 ENDROW 行中的数据。
+%
+% Example:
+%   ndop= import_n_dop('n_dop.txt', 2, 13309);
+%
+%    另请参阅 TEXTSCAN。
+
+% 由 MATLAB 自动生成于 2021/09/11 23:36:51
+
+%% 初始化变量。
+if nargin<=2
+    startRow = 2;
+    endRow = inf;
+end
+
+%% 每个文本行的格式:
+%   列1: 双精度值 (%f)
+%	列2: 双精度值 (%f)
+%   列3: 双精度值 (%f)
+%	列4: 双精度值 (%f)
+%   列5: 双精度值 (%f)
+%	列6: 双精度值 (%f)
+%   列7: 双精度值 (%f)
+% 有关详细信息，请参阅 TEXTSCAN 文档。
+formatSpec = '%4f%9f%8f%9f%9f%9f%f%[^\n\r]';
+
+%% 打开文本文件。
+fileID = fopen(filename,'r');
+
+%% 根据格式读取数据列。
+% 该调用基于生成此代码所用的文件的结构。如果其他文件出现错误，请尝试通过导入工具重新生成代码。
+dataArray = textscan(fileID, formatSpec, endRow(1)-startRow(1)+1, 'Delimiter', '', 'WhiteSpace', '', 'TextType', 'string', 'EmptyValue', NaN, 'HeaderLines', startRow(1)-1, 'ReturnOnError', false, 'EndOfLine', '\r\n');
+for block=2:length(startRow)
+    frewind(fileID);
+    dataArrayBlock = textscan(fileID, formatSpec, endRow(block)-startRow(block)+1, 'Delimiter', '', 'WhiteSpace', '', 'TextType', 'string', 'EmptyValue', NaN, 'HeaderLines', startRow(block)-1, 'ReturnOnError', false, 'EndOfLine', '\r\n');
+    for col=1:length(dataArray)
[…]

### 2021-11-21 code/matlab/analysis/import_snr_mp.m

@@ -1,0 +1,95 @@
+function snrmp = import_snr_mp(filename, startRow, endRow)
+%IMPORTFILE 将文本文件中的数值数据作为矩阵导入。
+%   SNRMP = IMPORTFILE(FILENAME) 读取文本文件 FILENAME 中默认选定范围的数据。
+%
+%   SNRMP = IMPORTFILE(FILENAME, STARTROW, ENDROW) 读取文本文件 FILENAME 的
+%   STARTROW 行到 ENDROW 行中的数据。
+%
+% Example:
+%   snrmp = importfile('snr_mp.txt', 2, 99549);
+%
+%    另请参阅 TEXTSCAN。
+
+% 由 MATLAB 自动生成于 2021/09/11 21:41:49
+
+%% 初始化变量。
+if nargin<=2
+    startRow = 2;
+    endRow = inf;
+end
+
+%% 将数据列作为文本读取:
+% 有关详细信息，请参阅 TEXTSCAN 文档。
+formatSpec = '%4s%10s%8s%9s%9s%10s%s%[^\n\r]';
+
+%% 打开文本文件。
+fileID = fopen(filename,'r');
+
+%% 根据格式读取数据列。
+% 该调用基于生成此代码所用的文件的结构。如果其他文件出现错误，请尝试通过导入工具重新生成代码。
+dataArray = textscan(fileID, formatSpec, endRow(1)-startRow(1)+1, 'Delimiter', '', 'WhiteSpace', '', 'TextType', 'string', 'HeaderLines', startRow(1)-1, 'ReturnOnError', false, 'EndOfLine', '\r\n');
+for block=2:length(startRow)
+    frewind(fileID);
+    dataArrayBlock = textscan(fileID, formatSpec, endRow(block)-startRow(block)+1, 'Delimiter', '', 'WhiteSpace', '', 'TextType', 'string', 'HeaderLines', startRow(block)-1, 'ReturnOnError', false, 'EndOfLine', '\r\n');
+    for col=1:length(dataArray)
+        dataArray{col} = [dataArray{col};dataArrayBlock{col}];
+    end
+end
+
+%% 关闭文本文件。
+fclose(fileID);
+
+%% 将包含数值文本的列内容转换为数值。
+% 将非数值文本替换为 NaN。
+raw = repmat({''},length(dataArray{1}),length(dataArray)-1);
+for col=1:length(dataArray)-1
[…]
